---
title: "Individual Methodologies"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Note get.prob function has to be changed according to whether test set is pre or post 2022.

```{r}
source("2_1_hierarchical_model_probabilities.R")
grand.slams <- c("Australian Open","Roland Garros","Wimbledon","Us Open")
# "Us Open" specific to 2022 test sets
get.prob.pre.2022 <- function(p1,p2,match,atp=TRUE){
  if (is.na(p1)||is.na(p2)){
    return(NA)
  }
  if (match %in% grand.slams){
    if (match=="US Open"){
      ret <- match.win.prob.nonpw(p1,p2,format=0+atp)
    } else {
      ret <- match.win.prob.nonpw(p1,p2,format=4+atp)
    }
  } else {
    ret <- match.win.prob.nonpw(p1,p2,format=0)
  }
  return(ret)
}
get.prob.post.2022 <- function(p1,p2,match,atp=TRUE){
  if (is.na(p1)||is.na(p2)){
    return(NA)
  }
  if (match %in% grand.slams){
    ret <- match.win.prob.nonpw(p1,p2,format=2+atp)
  } else {
    ret <- match.win.prob.nonpw(p1,p2,format=0)
  }
  return(ret)
}
```

## Data

```{r}
# testing data
# if Error: no more error handlers available (recursive errors?); invoking 'abort' restart
# Warning: type 29 is unimplemented in 'type2char'Error in pmatch(rw, c("read", "write"), 0L) : 
# INTEGER() can only be applied to a 'integer', not a 'unknown type #29'
# just run again
atp.test <- read.csv('../New Data/atp/atp_testing_2022.csv')
wta.test <- read.csv('../New Data/wta/wta_testing_2022.csv')
```
```{r}
# following function highlights matches that were incomplete
# this is determined by if the score has letters ("W/O","Def.","RET" etc.)
# takes as input the score column of a dataset and returns indexes
ic.match <- function(score) grep("[A-Za-z]",score)
ic.atp <- ic.match(atp.test$score)
ic.wta <- ic.match(wta.test$score)
```
```{r}
# training data
atp.basic <- read.csv('../New Data/atp/2019-2021_atp_individual.csv')
wta.basic <- read.csv('../New Data/wta/2019-2021_wta_individual.csv')
atp.h2h <- read.csv('../New Data/atp/2019-2021_atp_h2h.csv')
wta.h2h <- read.csv('../New Data/wta/2019-2021_wta_h2h.csv')
atp.co <- read.csv('../New Data/atp/2019-2021_atp_co.csv')
wta.co <- read.csv('../New Data/wta/2019-2021_wta_co.csv')
# for the match specific datasets, they also need ic entries removed
atp.h2h <- atp.h2h[-ic.atp,]
wta.h2h <- wta.h2h[-ic.wta,]
atp.co <- atp.co[-ic.atp,]
wta.co <- wta.co[-ic.wta,]
# remove incomplete matches for test sets
atp.test <- atp.test[-ic.atp,]
wta.test <- wta.test[-ic.wta,]
# reset indices after row removals
row.names(atp.h2h) <- NULL
row.names(atp.co) <- NULL
row.names(wta.h2h) <- NULL
row.names(wta.co) <- NULL
row.names(atp.test) <- NULL
row.names(wta.test) <- NULL
```

Testing set sizes: ATP 2022 (1220) / WTA 2022 (1371) / ATP 2018 (1304) / WTA 2018 (1457) / ATP 2014 (1330) / WTA 2014 (1467)

## Individual Methods

### Basic

```{r}
# ad-hoc code used to check na rate, don't uncomment
# wta.basic$total_pts_served <- wta.basic$grass_pts_served + 
#   wta.basic$clay_pts_served + wta.basic$hard_pts_served
# wta.basic$total_service_pts_won <- wta.basic$grass_service_pts_won +
#   wta.basic$hard_service_pts_won + wta.basic$clay_service_pts_won
# wta.basic$p.estimate <- wta.basic$total_service_pts_won/wta.basic$total_pts_served
# ids <- unique(c(wta.test$winner_id,wta.test$loser_id))
# wta.na.check <- wta.basic$p.estimate[which(wta.basic$player_id %in% ids)]
# length(which(is.na(wta.na.check)))/length(wta.na.check)
# sum(wta.basic$grass_pts_served)+sum(wta.basic$clay_pts_served)+sum(wta.basic$hard_pts_served)
```

```{r}
# ad-hoc code used to check na rate, don't uncomment
# atp.basic$total_pts_served <- atp.basic$grass_pts_served + 
#   atp.basic$clay_pts_served + atp.basic$hard_pts_served
# atp.basic$total_service_pts_won <- atp.basic$grass_service_pts_won +
#   atp.basic$hard_service_pts_won + atp.basic$clay_service_pts_won
# atp.basic$p.estimate <- atp.basic$total_service_pts_won/atp.basic$total_pts_served
# ids <- unique(c(atp.test$winner_id,atp.test$loser_id))
# atp.na.check <- atp.basic$p.estimate[which(atp.basic$player_id %in% ids)]
# length(which(is.na(atp.na.check)))/length(atp.na.check)
# sum(atp.basic$grass_pts_served)+sum(atp.basic$clay_pts_served)+sum(atp.basic$hard_pts_served)
```

```{r}
# augmentations to training set
atp.basic$total_pts_served <- atp.basic$grass_pts_served + 
  atp.basic$clay_pts_served + atp.basic$hard_pts_served
atp.basic$total_service_pts_won <- atp.basic$grass_service_pts_won +
  atp.basic$hard_service_pts_won + atp.basic$clay_service_pts_won
atp.basic$p.estimate <- atp.basic$total_service_pts_won/atp.basic$total_pts_served
# since using id's we have all players, most have NA p estimates
# plug in average of other p's
atp.basic$p.estimate[which(is.na(atp.basic$p.estimate))] <-
  mean(atp.basic$p.estimate[-which(is.na(atp.basic$p.estimate))])

wta.basic$total_pts_served <- wta.basic$grass_pts_served + 
  wta.basic$clay_pts_served + wta.basic$hard_pts_served
wta.basic$total_service_pts_won <- wta.basic$grass_service_pts_won +
  wta.basic$hard_service_pts_won + wta.basic$clay_service_pts_won
wta.basic$p.estimate <- wta.basic$total_service_pts_won/wta.basic$total_pts_served
# since using id's we have all players, most have NA p estimates
# plug in average of other p's
wta.basic$p.estimate[which(is.na(wta.basic$p.estimate))] <-
  mean(wta.basic$p.estimate[-which(is.na(wta.basic$p.estimate))])
```

Plug in values: ATP 2022 (0.595843) / WTA 2022 (0.5227285) / ATP 2018 (0.5921587) / WTA 2018 (0.5178595) / ATP 2014 (0.585246) / WTA 2014 (0.5145110)

```{r}
n <- nrow(atp.test)
res1 <- rep(0,n)
exact.res1 <- rep(0,n) # for merges etc.
for (i in 1:n){
  winner <- atp.test$winner_id[i]
  loser <- atp.test$loser_id[i]
  winner.idx <- which(atp.basic$player_id==winner)
  loser.idx <- which(atp.basic$player_id==loser)
  if (atp.basic$p.estimate[winner.idx]>atp.basic$p.estimate[loser.idx]) res1[i]<-1
  exact.res1[i] <- get.prob.post.2022(atp.basic$p.estimate[winner.idx],
                                     atp.basic$p.estimate[loser.idx],
                                     atp.test$tourney_name[i],atp=TRUE)
}
saveRDS(exact.res1,"../Results/Individual/atp22_basic")
mean(res1)
```

ATP 2022 (0.6081967) / ATP 2018 (0.6173313) / ATP 2014 (0.5902256)

```{r}
n <- nrow(wta.test)
res2 <- rep(0,n)
exact.res2 <- rep(0,n)
for (i in 1:n){
  winner <- wta.test$winner_id[i]
  loser <- wta.test$loser_id[i]
  winner.idx <- which(wta.basic$player_id==winner)
  loser.idx <- which(wta.basic$player_id==loser)
  if (wta.basic$p.estimate[winner.idx]>wta.basic$p.estimate[loser.idx]) res2[i]<-1
  exact.res2[i] <- get.prob.post.2022(wta.basic$p.estimate[winner.idx],
                                     wta.basic$p.estimate[loser.idx],
                                     wta.test$tourney_name[i])
}
saveRDS(exact.res2,"../Results/Individual/wta22_basic")
mean(res2)
```

WTA 2022 (0.6017505) / WTA 2018 (0.6012354) / WTA 2014 (0.6203136)

### Opponent-Adjusted Formula

```{r}
# same augmentation as [1]
# augmentations to training set
# reload set after experiment
atp.basic$total_pts_served <- atp.basic$grass_pts_served + 
  atp.basic$clay_pts_served + atp.basic$hard_pts_served
atp.basic$total_service_pts_won <- atp.basic$grass_service_pts_won +
  atp.basic$hard_service_pts_won + atp.basic$clay_service_pts_won
atp.basic$p.estimate <- atp.basic$total_service_pts_won/atp.basic$total_pts_served
atp.basic$p.estimate[which(is.na(atp.basic$p.estimate))] <-
  mean(atp.basic$p.estimate[-which(is.na(atp.basic$p.estimate))])
# get q estimates as well
atp.basic$total_pts_received <- atp.basic$grass_pts_received +
  atp.basic$hard_pts_received + atp.basic$clay_pts_received
atp.basic$total_receiving_pts_won <- atp.basic$grass_receiving_pts_won +
  atp.basic$hard_receiving_pts_won + atp.basic$clay_receiving_pts_won
atp.basic$q.estimate <- atp.basic$total_receiving_pts_won/atp.basic$total_pts_received
q.bar <- mean(atp.basic$q.estimate[-which(is.na(atp.basic$q.estimate))])
atp.basic$q.estimate[which(is.na(atp.basic$q.estimate))] <- q.bar

n <- nrow(atp.test)
res3 <- rep(0,n)
exact.res3 <- rep(0,n) # for merges etc.
for (i in 1:n){
  winner <- atp.test$winner_id[i]
  loser <- atp.test$loser_id[i]
  winner.idx <- which(atp.basic$player_id==winner)
  loser.idx <- which(atp.basic$player_id==loser)
  winner.adj.p <- atp.basic$p.estimate[winner.idx]-(atp.basic$q.estimate[loser.idx]-q.bar)
  loser.adj.p <- atp.basic$p.estimate[loser.idx]-(atp.basic$q.estimate[winner.idx]-q.bar)
  res3[i] <- winner.adj.p > loser.adj.p
  exact.res3[i] <- get.prob.post.2022(winner.adj.p,loser.adj.p,                         
                                      atp.test$tourney_name[i],atp=TRUE)
}
mean(res3)
saveRDS(exact.res3,"../Results/Individual/atp22_oaf")
```

ATP 2022 (0.6516393) / ATP 2018 (0.6395706) / ATP 2014 (0.6383459)

```{r}
# same augmentation as [1]
# augmentations to training set
# reload set after experiment
wta.basic$total_pts_served <- wta.basic$grass_pts_served + 
  wta.basic$clay_pts_served + wta.basic$hard_pts_served
wta.basic$total_service_pts_won <- wta.basic$grass_service_pts_won +
  wta.basic$hard_service_pts_won + wta.basic$clay_service_pts_won
wta.basic$p.estimate <- wta.basic$total_service_pts_won/wta.basic$total_pts_served
wta.basic$p.estimate[which(is.na(wta.basic$p.estimate))] <-
  mean(wta.basic$p.estimate[-which(is.na(wta.basic$p.estimate))])
# get q estimates as well
wta.basic$total_pts_received <- wta.basic$grass_pts_received +
  wta.basic$hard_pts_received + wta.basic$clay_pts_received
wta.basic$total_receiving_pts_won <- wta.basic$grass_receiving_pts_won +
  wta.basic$hard_receiving_pts_won + wta.basic$clay_receiving_pts_won
wta.basic$q.estimate <- wta.basic$total_receiving_pts_won/wta.basic$total_pts_received
q.bar <-  mean(wta.basic$q.estimate[-which(is.na(wta.basic$q.estimate))])
wta.basic$q.estimate[which(is.na(wta.basic$q.estimate))] <- q.bar

n <- nrow(wta.test)
res4 <- rep(0,n)
exact.res4 <- rep(0,n) # for merges etc.
for (i in 1:n){
  winner <- wta.test$winner_id[i]
  loser <- wta.test$loser_id[i]
  winner.idx <- which(wta.basic$player_id==winner)
  loser.idx <- which(wta.basic$player_id==loser)
  winner.adj.p <- wta.basic$p.estimate[winner.idx]-(wta.basic$q.estimate[loser.idx]-q.bar)
  loser.adj.p <- wta.basic$p.estimate[loser.idx]-(wta.basic$q.estimate[winner.idx]-q.bar)
  res4[i] <- winner.adj.p > loser.adj.p
  exact.res4[i] <- get.prob.post.2022(winner.adj.p,loser.adj.p,                         
                                      wta.test$tourney_name[i])
}
mean(res4)
saveRDS(exact.res4,"../Results/Individual/wta22_oaf")
```

WTA 2022 (0.6316557) / WTA 2018 (0.6300618) / WTA 2014 (0.6625767)

### Head-to-Head

```{r}
# in h2h/co datasets, p1 is always the winner
atp.h2h$w_total_pts_served <- atp.h2h$grass_pts_served1 + 
  atp.h2h$hard_pts_served1 + atp.h2h$clay_pts_served1
atp.h2h$w_total_service_pts_won <- atp.h2h$grass_service_pts_won1 +
  atp.h2h$hard_service_pts_won1 + atp.h2h$clay_service_pts_won1
atp.h2h$w_p <- atp.h2h$w_total_service_pts_won/atp.h2h$w_total_pts_served
atp.h2h$l_total_pts_served <- atp.h2h$grass_pts_served2 + 
  atp.h2h$hard_pts_served2 + atp.h2h$clay_pts_served2
atp.h2h$l_total_service_pts_won <- atp.h2h$grass_service_pts_won2 +
  atp.h2h$hard_service_pts_won2 + atp.h2h$clay_service_pts_won2
atp.h2h$l_p <- atp.h2h$l_total_service_pts_won/atp.h2h$l_total_pts_served
# first see accuracy for entries where h2h data is available
h2h.valid <- which(!is.na(atp.h2h$w_p)) #l_p also works
res5 <- rep(0,length(h2h.valid))
exact.res5 <- rep(0,length(h2h.valid))
for (i in 1:length(h2h.valid)){
  res5[i] <- atp.h2h$w_p[h2h.valid[i]] > atp.h2h$l_p[h2h.valid[i]]
  exact.res5[i] <- get.prob.post.2022(atp.h2h$w_p[h2h.valid[i]],atp.h2h$l_p[h2h.valid[i]],
                                      atp.test$tourney_name[h2h.valid[i]],atp=TRUE)
}
mean(res5)
```

ATP 2022 (0.6167401) / ATP 2018 (0.6412214) / ATP 2014 (0.6433962)

```{r}
res5.sv <- rep(-1,nrow(atp.test))
res5.sv[h2h.valid] <- res5
exact.res5.sv <- rep(-1,nrow(atp.test))
exact.res5.sv[h2h.valid] <- exact.res5
saveRDS(res5.sv,"../Results/Individual/atp22_h2h_binary")
saveRDS(exact.res5.sv,"../Results/Individual/atp22_h2h")
```

```{r}
# in h2h/co datasets, p1 is always the winner
wta.h2h$w_total_pts_served <- wta.h2h$grass_pts_served1 + 
  wta.h2h$hard_pts_served1 + wta.h2h$clay_pts_served1
wta.h2h$w_total_service_pts_won <- wta.h2h$grass_service_pts_won1 +
  wta.h2h$hard_service_pts_won1 + wta.h2h$clay_service_pts_won1
wta.h2h$w_p <- wta.h2h$w_total_service_pts_won/wta.h2h$w_total_pts_served
wta.h2h$l_total_pts_served <- wta.h2h$grass_pts_served2 + 
  wta.h2h$hard_pts_served2 + wta.h2h$clay_pts_served2
wta.h2h$l_total_service_pts_won <- wta.h2h$grass_service_pts_won2 +
  wta.h2h$hard_service_pts_won2 + wta.h2h$clay_service_pts_won2
wta.h2h$l_p <- wta.h2h$l_total_service_pts_won/wta.h2h$l_total_pts_served
# first see accuracy for entries where h2h data is available
h2h.valid <- which(!is.na(wta.h2h$w_p)) #l_p also works
res6 <- rep(0,length(h2h.valid))
exact.res6 <- rep(0,length(h2h.valid))
for (i in 1:length(h2h.valid)){
  res6[i] <- wta.h2h$w_p[h2h.valid[i]] > wta.h2h$l_p[h2h.valid[i]]
  exact.res6[i] <- get.prob.post.2022(wta.h2h$w_p[h2h.valid[i]],wta.h2h$l_p[h2h.valid[i]],
                                      wta.test$tourney_name[h2h.valid[i]])
}
mean(res6)
```

WTA 2022 (0.5237154) / WTA 2018 (0.5906977) / WTA 2014 (0.6268657)

```{r}
res6.sv <- rep(-1,nrow(wta.test))
res6.sv[h2h.valid] <- res6
exact.res6.sv <- rep(-1,nrow(wta.test))
exact.res6.sv[h2h.valid] <- exact.res6
saveRDS(res6.sv,"../Results/Individual/wta22_h2h_binary")
saveRDS(exact.res6.sv,"../Results/Individual/wta22_h2h")
```

### Common Opponents (No Surface Filtering)

```{r}
# in h2h/co datasets, p1 is always the winner
atp.co$w_total_pts_served <- atp.co$grass_pts_served1 + 
  atp.co$hard_pts_served1 + atp.co$clay_pts_served1
atp.co$w_total_service_pts_won <- atp.co$grass_service_pts_won1 +
  atp.co$hard_service_pts_won1 + atp.co$clay_service_pts_won1
atp.co$w_p <- atp.co$w_total_service_pts_won/atp.co$w_total_pts_served
atp.co$l_total_pts_served <- atp.co$grass_pts_served2 + 
  atp.co$hard_pts_served2 + atp.co$clay_pts_served2
atp.co$l_total_service_pts_won <- atp.co$grass_service_pts_won2 +
  atp.co$hard_service_pts_won2 + atp.co$clay_service_pts_won2
atp.co$l_p <- atp.co$l_total_service_pts_won/atp.co$l_total_pts_served
# first see accuracy for entries where co data is available
co.valid <- which(!is.na(atp.co$w_p) & !is.na(atp.co$l_p))
res7 <- rep(0,length(co.valid))
exact.res7 <- rep(0,length(co.valid))
for (i in 1:length(co.valid)){
  res7[i] <- atp.co$w_p[co.valid[i]] > atp.co$l_p[co.valid[i]]
  exact.res7[i] <- get.prob.post.2022(atp.co$w_p[co.valid[i]],atp.co$l_p[co.valid[i]],
                                      atp.test$tourney_name[co.valid[i]],atp=TRUE)
}
mean(res7)
```

ATP 2022 (0.6147144) / ATP 2018 (0.633945) / ATP 2014 (0.6341463)

```{r}
res7.sv <- rep(-1,nrow(atp.test))
res7.sv[co.valid] <- res7
exact.res7.sv <- rep(-1,nrow(atp.test))
exact.res7.sv[co.valid] <- exact.res7
saveRDS(res7.sv,"../Results/Individual/atp22_co_binary")
saveRDS(exact.res7.sv,"../Results/Individual/atp22_co")
```

```{r}
# in h2h/co datasets, p1 is always the winner
wta.co$w_total_pts_served <- wta.co$grass_pts_served1 + 
  wta.co$hard_pts_served1 + wta.co$clay_pts_served1
wta.co$w_total_service_pts_won <- wta.co$grass_service_pts_won1 +
  wta.co$hard_service_pts_won1 + wta.co$clay_service_pts_won1
wta.co$w_p <- wta.co$w_total_service_pts_won/wta.co$w_total_pts_served
wta.co$l_total_pts_served <- wta.co$grass_pts_served2 + 
  wta.co$hard_pts_served2 + wta.co$clay_pts_served2
wta.co$l_total_service_pts_won <- wta.co$grass_service_pts_won2 +
  wta.co$hard_service_pts_won2 + wta.co$clay_service_pts_won2
wta.co$l_p <- wta.co$l_total_service_pts_won/wta.co$l_total_pts_served
# first see accuracy for entries where co data is available
co.valid <- which(!is.na(wta.co$w_p) & !is.na(wta.co$l_p))
res8 <- rep(0,length(co.valid))
exact.res8 <- rep(0,length(co.valid))
for (i in 1:length(co.valid)){
  res8[i] <- wta.co$w_p[co.valid[i]] > wta.co$l_p[co.valid[i]]
  exact.res8[i] <- get.prob.post.2022(wta.co$w_p[co.valid[i]],wta.co$l_p[co.valid[i]],
                                      wta.test$tourney_name[co.valid[i]])
}
mean(res8)
```

WTA 2022 (0.5905512) / WTA 2018 (0.5813783) / WTA 2014 (0.6184408)

```{r}
res8.sv <- rep(-1,nrow(wta.test))
res8.sv[co.valid] <- res8
exact.res8.sv <- rep(-1,nrow(wta.test))
exact.res8.sv[co.valid] <- exact.res8
saveRDS(res8.sv,"../Results/Individual/wta22_co_binary")
saveRDS(exact.res8.sv,"../Results/Individual/wta22_co")
```

### Common Opponents with Opponent-Adjusted Formula

```{r}
# in h2h/co datasets, p1 is always the winner
atp.co$w_total_pts_served <- atp.co$grass_pts_served1 + 
  atp.co$hard_pts_served1 + atp.co$clay_pts_served1
atp.co$w_total_service_pts_won <- atp.co$grass_service_pts_won1 +
  atp.co$hard_service_pts_won1 + atp.co$clay_service_pts_won1
atp.co$w_p <- atp.co$w_total_service_pts_won/atp.co$w_total_pts_served
atp.co$l_total_pts_served <- atp.co$grass_pts_served2 + 
  atp.co$hard_pts_served2 + atp.co$clay_pts_served2
atp.co$l_total_service_pts_won <- atp.co$grass_service_pts_won2 +
  atp.co$hard_service_pts_won2 + atp.co$clay_service_pts_won2
atp.co$l_p <- atp.co$l_total_service_pts_won/atp.co$l_total_pts_served

atp.co$w_total_pts_received <- atp.co$grass_pts_received1 + 
  atp.co$hard_pts_received1 + atp.co$clay_pts_received1
atp.co$w_total_receiving_pts_won <- atp.co$grass_receiving_pts_won1 +
  atp.co$hard_receiving_pts_won1 + atp.co$clay_receiving_pts_won1
atp.co$w_q <- atp.co$w_total_receiving_pts_won/atp.co$w_total_pts_received
atp.co$l_total_pts_received <- atp.co$grass_pts_received2 + 
  atp.co$hard_pts_received2 + atp.co$clay_pts_received2
atp.co$l_total_receiving_pts_won <- atp.co$grass_receiving_pts_won2 +
  atp.co$hard_receiving_pts_won2 + atp.co$clay_receiving_pts_won2
atp.co$l_q <- atp.co$l_total_receiving_pts_won/atp.co$l_total_pts_received
q.bar <- mean(c(atp.co$w_q[which(!is.na(atp.co$w_q))],
                atp.co$l_q[which(!is.na(atp.co$l_q))]))
# For CO(OAF) already dealing with incomplete coverage,
# no further imputation needed

co.valid <- which(!is.na(atp.co$w_p) & !is.na(atp.co$l_p))
resY <- rep(0,length(co.valid))
exact.resY <- rep(0,length(co.valid))
for (i in 1:length(co.valid)){
  exact.resY[i] <- get.prob.post.2022(atp.co$w_p[co.valid[i]]-(atp.co$l_q[co.valid[i]]-q.bar),
                                      atp.co$l_p[co.valid[i]]-(atp.co$w_q[co.valid[i]]-q.bar),
                                      atp.test$tourney_name[co.valid[i]],atp=TRUE)
  resY[i] <- exact.resY[i] > 0.5
}
mean(resY)
```

ATP 2014 (0.684803) / ATP 2018 (0.666055) / ATP 2022 (0.6360116)

```{r}
resY.sv <- rep(-1,nrow(atp.test))
resY.sv[co.valid] <- resY
exact.resY.sv <- rep(-1,nrow(atp.test))
exact.resY.sv[co.valid] <- exact.resY
saveRDS(resY.sv,"../Results/Ensembles/atp22_co(oaf)_binary")
saveRDS(exact.resY.sv,"../Results/Ensembles/atp22_co(oaf)")
```

```{r}
# in h2h/co datasets, p1 is always the winner
wta.co$w_total_pts_served <- wta.co$grass_pts_served1 + 
  wta.co$hard_pts_served1 + wta.co$clay_pts_served1
wta.co$w_total_service_pts_won <- wta.co$grass_service_pts_won1 +
  wta.co$hard_service_pts_won1 + wta.co$clay_service_pts_won1
wta.co$w_p <- wta.co$w_total_service_pts_won/wta.co$w_total_pts_served
wta.co$l_total_pts_served <- wta.co$grass_pts_served2 + 
  wta.co$hard_pts_served2 + wta.co$clay_pts_served2
wta.co$l_total_service_pts_won <- wta.co$grass_service_pts_won2 +
  wta.co$hard_service_pts_won2 + wta.co$clay_service_pts_won2
wta.co$l_p <- wta.co$l_total_service_pts_won/wta.co$l_total_pts_served

wta.co$w_total_pts_received <- wta.co$grass_pts_received1 + 
  wta.co$hard_pts_received1 + wta.co$clay_pts_received1
wta.co$w_total_receiving_pts_won <- wta.co$grass_receiving_pts_won1 +
  wta.co$hard_receiving_pts_won1 + wta.co$clay_receiving_pts_won1
wta.co$w_q <- wta.co$w_total_receiving_pts_won/wta.co$w_total_pts_received
wta.co$l_total_pts_received <- wta.co$grass_pts_received2 + 
  wta.co$hard_pts_received2 + wta.co$clay_pts_received2
wta.co$l_total_receiving_pts_won <- wta.co$grass_receiving_pts_won2 +
  wta.co$hard_receiving_pts_won2 + wta.co$clay_receiving_pts_won2
wta.co$l_q <- wta.co$l_total_receiving_pts_won/wta.co$l_total_pts_received
q.bar <- mean(c(wta.co$w_q[which(!is.na(wta.co$w_q))],
                wta.co$l_q[which(!is.na(wta.co$l_q))]))
# For CO(OAF) already dealing with incomplete coverage,
# no further imputation needed

co.valid <- which(!is.na(wta.co$w_p) & !is.na(wta.co$l_p))
resX <- rep(0,length(co.valid))
exact.resX <- rep(0,length(co.valid))
for (i in 1:length(co.valid)){
  exact.resX[i] <- get.prob.post.2022(wta.co$w_p[co.valid[i]]-(wta.co$l_q[co.valid[i]]-q.bar),
                                      wta.co$l_p[co.valid[i]]-(wta.co$w_q[co.valid[i]]-q.bar),
                                      wta.test$tourney_name[co.valid[i]])
  resX[i] <- exact.resX[i] > 0.5
}
mean(resX)
```

WTA 2014 (0.6484258) / WTA 2018 (0.6129032) / WTA 2022 (0.6102362)

```{r}
resX.sv <- rep(-1,nrow(wta.test))
resX.sv[co.valid] <- resX
exact.resX.sv <- rep(-1,nrow(wta.test))
exact.resX.sv[co.valid] <- exact.resX
saveRDS(resX.sv,"../Results/Ensembles/wta22_co(oaf)_binary")
saveRDS(exact.resX.sv,"../Results/Ensembles/wta22_co(oaf)")
```

### Below may move to surface/time horizon notebook later

### Common Opponents (Surface Filter to Opponent List Only)

```{r}
atp.co$w_p_2nsf <- atp.co$co2nsf_service_pts_won1/atp.co$co2nsf_pts_served1
atp.co$l_p_2nsf <- atp.co$co2nsf_service_pts_won2/atp.co$co2nsf_pts_served2
# first see accuracy for entries where co data is available
co.valid <- which(!is.na(atp.co$w_p_2nsf) & !is.na(atp.co$l_p_2nsf))
res9 <- rep(0,length(co.valid))
# exact.res7 <- rep(0,length(co.valid))
for (i in 1:length(co.valid)){
  res9[i] <- atp.co$w_p_2nsf[co.valid[i]] > atp.co$l_p_2nsf[co.valid[i]]
  # exact.res7[i] <- get.prob.post.2022(atp.co$w_p[co.valid[i]],atp.co$l_p[co.valid[i]],
  #                                     atp.test$tourney_name[co.valid[i]],atp=TRUE)
}
mean(res9)
```

ATP 2022 (0.6042155) / ATP 2018 (0.620985) / ATP 2014 (0.631068)

```{r}
wta.co$w_p_2nsf <- wta.co$co2nsf_service_pts_won1/wta.co$co2nsf_pts_served1
wta.co$l_p_2nsf <- wta.co$co2nsf_service_pts_won2/wta.co$co2nsf_pts_served2
# first see accuracy for entries where co data is available
co.valid <- which(!is.na(wta.co$w_p_2nsf) & !is.na(wta.co$l_p_2nsf))
res10 <- rep(0,length(co.valid))
# exact.res7 <- rep(0,length(co.valid))
for (i in 1:length(co.valid)){
  res10[i] <- wta.co$w_p_2nsf[co.valid[i]] > wta.co$l_p_2nsf[co.valid[i]]
  # exact.res7[i] <- get.prob.post.2022(wta.co$w_p[co.valid[i]],wta.co$l_p[co.valid[i]],
  #                                     wta.test$tourney_name[co.valid[i]])
}
mean(res10)
```

WTA 2022 (0.5740561) / WTA 2018 (0.5733445) / WTA 2014 (0.6214286)

### Common Opponents (Surface Filtered to All)

```{r}
atp.co$w_p_2 <- atp.co$co2_service_pts_won1/atp.co$co2_pts_served1
atp.co$l_p_2 <- atp.co$co2_service_pts_won2/atp.co$co2_pts_served2
# first see accuracy for entries where co data is available
co.valid <- which(!is.na(atp.co$w_p_2) & !is.na(atp.co$l_p_2))
res11 <- rep(0,length(co.valid))
for (i in 1:length(co.valid)){
  res11[i] <- atp.co$w_p_2[co.valid[i]] > atp.co$l_p_2[co.valid[i]]
}
mean(res11)
```

ATP 2022 (0.6049238) / ATP 2018 (0.6199143) / ATP 2014 (0.6245955)

```{r}
wta.co$w_p_2 <- wta.co$co2_service_pts_won1/wta.co$co2_pts_served1
wta.co$l_p_2 <- wta.co$co2_service_pts_won2/wta.co$co2_pts_served2
# first see accuracy for entries where co data is available
co.valid <- which(!is.na(wta.co$w_p_2) & !is.na(wta.co$l_p_2))
res12 <- rep(0,length(co.valid))
for (i in 1:length(co.valid)){
  res12[i] <- wta.co$w_p_2[co.valid[i]] > wta.co$l_p_2[co.valid[i]]
}
mean(res12)
```

WTA 2022 (0.5650485) / WTA 2018 (0.5759866) / WTA 2014 (0.618231)
