---
title: "Individual Methodologies"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

get.time function also has pre/post 2022 versions.

```{r}
source("2_2_hierarchical_model_durations.R")
grand.slams <- c("Australian Open","Roland Garros","Wimbledon","Us Open","US Open")
get.time.pre.2022 <- function(p1,p2,match,mu,atp=TRUE){
  if (is.na(p1)||is.na(p2)){
    return(NA)
  }
  if (match %in% grand.slams){
    if (match=="US Open"||match=="Us Open"){
      ret <- match.duration.nonpw(p1,p2,mu,format=0+atp)
    } else {
      ret <- match.duration.nonpw(p1,p2,mu,format=4+atp)
    }
  } else {
    ret <- match.duration.nonpw(p1,p2,mu,format=0)
  }
  return(ret)
}
get.time.post.2022 <- function(p1,p2,match,mu,atp=TRUE){
  if (is.na(p1)||is.na(p2)){
    return(NA)
  }
  if (match %in% grand.slams){
    ret <- match.duration.nonpw(p1,p2,mu,format=2+atp)
  } else {
    ret <- match.duration.nonpw(p1,p2,mu,format=0)
  }
  return(ret)
}
```

## Data

Obtained in 1_3:

ATP 2011-2013: 0.5753121363701876

ATP 2015-2017: 0.5586784508135149, WTA 2015-2017: 0.581537649060811

ATP 2019-2021: 0.6354581848475032, WTA 2019-2021: 0.588497149403478

```{r}
mu.atp <- 0.6354581848475032
mu.wta <- 0.588497149403478
```

```{r}
# testing data
# if Error: no more error handlers available (recursive errors?); invoking 'abort' restart
# Warning: type 29 is unimplemented in 'type2char'Error in pmatch(rw, c("read", "write"), 0L) : 
# INTEGER() can only be applied to a 'integer', not a 'unknown type #29'
# just run again
atp.test <- read.csv('../New Data/atp/atp_testing_2022.csv')
wta.test <- read.csv('../New Data/wta/wta_testing_2022.csv')
```
```{r}
# following function highlights matches that were incomplete
# this is determined by if the score has letters ("W/O","Def.","RET" etc.)
# takes as input the score column of a dataset and returns indexes
ic.match <- function(score) grep("[A-Za-z]",score)
ic.atp <- ic.match(atp.test$score)
ic.wta <- ic.match(wta.test$score)
```
```{r}
# training data
atp.basic <- read.csv('../New Data/atp/2019-2021_atp_individual.csv')
wta.basic <- read.csv('../New Data/wta/2019-2021_wta_individual.csv')
atp.h2h <- read.csv('../New Data/atp/2019-2021_atp_h2h.csv')
wta.h2h <- read.csv('../New Data/wta/2019-2021_wta_h2h.csv')
atp.co <- read.csv('../New Data/atp/2019-2021_atp_co.csv')
wta.co <- read.csv('../New Data/wta/2019-2021_wta_co.csv')
# for the match specific datasets, they also need ic entries removed
atp.h2h <- atp.h2h[-ic.atp,]
wta.h2h <- wta.h2h[-ic.wta,]
atp.co <- atp.co[-ic.atp,]
wta.co <- wta.co[-ic.wta,]
# remove incomplete matches for test sets
atp.test <- atp.test[-ic.atp,]
wta.test <- wta.test[-ic.wta,]
# reset indices after row removals
row.names(atp.h2h) <- NULL
row.names(atp.co) <- NULL
row.names(wta.h2h) <- NULL
row.names(wta.co) <- NULL
row.names(atp.test) <- NULL
row.names(wta.test) <- NULL
```

Testing set sizes: ATP 2022 (1220) / WTA 2022 (1371) / ATP 2018 (1304) / WTA 2018 (1457) / ATP 2014 (1330) / WTA 2014 (1467)

## Individual Methods

### Basic

```{r}
# augmentations to training set
atp.basic$total_pts_served <- atp.basic$grass_pts_served + 
  atp.basic$clay_pts_served + atp.basic$hard_pts_served
atp.basic$total_service_pts_won <- atp.basic$grass_service_pts_won +
  atp.basic$hard_service_pts_won + atp.basic$clay_service_pts_won
atp.basic$p.estimate <- atp.basic$total_service_pts_won/atp.basic$total_pts_served
# since using id's we have all players, most have NA p estimates
# plug in average of other p's
atp.basic$p.estimate[which(is.na(atp.basic$p.estimate))] <-
  mean(atp.basic$p.estimate[-which(is.na(atp.basic$p.estimate))])

wta.basic$total_pts_served <- wta.basic$grass_pts_served + 
  wta.basic$clay_pts_served + wta.basic$hard_pts_served
wta.basic$total_service_pts_won <- wta.basic$grass_service_pts_won +
  wta.basic$hard_service_pts_won + wta.basic$clay_service_pts_won
wta.basic$p.estimate <- wta.basic$total_service_pts_won/wta.basic$total_pts_served
# since using id's we have all players, most have NA p estimates
# plug in average of other p's
wta.basic$p.estimate[which(is.na(wta.basic$p.estimate))] <-
  mean(wta.basic$p.estimate[-which(is.na(wta.basic$p.estimate))])
```

Plug in values: ATP 2022 (0.595843) / WTA 2022 (0.5227285) / ATP 2018 (0.5921587) / WTA 2018 (0.5178595) / ATP 2014 (0.585246) / WTA 2014 (0.5145110)

```{r}
n <- nrow(atp.test)
sse <- 0
n.tot <- n
res1 <- rep(0,n)
for (i in 1:n){
  winner <- atp.test$winner_id[i]
  loser <- atp.test$loser_id[i]
  winner.idx <- which(atp.basic$player_id==winner)
  loser.idx <- which(atp.basic$player_id==loser)
  res1[i] <- get.time.post.2022(atp.basic$p.estimate[winner.idx],
                               atp.basic$p.estimate[loser.idx],
                               atp.test$tourney_name[i],
                               mu=mu.atp,atp=TRUE)
  if (is.na(atp.test$minutes[i])){
    n.tot <- n.tot-1
  } else {
    sse <- sse + (atp.test$minutes[i]-res1[i])^2
  }
}
saveRDS(res1,"../Results/Individual/t_atp22_basic")
sqrt(sse/n.tot)
```

ATP 2014 (42.83261) / ATP 2018 (43.18453) / ATP 2022 (45.13423)
N: 1044 / 1283 / 957

```{r}
n <- nrow(wta.test)
sse <- 0
n.tot <- n
res2 <- rep(0,n)
for (i in 1:n){
  winner <- wta.test$winner_id[i]
  loser <- wta.test$loser_id[i]
  winner.idx <- which(wta.basic$player_id==winner)
  loser.idx <- which(wta.basic$player_id==loser)
  res2[i] <- get.time.post.2022(wta.basic$p.estimate[winner.idx],
                               wta.basic$p.estimate[loser.idx],
                               wta.test$tourney_name[i],
                               mu=mu.wta,atp=FALSE)
  if (is.na(wta.test$minutes[i])){
    n.tot <- n.tot-1
  } else {
    sse <- sse + (wta.test$minutes[i]-res2[i])^2
  }
}
saveRDS(res2,"../Results/Individual/t_wta22_basic")
sqrt(sse/n.tot)
```

WTA 2014 (NULL) / WTA 2018 (49.37423) / WTA 2022 (33.01183)
N: NA / 1457 / 1251

### Opponent-Adjusted Formula

```{r}
# same augmentation as [1]
# augmentations to training set
# reload set after experiment
atp.basic$total_pts_served <- atp.basic$grass_pts_served + 
  atp.basic$clay_pts_served + atp.basic$hard_pts_served
atp.basic$total_service_pts_won <- atp.basic$grass_service_pts_won +
  atp.basic$hard_service_pts_won + atp.basic$clay_service_pts_won
atp.basic$p.estimate <- atp.basic$total_service_pts_won/atp.basic$total_pts_served
atp.basic$p.estimate[which(is.na(atp.basic$p.estimate))] <-
  mean(atp.basic$p.estimate[-which(is.na(atp.basic$p.estimate))])
# get q estimates as well
atp.basic$total_pts_received <- atp.basic$grass_pts_received +
  atp.basic$hard_pts_received + atp.basic$clay_pts_received
atp.basic$total_receiving_pts_won <- atp.basic$grass_receiving_pts_won +
  atp.basic$hard_receiving_pts_won + atp.basic$clay_receiving_pts_won
atp.basic$q.estimate <- atp.basic$total_receiving_pts_won/atp.basic$total_pts_received
q.bar <- mean(atp.basic$q.estimate[-which(is.na(atp.basic$q.estimate))])
atp.basic$q.estimate[which(is.na(atp.basic$q.estimate))] <- q.bar

n <- nrow(atp.test)
n.tot <- n
sse <- 0
res3 <- rep(0,n)
for (i in 1:n){
  winner <- atp.test$winner_id[i]
  loser <- atp.test$loser_id[i]
  winner.idx <- which(atp.basic$player_id==winner)
  loser.idx <- which(atp.basic$player_id==loser)
  winner.adj.p <- atp.basic$p.estimate[winner.idx]-(atp.basic$q.estimate[loser.idx]-q.bar)
  loser.adj.p <- atp.basic$p.estimate[loser.idx]-(atp.basic$q.estimate[winner.idx]-q.bar)
  res3[i] <- get.time.post.2022(winner.adj.p,loser.adj.p,atp.test$tourney_name[i],
                               mu.atp,atp=TRUE)
  if (is.na(atp.test$minutes[i])){
    n.tot <- n.tot-1
  } else {
    sse <- sse + (atp.test$minutes[i]-res3[i])^2
  }
}
saveRDS(res3,"../Results/Individual/t_atp22_oaf")
sqrt(sse/n.tot)
```

ATP 2014 (40.92694) / ATP 2018 (42.71323) / ATP 2022 (44.65613)
N: 1044 / 1283 / 957

```{r}
# same augmentation as [1]
# augmentations to training set
# reload set after experiment
wta.basic$total_pts_served <- wta.basic$grass_pts_served + 
  wta.basic$clay_pts_served + wta.basic$hard_pts_served
wta.basic$total_service_pts_won <- wta.basic$grass_service_pts_won +
  wta.basic$hard_service_pts_won + wta.basic$clay_service_pts_won
wta.basic$p.estimate <- wta.basic$total_service_pts_won/wta.basic$total_pts_served
wta.basic$p.estimate[which(is.na(wta.basic$p.estimate))] <-
  mean(wta.basic$p.estimate[-which(is.na(wta.basic$p.estimate))])
# get q estimates as well
wta.basic$total_pts_received <- wta.basic$grass_pts_received +
  wta.basic$hard_pts_received + wta.basic$clay_pts_received
wta.basic$total_receiving_pts_won <- wta.basic$grass_receiving_pts_won +
  wta.basic$hard_receiving_pts_won + wta.basic$clay_receiving_pts_won
wta.basic$q.estimate <- wta.basic$total_receiving_pts_won/wta.basic$total_pts_received
q.bar <-  mean(wta.basic$q.estimate[-which(is.na(wta.basic$q.estimate))])
wta.basic$q.estimate[which(is.na(wta.basic$q.estimate))] <- q.bar

n <- nrow(wta.test)
n.tot <- n
sse <- 0
res4 <- rep(0,n)
for (i in 1:n){
  winner <- wta.test$winner_id[i]
  loser <- wta.test$loser_id[i]
  winner.idx <- which(wta.basic$player_id==winner)
  loser.idx <- which(wta.basic$player_id==loser)
  winner.adj.p <- wta.basic$p.estimate[winner.idx]-(wta.basic$q.estimate[loser.idx]-q.bar)
  loser.adj.p <- wta.basic$p.estimate[loser.idx]-(wta.basic$q.estimate[winner.idx]-q.bar)
  res4[i] <- get.time.post.2022(winner.adj.p,loser.adj.p,wta.test$tourney_name[i],
                               mu.wta,atp=FALSE)
  if (is.na(wta.test$minutes[i])){
    n.tot <- n.tot-1
  } else {
    sse <- sse + (wta.test$minutes[i]-res4[i])^2
  }
}
saveRDS(res4,"../Results/Individual/t_wta22_oaf")
sqrt(sse/n.tot)
```

WTA 2014 (NULL) / WTA 2018 (49.09437) / WTA 2022 (33.07469)
N: NA / 1457 / 1251

### Head-to-Head

```{r}
# in h2h/co datasets, p1 is always the winner
atp.h2h$w_total_pts_served <- atp.h2h$grass_pts_served1 + 
  atp.h2h$hard_pts_served1 + atp.h2h$clay_pts_served1
atp.h2h$w_total_service_pts_won <- atp.h2h$grass_service_pts_won1 +
  atp.h2h$hard_service_pts_won1 + atp.h2h$clay_service_pts_won1
atp.h2h$w_p <- atp.h2h$w_total_service_pts_won/atp.h2h$w_total_pts_served
atp.h2h$l_total_pts_served <- atp.h2h$grass_pts_served2 + 
  atp.h2h$hard_pts_served2 + atp.h2h$clay_pts_served2
atp.h2h$l_total_service_pts_won <- atp.h2h$grass_service_pts_won2 +
  atp.h2h$hard_service_pts_won2 + atp.h2h$clay_service_pts_won2
atp.h2h$l_p <- atp.h2h$l_total_service_pts_won/atp.h2h$l_total_pts_served
# first see accuracy for entries where h2h data is available
h2h.valid <- which(!is.na(atp.h2h$w_p)) #l_p also works
res5 <- rep(0,length(h2h.valid))
n.tot <- length(h2h.valid)
sse <- 0
for (i in 1:length(h2h.valid)){
  res5[i] <- get.time.post.2022(atp.h2h$w_p[h2h.valid[i]],
                               atp.h2h$l_p[h2h.valid[i]],
                               atp.test$tourney_name[h2h.valid[i]],
                               mu.atp,atp=TRUE)
  if (is.na(atp.test$minutes[h2h.valid[i]])){
    n.tot <- n.tot-1
  } else {
    sse <- sse + (atp.test$minutes[h2h.valid[i]]-res5[i])^2
  }
}
res5.sv <- rep(-1,nrow(atp.test))
res5.sv[h2h.valid] <- res5
saveRDS(res5.sv,"../Results/Individual/t_atp22_h2h")
sqrt(sse/n.tot)
```
ATP 2014 (40.73772) / ATP 2018 (46.78802) / ATP 2022 (46.22931)
N: 502 / 519 / 402

```{r}
# in h2h/co datasets, p1 is always the winner
wta.h2h$w_total_pts_served <- wta.h2h$grass_pts_served1 + 
  wta.h2h$hard_pts_served1 + wta.h2h$clay_pts_served1
wta.h2h$w_total_service_pts_won <- wta.h2h$grass_service_pts_won1 +
  wta.h2h$hard_service_pts_won1 + wta.h2h$clay_service_pts_won1
wta.h2h$w_p <- wta.h2h$w_total_service_pts_won/wta.h2h$w_total_pts_served
wta.h2h$l_total_pts_served <- wta.h2h$grass_pts_served2 + 
  wta.h2h$hard_pts_served2 + wta.h2h$clay_pts_served2
wta.h2h$l_total_service_pts_won <- wta.h2h$grass_service_pts_won2 +
  wta.h2h$hard_service_pts_won2 + wta.h2h$clay_service_pts_won2
wta.h2h$l_p <- wta.h2h$l_total_service_pts_won/wta.h2h$l_total_pts_served
# first see accuracy for entries where h2h data is available
h2h.valid <- which(!is.na(wta.h2h$w_p)) #l_p also works
res6 <- rep(0,length(h2h.valid))
n.tot <- length(h2h.valid)
sse <- 0

for (i in 1:length(h2h.valid)){
  res6[i] <- get.time.post.2022(wta.h2h$w_p[h2h.valid[i]],
                               wta.h2h$l_p[h2h.valid[i]],
                               wta.test$tourney_name[h2h.valid[i]],
                               mu.wta,atp=FALSE)
  if (is.na(wta.test$minutes[h2h.valid[i]])){
    n.tot <- n.tot-1
  } else {
    sse <- sse + (wta.test$minutes[h2h.valid[i]]-res6[i])^2
  }
}
res6.sv <- rep(-1,nrow(wta.test))
res6.sv[h2h.valid] <- res6
saveRDS(res6.sv,"../Results/Individual/t_wta22_h2h")
sqrt(sse/n.tot)
```

WTA 2014 (NULL) / WTA 2018 (64.90247) / WTA 2022 (34.18973)
N: NA / 645 / 471

### Common Opponents (No Surface Filtering)

```{r}
# in h2h/co datasets, p1 is always the winner
atp.co$w_total_pts_served <- atp.co$grass_pts_served1 + 
  atp.co$hard_pts_served1 + atp.co$clay_pts_served1
atp.co$w_total_service_pts_won <- atp.co$grass_service_pts_won1 +
  atp.co$hard_service_pts_won1 + atp.co$clay_service_pts_won1
atp.co$w_p <- atp.co$w_total_service_pts_won/atp.co$w_total_pts_served
atp.co$l_total_pts_served <- atp.co$grass_pts_served2 + 
  atp.co$hard_pts_served2 + atp.co$clay_pts_served2
atp.co$l_total_service_pts_won <- atp.co$grass_service_pts_won2 +
  atp.co$hard_service_pts_won2 + atp.co$clay_service_pts_won2
atp.co$l_p <- atp.co$l_total_service_pts_won/atp.co$l_total_pts_served
# first see accuracy for entries where co data is available
co.valid <- which(!is.na(atp.co$w_p) & !is.na(atp.co$l_p))
res7 <- rep(0,length(co.valid))
sse <- 0
n.tot <- length(co.valid)
for (i in 1:length(co.valid)){
  res7[i] <- get.time.post.2022(atp.co$w_p[co.valid[i]],
                               atp.co$l_p[co.valid[i]],
                               atp.test$tourney_name[co.valid[i]],
                               mu.atp,atp=TRUE)
  if (is.na(atp.test$minutes[co.valid[i]])){
    n.tot <- n.tot-1
  } else {
    sse <- sse + (atp.test$minutes[co.valid[i]]-res7[i])^2
  }
}
res7.sv <- rep(-1,nrow(atp.test))
res7.sv[co.valid] <- res7
saveRDS(res7.sv,"../Results/Individual/t_atp22_co")
sqrt(sse/n.tot)
```

ATP 2014 (42.1763) / ATP 2018 (43.56084) / ATP 2022 (44.83542)
N: 974 / 1079 / 862

```{r}
# in h2h/co datasets, p1 is always the winner
wta.co$w_total_pts_served <- wta.co$grass_pts_served1 + 
  wta.co$hard_pts_served1 + wta.co$clay_pts_served1
wta.co$w_total_service_pts_won <- wta.co$grass_service_pts_won1 +
  wta.co$hard_service_pts_won1 + wta.co$clay_service_pts_won1
wta.co$w_p <- wta.co$w_total_service_pts_won/wta.co$w_total_pts_served
wta.co$l_total_pts_served <- wta.co$grass_pts_served2 + 
  wta.co$hard_pts_served2 + wta.co$clay_pts_served2
wta.co$l_total_service_pts_won <- wta.co$grass_service_pts_won2 +
  wta.co$hard_service_pts_won2 + wta.co$clay_service_pts_won2
wta.co$l_p <- wta.co$l_total_service_pts_won/wta.co$l_total_pts_served
# first see accuracy for entries where co data is available
co.valid <- which(!is.na(wta.co$w_p) & !is.na(wta.co$l_p))
res8 <- rep(0,length(co.valid))
n.tot <- length(co.valid)
sse <- 0
for (i in 1:length(co.valid)){
  res8[i] <- get.time.post.2022(wta.co$w_p[co.valid[i]],
                               wta.co$l_p[co.valid[i]],
                               wta.test$tourney_name[co.valid[i]],
                               mu.wta,atp=FALSE)
  if (is.na(wta.test$minutes[co.valid[i]])){
    n.tot <- n.tot-1
  } else {
    sse <- sse + (wta.test$minutes[co.valid[i]]-res8[i])^2
  }
}
res8.sv <- rep(-1,nrow(wta.test))
res8.sv[co.valid] <- res8
saveRDS(res8.sv,"../Results/Individual/t_wta22_co")
sqrt(sse/n.tot)
```

WTA 2014 (NULL) / WTA 2018 (50.28881) / WTA 2022 (32.77271)
N: NA / 1364 / 1163

### Common Opponents with Opponent-Adjusted Formula

```{r}
# in h2h/co datasets, p1 is always the winner
atp.co$w_total_pts_served <- atp.co$grass_pts_served1 + 
  atp.co$hard_pts_served1 + atp.co$clay_pts_served1
atp.co$w_total_service_pts_won <- atp.co$grass_service_pts_won1 +
  atp.co$hard_service_pts_won1 + atp.co$clay_service_pts_won1
atp.co$w_p <- atp.co$w_total_service_pts_won/atp.co$w_total_pts_served
atp.co$l_total_pts_served <- atp.co$grass_pts_served2 + 
  atp.co$hard_pts_served2 + atp.co$clay_pts_served2
atp.co$l_total_service_pts_won <- atp.co$grass_service_pts_won2 +
  atp.co$hard_service_pts_won2 + atp.co$clay_service_pts_won2
atp.co$l_p <- atp.co$l_total_service_pts_won/atp.co$l_total_pts_served

atp.co$w_total_pts_received <- atp.co$grass_pts_received1 + 
  atp.co$hard_pts_received1 + atp.co$clay_pts_received1
atp.co$w_total_receiving_pts_won <- atp.co$grass_receiving_pts_won1 +
  atp.co$hard_receiving_pts_won1 + atp.co$clay_receiving_pts_won1
atp.co$w_q <- atp.co$w_total_receiving_pts_won/atp.co$w_total_pts_received
atp.co$l_total_pts_received <- atp.co$grass_pts_received2 + 
  atp.co$hard_pts_received2 + atp.co$clay_pts_received2
atp.co$l_total_receiving_pts_won <- atp.co$grass_receiving_pts_won2 +
  atp.co$hard_receiving_pts_won2 + atp.co$clay_receiving_pts_won2
atp.co$l_q <- atp.co$l_total_receiving_pts_won/atp.co$l_total_pts_received
q.bar <- mean(c(atp.co$w_q[which(!is.na(atp.co$w_q))],
                atp.co$l_q[which(!is.na(atp.co$l_q))]))
# For CO(OAF) already dealing with incomplete coverage,
# no further imputation needed

co.valid <- which(!is.na(atp.co$w_p) & !is.na(atp.co$l_p))
resY <- rep(0,length(co.valid))
sse <- 0
n.tot <- length(co.valid)

for (i in 1:length(co.valid)){
  resY[i] <- get.time.post.2022(atp.co$w_p[co.valid[i]]-(atp.co$l_q[co.valid[i]]-q.bar),
                               atp.co$l_p[co.valid[i]]-(atp.co$w_q[co.valid[i]]-q.bar),
                               atp.test$tourney_name[co.valid[i]],
                               mu.atp,atp=TRUE)
  if (is.na(atp.test$minutes[co.valid[i]])){
    n.tot <- n.tot-1
  } else {
    sse <- sse + (atp.test$minutes[co.valid[i]]-resY[i])^2
  }
}
resY.sv <- rep(-1,nrow(atp.test))
resY.sv[co.valid] <- resY
saveRDS(resY.sv,"../Results/Individual/t_atp22_co(oaf)")
sqrt(sse/n.tot)
```

ATP 2014 (40.77502) / ATP 2018 (43.04233) / ATP 2022 (44.14911)
N: 974 / 1079 / 862


```{r}
# in h2h/co datasets, p1 is always the winner
wta.co$w_total_pts_served <- wta.co$grass_pts_served1 + 
  wta.co$hard_pts_served1 + wta.co$clay_pts_served1
wta.co$w_total_service_pts_won <- wta.co$grass_service_pts_won1 +
  wta.co$hard_service_pts_won1 + wta.co$clay_service_pts_won1
wta.co$w_p <- wta.co$w_total_service_pts_won/wta.co$w_total_pts_served
wta.co$l_total_pts_served <- wta.co$grass_pts_served2 + 
  wta.co$hard_pts_served2 + wta.co$clay_pts_served2
wta.co$l_total_service_pts_won <- wta.co$grass_service_pts_won2 +
  wta.co$hard_service_pts_won2 + wta.co$clay_service_pts_won2
wta.co$l_p <- wta.co$l_total_service_pts_won/wta.co$l_total_pts_served

wta.co$w_total_pts_received <- wta.co$grass_pts_received1 + 
  wta.co$hard_pts_received1 + wta.co$clay_pts_received1
wta.co$w_total_receiving_pts_won <- wta.co$grass_receiving_pts_won1 +
  wta.co$hard_receiving_pts_won1 + wta.co$clay_receiving_pts_won1
wta.co$w_q <- wta.co$w_total_receiving_pts_won/wta.co$w_total_pts_received
wta.co$l_total_pts_received <- wta.co$grass_pts_received2 + 
  wta.co$hard_pts_received2 + wta.co$clay_pts_received2
wta.co$l_total_receiving_pts_won <- wta.co$grass_receiving_pts_won2 +
  wta.co$hard_receiving_pts_won2 + wta.co$clay_receiving_pts_won2
wta.co$l_q <- wta.co$l_total_receiving_pts_won/wta.co$l_total_pts_received
q.bar <- mean(c(wta.co$w_q[which(!is.na(wta.co$w_q))],
                wta.co$l_q[which(!is.na(wta.co$l_q))]))
# For CO(OAF) already dealing with incomplete coverage,
# no further imputation needed

co.valid <- which(!is.na(wta.co$w_p) & !is.na(wta.co$l_p))
resX <- rep(0,length(co.valid))
sse <- 0
n.tot <- length(co.valid)

for (i in 1:length(co.valid)){
  resX[i] <- get.time.post.2022(wta.co$w_p[co.valid[i]]-(wta.co$l_q[co.valid[i]]-q.bar),
                               wta.co$l_p[co.valid[i]]-(wta.co$w_q[co.valid[i]]-q.bar),
                               wta.test$tourney_name[co.valid[i]],
                               mu.wta,atp=FALSE)
  if (is.na(wta.test$minutes[co.valid[i]])){
    n.tot <- n.tot-1
  } else {
    sse <- sse + (wta.test$minutes[co.valid[i]]-resX[i])^2
  }
}
resX.sv <- rep(-1,nrow(wta.test))
resX.sv[co.valid] <- resX
saveRDS(resX.sv,"../Results/Individual/t_wta22_co(oaf)")
sqrt(sse/n.tot)
```

WTA 2014 (NULL) / WTA 2018 (50.09044) / WTA 2022 (33.43789)
N: NA / 1364 / 1163

## Hypothesis Testing w/ Basic Baseline

```{r}
# SIGNIFICANCE TEST CODE
# two sample student t to compare two means
basic.atp <- readRDS("../Results/Individual/t_atp22_basic")
oaf.atp <- readRDS("../Results/Individual/t_atp22_oaf")
h2h.atp <- readRDS("../Results/Individual/t_atp22_h2h")
co.atp <- readRDS("../Results/Individual/t_atp22_co")
cooaf.atp <- readRDS("../Results/Individual/t_atp22_co(oaf)")
ind.atp <- which(!is.na(atp.test$minutes))
basic.wta <- readRDS("../Results/Individual/t_wta22_basic")
oaf.wta <- readRDS("../Results/Individual/t_wta22_oaf")
h2h.wta <- readRDS("../Results/Individual/t_wta22_h2h")
co.wta <- readRDS("../Results/Individual/t_wta22_co")
cooaf.wta <- readRDS("../Results/Individual/t_wta22_co(oaf)")
ind.wta <- which(!is.na(wta.test$minutes))
```

```{r}
# OAF
t.test(((basic.atp-atp.test$minutes)^2)[ind.atp],((oaf.atp-atp.test$minutes)^2)[ind.atp],
       var.equal=TRUE,alternative="greater")$p.value
# added to see if overall we're overestimating or underestimating
summary((oaf.atp-atp.test$minutes)[ind.atp]) # overall leaning towards overestimating
```
Leans towards: over / over / over

```{r}
h2h.atp <- h2h.atp[ind.atp]
h2h.test <- atp.test$minutes[ind.atp]
h2h.test <- h2h.test[which(h2h.atp>0)]
h2h.atp <- h2h.atp[which(h2h.atp>0)]
t.test(((basic.atp-atp.test$minutes)^2)[ind.atp],
       (h2h.atp-h2h.test)^2,
       var.equal=TRUE,alternative="greater")$p.value
# added to see if overall we're overestimating or underestimating
summary(h2h.atp-h2h.test) # slightly underestimating overall
```
Leans towards: over / under / under

```{r}
co.atp <- co.atp[ind.atp]
co.test <- atp.test$minutes[ind.atp]
co.test <- co.test[which(co.atp>0)]
co.atp <- co.atp[which(co.atp>0)]
t.test(((basic.atp-atp.test$minutes)^2)[ind.atp],
       (co.atp-co.test)^2,
       var.equal=TRUE,alternative="greater")$p.value
# added to see if overall we're overestimating or underestimating
summary(co.atp-co.test) # slightly overestimating overall
```
Leans towards: over / over / over

```{r}
cooaf.atp <- cooaf.atp[ind.atp]
cooaf.test <- atp.test$minutes[ind.atp]
cooaf.test <- cooaf.test[which(cooaf.atp>0)]
cooaf.atp <- cooaf.atp[which(cooaf.atp>0)]
t.test(((basic.atp-atp.test$minutes)^2)[ind.atp],
       (cooaf.atp-cooaf.test)^2,
       var.equal=TRUE,alternative="greater")$p.value
# added to see if overall we're overestimating or underestimating
summary(cooaf.atp-cooaf.test) # slightly overestimating overall
```
Leans towards: over / over / over

```{r}
cooaf.atp <- readRDS("../Results/Individual/t_atp22_co(oaf)")
cooaf.atp <- cooaf.atp[ind.atp]
cooaf.test <- atp.test$minutes[ind.atp]
cooaf.test <- cooaf.test[which(cooaf.atp>0)]
cooaf.atp <- cooaf.atp[which(cooaf.atp>0)]
t.test(((oaf.atp-atp.test$minutes)^2)[ind.atp],
       (cooaf.atp-cooaf.test)^2,
       var.equal=TRUE,alternative="greater")$p.value
```

```{r}
# OAF
t.test(((basic.wta-wta.test$minutes)^2)[ind.wta],((oaf.wta-wta.test$minutes)^2)[ind.wta],
       var.equal=TRUE,alternative="greater")$p.value
# added to see if overall we're overestimating or underestimating
summary((oaf.wta-wta.test$minutes)[ind.wta]) # slightly overestimating overall
```
Leans towards: over / over

```{r}
h2h.wta <- h2h.wta[ind.wta]
h2h.test <- wta.test$minutes[ind.wta]
h2h.test <- h2h.test[which(h2h.wta>0)]
h2h.wta <- h2h.wta[which(h2h.wta>0)]
t.test(((basic.wta-wta.test$minutes)^2)[ind.wta],
       (h2h.wta-h2h.test)^2,
       var.equal=TRUE,alternative="greater")$p.value
# added to see if overall we're overestimating or underestimating
summary(h2h.wta-h2h.test) # slightly underestimating overall
```
Leans towards: median slightly over, mean more clearly under / under

```{r}
co.wta <- co.wta[ind.wta]
co.test <- wta.test$minutes[ind.wta]
co.test <- co.test[which(co.wta>0)]
co.wta <- co.wta[which(co.wta>0)]
t.test(((basic.wta-wta.test$minutes)^2)[ind.wta],
       (co.wta-co.test)^2,
       var.equal=TRUE,alternative="greater")$p.value
# added to see if overall we're overestimating or underestimating
summary(co.wta-co.test) # slightly overestimating overall
```
Leans towards: over / over

```{r}
cooaf.wta <- cooaf.wta[ind.wta]
cooaf.test <- wta.test$minutes[ind.wta]
cooaf.test <- cooaf.test[which(cooaf.wta>0)]
cooaf.wta <- cooaf.wta[which(cooaf.wta>0)]
t.test(((basic.wta-wta.test$minutes)^2)[ind.wta],
       (cooaf.wta-cooaf.test)^2,
       var.equal=TRUE,alternative="greater")$p.value
# added to see if overall we're overestimating or underestimating
summary(cooaf.wta-cooaf.test) # slightly overestimating overall
```
Leans towards: over / over

```{r}
cooaf.wta <- readRDS("../Results/Individual/t_wta22_co(oaf)")
cooaf.wta <- cooaf.wta[ind.wta]
cooaf.test <- wta.test$minutes[ind.wta]
cooaf.test <- cooaf.test[which(cooaf.wta>0)]
cooaf.wta <- cooaf.wta[which(cooaf.wta>0)]
t.test(((oaf.wta-wta.test$minutes)^2)[ind.wta],
       (cooaf.wta-cooaf.test)^2,
       var.equal=TRUE,alternative="greater")$p.value
```



