---
title: "Point Specific Durations I. Greedy for Accuracy"
output: pdf_document
date: "2024-12-18"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

When we still go after high accuracy scores with the greedy approach, the states selected for activation/deactivation will be the same as in 4_1, so we just need slightly alter some functions to work with durations to be able to activate/deactivate states to obtain new duration estimates.

```{r}
mu.atp14 <- 0.5753121363701876
mu.wta18 <- 0.581537649060811
mu.atp18 <- 0.5586784508135149
mu.wta22 <- 0.588497149403478
mu.atp22 <- 0.6354581848475032
```

# Prep Functions

```{r functions}
# main function is match.win.prob
source("2_2_hierarchical_model_durations.R")

# 3 helper functions

get.unique.players <- function(testset){
  # takes the players in the test set and returns vector
  # containing unique players in the test set
  names <- c(testset$winner_name,testset$loser_name)
  names <- unique(names)
  return(names)
}

get.equiv.names <- function(fullname){
  # returns vector of equivalent names in different formats
  # according to the fullname given
  # fullname ideally from get.unique.players output
  # More special examples:
  #   Alejandro Davidovich Fokina -> A Davidovich Fokina & A. Davidovich Fokina
  #   Pierre Hugues Herbert -> P Herbert & Ph Herbert & P. Herbert
  #   Alex De Minaur -> A. De Minaur & Alex de Minaur & A De Minaur
  #   Karolina Pliskova -> K. Pliskova & Ka. Pliskova & Ka Pliskova
  #   Kristyna Pliskova -> K. Pliskova & Kr. Pliskova & Kr Pliskova
  #   some cases manually remediated (see misc. google doc)
  #   but quick manual remediation can't help if player in test set has middle name
  #   and full name isn't in pbp training set.
  #   Function tries to account for this as follows.
  
  # Alex Bee Caine -> c("A. Caine", "A Caine", "A. Bee Caine", "A Bee Caine",
  #                     "Ab Caine", "A Bee-Caine", "A. Bee-Caine")
  
  # This method risks picking up on players with same last name and first letter
  # But this is unlikely as the pbp training set only 1 case of this - Kr&Ka Pliskova
  # And this was picked up since there were 2 characters before the space
  
  parts <- strsplit(fullname,split=" ")[[1]]
  n <- length(parts)
  first.letter <- substr(parts[1],1,1)
  equiv <- c(fullname,
             paste(first.letter," ",parts[n],sep=""),
             paste(first.letter,"."," ",parts[n],sep=""))
  if (n > 2){
    rest <- ""
    rest.dash <- ""
    for (i in 1:(n-1)){
      rest <- paste(rest," ",parts[i+1],sep="")
      rest.dash <- paste(rest.dash,parts[i+1],sep="-")
    }
    rest.dash <- substr(rest.dash,2,nchar(rest.dash)) # get rid of first dash
    first.middle.name.letter <- tolower(substr(parts[2],1,1))
    rest.more <- "" # for if the name has four or more parts
    for (i in 1:(n-2)){
      rest.more <- paste(rest.more," ",parts[i+2],sep="")
    }
    # rest contains the first space, rest.dash doesn't
    equiv <- c(equiv, paste(first.letter,rest,sep=""),
               paste(first.letter,".",rest,sep=""),
               paste(first.letter," ",rest.dash,sep=""),
               paste(first.letter,"."," ",rest.dash,sep=""),
               paste(first.letter,first.middle.name.letter,rest.more,sep=""))
  }
  return(equiv)
}

get.aggr.by.state <- function(entry){
  # extract serve won & serve total fields for a player
  # without surface distinction
  ret <- rep(0,38)
  for (i in 1:18){
    # odd indices for pts won, even for total
    ret[2*i-1] <- entry[[3+4*i]]
    ret[2*i] <- entry[[2+4*i]]
  }
  ret[37] <- entry[[3]]
  ret[38] <- entry[[2]]
  return(ret)
}

create.p.vector <- function(tst.names,pbp){
  # returns a dataframe with the rows in the order of names,
  # the columns being p's for states 1-18 and then t (tiebreak)
  # final column is overall p regardless of state by taking total won / total serve
  # names usually from get.unique.players on test data set
  # pbp is the point-by-point data given
  # note p-vectors not surface specific
  
  n <- length(tst.names)
  m <- nrow(pbp)
  pbp.name <- pbp$name
  aggr <- matrix(0,nrow=n,ncol=38) # 38=2x19, taking won & total to divide later
  for (i in 1:n){
    equiv <- get.equiv.names(tst.names[i])
    p <- length(equiv)
    for (j in 1:p){
      for (l in 1:m){
        # check 1 by 1 since pbp has non-unique names after manual remediation
        if (tolower(equiv[j])==tolower(pbp.name[l])){
          more.aggr <- get.aggr.by.state(pbp[l,])
          aggr[i,] <- aggr[i,]+more.aggr
        }
      }
    }
  }
  # now divide odd cols by even cols to obtain p's
  output <- matrix(0,nrow=n,ncol=20)
  output <- data.frame(output, row.names=tst.names)
  for (i in 1:n){
    for (j in 1:19){
      output[i,j] <- aggr[i,2*j-1]/aggr[i,2*j]
    } # note below first seq() output will end at 37
    output[i,20] <- sum(aggr[i,seq(1,38,by=2)])/sum(aggr[i,seq(2,38,by=2)])
  }
  return(output)
}

grand.slams <- c("Australian Open","Roland Garros","Wimbledon","US Open","Us Open")
get.time.pre.2022 <- function(p1,p2,match,mu,atp=TRUE){
  if (match %in% grand.slams){
    if (match=="US Open"||match=="Us Open"){
      ret <- match.duration.pw(p1,p2,mu,format=0+atp)
    } else {
      ret <- match.duration.pw(p1,p2,mu,format=4+atp)
    }
  } else {
    ret <- match.duration.pw(p1,p2,mu,format=0)
  }
  return(ret)
}
get.time.post.2022 <- function(p1,p2,match,mu,atp=TRUE){
  if (match %in% grand.slams){
    ret <- match.duration.pw(p1,p2,mu,format=2+atp)
  } else {
    ret <- match.duration.pw(p1,p2,mu,format=0)
  }
  return(ret)
}

# overall function to do experiments with
conduct.experiment <- function(inactive.states, P, test.set, mu, atp=TRUE, test.year=0){
  # inactive.states:
  #   vector containing states (19 for tiebreak) to deactivate, i.e. 
  #   replace the state's unique p with the player's overall p
  # P:
  #   data.frame containing players' individual p vectors
  #   usually obtained via create.p.vector output
  # test.set:
  #   data set used to test accuracy of prediction
  # atp:
  #   boolean defaulted to true if test.set is ATP data
  # test.year:
  #   three valid values: 0,1,2
  #   0 for up to 2018, 1 for 2019 to 2021 inclusive, 2 for 2022 beyond
  #   no testing year actually falls between 2019-2021, this new version
  #   just depreicates this, so 1 is not an actual valid input for test.year
  
  # make copy of P and change copy to align with specified inactive.states
  cP <- P[,1:19]
  cP[,inactive.states] <- P[,20]
  
  # record duration estimates
  n <- nrow(test.set)
  n.tot <- n
  exact <- rep(0,n)
  sse <- 0
  
  # experiment begins
  pbp.names <- rownames(cP)
  for (i in 1:n){
    matchup <- test.set[i,]
    winner <- matchup$winner_name
    loser <- matchup$loser_name
    inds <- match(c(winner,loser),pbp.names)
    winner.P <- unname(unlist(cP[inds[1],]))
    loser.P <- unname(unlist(cP[inds[2],]))
    if (test.year==0){
      exact[i] <- get.time.pre.2022(p1=winner.P,p2=loser.P,
                                    matchup$tourney_name,mu,atp)
    } else {
      exact[i] <- get.time.post.2022(p1=winner.P,p2=loser.P,
                                    matchup$tourney_name,mu,atp)
    }
    if (is.na(matchup$minutes)){
      n.tot <- n.tot-1
    } else {
      sse <- sse + (matchup$minutes-exact[i])^2
    }
  }
  return(list("score"=sqrt(sse/n.tot),"exact"=exact))
}

# --- below still needs to be retooled for duration

downwards.wrapper <- function(deactivate,P,testset,atp,test.year){
  # atp is boolean for if testset is for ATP
  scores <- rep(0,19)
  if (length(deactivate)==0){
    options <- 1:19
  } else {
    options <- (1:19)[-deactivate]
  }
  for (i in options){
    scores[i] <- conduct.experiment(c(i,deactivate),P,testset,atp,test.year)$score
    # so deactivated state's indices will have 0
  }
  return(list("max"=max(scores),"candidates"=which(scores==max(scores))))
}
upwards.wrapper <- function(activate,P,testset,atp,test.year){
  # atp is boolean for if testset is for ATP
  if (length(activate)==0){
    deactivate <- 1:19
  } else {
    deactivate <- (1:19)[-activate]
  }
  scores <- rep(0,19)
  for (i in deactivate){
    deactivate.no.i <- (1:19)[-c(activate,i)]
    scores[i] <- conduct.experiment(deactivate.no.i,P,testset,atp,test.year)$score
    # activated state's indices will have 0
  }
  return(list("max"=max(scores),"candidates"=which(scores==max(scores))))
}

downwards.experiment <- function(starting.states,P,testset,atp,previous.scores,
                                 depth=18,test.year=2){
  
  diverge.lists <- c()
  deactivate <- starting.states
  
  # through recursion, aim to combine all ovr.lists produced
  ovr.list <- list() # to contain lists containing state & score vectors
  path <- list()
  # if no previous scores, can initialize NULL list element for scores:
  # https://stackoverflow.com/questions/45666451/r-adding-an-empty-vector-to-a-list
  if (length(previous.scores)==0){
    path[1] <- list(NULL)
  } else {
    path[[1]] <- previous.scores # to record best scores of this path
  }
  # path[[2]] to record states deactivated, but does not need initialization
  
  while(length(deactivate) < depth){
    
    res <- downwards.wrapper(deactivate,P,testset,atp,test.year)
    score <- res$max
    cands <- res$candidates
    scores.sofar <- c(path[[1]],score)
    
    l <- length(cands)
    if (l>1){
      # recursion call
      for (i in 2:l){
        diverge.lists <- c(
          diverge.lists,
          downwards.experiment(c(deactivate,cands[i]),P,testset,atp,scores.sofar,
                               depth,test.year))
      }
    }
    path[[1]] <- scores.sofar
    deactivate <- c(deactivate,cands[1])
    path[[2]] <- deactivate
  }
  path[[2]] <- deactivate
  ovr.list[[1]] <- path
  ovr.list <- c(ovr.list,diverge.lists)
  
  return(ovr.list)
}

upwards.experiment <- function(starting.states,P,testset,atp,previous.scores,
                               depth=18,test.year=2){
  
  diverge.lists <- c()
  activate <- starting.states
  
  # through recursion, aim to combine all ovr.lists produced
  ovr.list <- list() # to contain lists containing state & score vectors
  path <- list()
  # if no previous scores, can initialize NULL list element for scores:
  # https://stackoverflow.com/questions/45666451/r-adding-an-empty-vector-to-a-list
  if (length(previous.scores)==0){
    path[1] <- list(NULL)
  } else {
    path[[1]] <- previous.scores # to record best scores of this path
  }
  # path[[2]] to record states deactivated, but does not need initialization
  
  while(length(activate) < depth){
    
    res <- upwards.wrapper(activate,P,testset,atp,test.year)
    score <- res$max
    cands <- res$candidates
    scores.sofar <- c(path[[1]],score)
    
    l <- length(cands)
    if (l>1){
      # recursion call
      for (i in 2:l){
        diverge.lists <- c(
          diverge.lists,
          upwards.experiment(c(activate,cands[i]),P,testset,atp,scores.sofar,
                             depth,test.year))
      }
    }
    path[[1]] <- scores.sofar
    activate <- c(activate,cands[1])
    path[[2]] <- activate
  }
  path[[2]] <- activate
  ovr.list[[1]] <- path
  ovr.list <- c(ovr.list,diverge.lists)
  
  return(ovr.list)
}

plot.path.score <- function(n.down,dat.down,n.up,dat.up,
                      P, test.set, atp=TRUE, main="Score",
                      ylim.lower=0.55,ylim.upper=0.7,hide.axis=FALSE,test.year=0){
  # n - length of path given
  # dat - data saved containing paths
  # ylim.lower(upper) - ylim for plot, set to around 0(20) for type=2
  
  baseline.down <- conduct.experiment(c(),P,test.set,atp,test.year)$score
  baseline.up <- conduct.experiment(1:19,P,test.set,atp,test.year)$score
  
  if (hide.axis) {
    plot(0:n.up,c(baseline.up,dat.up[[1]][[1]]),'l',
         xlim=c(0,20),ylim=c(ylim.lower,ylim.upper),main=main)
  } else {
    plot(0:n.up,c(baseline.up,dat.up[[1]][[1]]),'l',
         xlim=c(0,20),ylim=c(ylim.lower,ylim.upper),main=main,
         ylab="Score",xlab="# States Activated")
  }
  for (i in 1:length(dat.up)){
    lines(0:n.up,c(baseline.up,dat.up[[i]][[1]]))
  }
  for (i in 1:length(dat.down)){
    lines(20:(20-n.down),c(baseline.down,dat.down[[i]][[1]]))
  }
}

plot.path.state <- function(n.down,dat.down,n.up,dat.up,main="States",
                            ylim.lower=0,ylim.upper=20,hide.axis=FALSE){
  # n - length of path given
  # dat - data saved containing paths
  # ylim.lower(upper) - ylim for plot, set to around 0(20) for state
  if (hide.axis) {
    plot(1:n.up,dat.up[[1]][[2]],'l',
         xlim=c(1,19),ylim=c(ylim.lower,ylim.upper),main=main)
  } else {
    plot(1:n.up,dat.up[[1]][[2]],'l',
         xlim=c(1,19),ylim=c(ylim.lower,ylim.upper),main=main,
         ylab="States",xlab="# States Activated")
  }
  for (i in 1:length(dat.up)){
    lines(1:n.up,dat.up[[i]][[2]])
  }
  for (i in 1:length(dat.down)){
    lines(19:(20-n.down),dat.down[[i]][[2]])
  }
}
```

# Data

```{r}
# Testing data
# if Error: no more error handlers available (recursive errors?); invoking 'abort' restart
# Warning: type 29 is unimplemented in 'type2char'Error in pmatch(rw, c("read", "write"), 0L) : 
# INTEGER() can only be applied to a 'integer', not a 'unknown type #29'
# just run again
atp.test.2014 <- read.csv('../New Data/atp/atp_testing_2014.csv')
wta.test.2014 <- read.csv('../New Data/wta/wta_testing_2014.csv')
atp.test.2018 <- read.csv('../New Data/atp/atp_testing_2018.csv')
wta.test.2018 <- read.csv('../New Data/wta/wta_testing_2018.csv')
atp.test.2022 <- read.csv('../New Data/atp/atp_testing_2022.csv')
wta.test.2022 <- read.csv('../New Data/wta/wta_testing_2022.csv')
# following function highlights matches that were incomplete
# this is determined by if the score has letters ("W/O","Def.","RET" etc.)
# takes as input the score column of a dataset and returns indexes
ic.match <- function(score) grep("[A-Za-z]",score)
atp.test.2014 <- atp.test.2014[-ic.match(atp.test.2014$score),]
wta.test.2014 <- wta.test.2014[-ic.match(wta.test.2014$score),]
atp.test.2018 <- atp.test.2018[-ic.match(atp.test.2018$score),]
wta.test.2018 <- wta.test.2018[-ic.match(wta.test.2018$score),]
atp.test.2022 <- atp.test.2022[-ic.match(atp.test.2022$score),]
wta.test.2022 <- wta.test.2022[-ic.match(wta.test.2022$score),]
row.names(atp.test.2014) <- NULL
row.names(wta.test.2014) <- NULL
row.names(atp.test.2018) <- NULL
row.names(wta.test.2018) <- NULL
row.names(atp.test.2022) <- NULL
row.names(wta.test.2022) <- NULL
# Validation data
atp.val.2013 <- read.csv('../New Data/atp/atp_val_2013.csv')
wta.val.2013 <- read.csv('../New Data/wta/wta_val_2013.csv')
atp.val.2017 <- read.csv('../New Data/atp/atp_val_2017.csv')
wta.val.2017 <- read.csv('../New Data/wta/wta_val_2017.csv')
atp.val.2021 <- read.csv('../New Data/atp/atp_val_2021.csv')
wta.val.2021 <- read.csv('../New Data/wta/wta_val_2021.csv')
atp.val.2013 <- atp.val.2013[-ic.match(atp.val.2013$score),]
wta.val.2013 <- wta.val.2013[-ic.match(wta.val.2013$score),]
atp.val.2017 <- atp.val.2017[-ic.match(atp.val.2017$score),]
wta.val.2017 <- wta.val.2017[-ic.match(wta.val.2017$score),]
atp.val.2021 <- atp.val.2021[-ic.match(atp.val.2021$score),]
wta.val.2021 <- wta.val.2021[-ic.match(wta.val.2021$score),]
row.names(atp.val.2013) <- NULL
row.names(wta.val.2013) <- NULL
row.names(atp.val.2017) <- NULL
row.names(wta.val.2017) <- NULL
row.names(atp.val.2021) <- NULL
row.names(wta.val.2021) <- NULL
# Point-by-Point data
pbp.123 <- read.csv('../New Data/pbp/2011-2013_pbp_individual.csv')
pbp.567 <- read.csv('../New Data/pbp/2015-2017_pbp_individual.csv')
pbp.901 <- read.csv('../New Data/pbp/2019-2021_pbp_individual.csv')
pbp.12 <- read.csv('../New Data/pbp/2011-2012_pbp_individual.csv')
pbp.56 <- read.csv('../New Data/pbp/2015-2016_pbp_individual.csv')
pbp.90 <- read.csv('../New Data/pbp/2019-2020_pbp_individual.csv')
# Getting unique names
atp.names.2014 <- get.unique.players(atp.test.2014)
atp.names.2018 <- get.unique.players(atp.test.2018)
atp.names.2022 <- get.unique.players(atp.test.2022)
wta.names.2014 <- get.unique.players(wta.test.2014)
wta.names.2018 <- get.unique.players(wta.test.2018)
wta.names.2022 <- get.unique.players(wta.test.2022)
atp.names.2013 <- get.unique.players(atp.val.2013)
atp.names.2017 <- get.unique.players(atp.val.2017)
atp.names.2021 <- get.unique.players(atp.val.2021)
wta.names.2013 <- get.unique.players(wta.val.2013)
wta.names.2017 <- get.unique.players(wta.val.2017)
wta.names.2021 <- get.unique.players(wta.val.2021)
# create p vectors
atp.P.123.14 <- create.p.vector(atp.names.2014,pbp.123)
atp.P.567.18 <- create.p.vector(atp.names.2018,pbp.567)
atp.P.901.22 <- create.p.vector(atp.names.2022,pbp.901)
wta.P.123.14 <- create.p.vector(wta.names.2014,pbp.123)
wta.P.567.18 <- create.p.vector(wta.names.2018,pbp.567)
wta.P.901.22 <- create.p.vector(wta.names.2022,pbp.901)
atp.P.12.14 <- create.p.vector(atp.names.2014,pbp.12)
atp.P.56.18 <- create.p.vector(atp.names.2018,pbp.56)
atp.P.90.22 <- create.p.vector(atp.names.2022,pbp.90)
wta.P.12.14 <- create.p.vector(wta.names.2014,pbp.12)
wta.P.56.18 <- create.p.vector(wta.names.2018,pbp.56)
wta.P.90.22 <- create.p.vector(wta.names.2022,pbp.90)
atp.P.123.13 <- create.p.vector(atp.names.2013,pbp.123)
atp.P.567.17 <- create.p.vector(atp.names.2017,pbp.567)
atp.P.901.21 <- create.p.vector(atp.names.2021,pbp.901)
wta.P.123.13 <- create.p.vector(wta.names.2013,pbp.123)
wta.P.567.17 <- create.p.vector(wta.names.2017,pbp.567)
wta.P.901.21 <- create.p.vector(wta.names.2021,pbp.901)
atp.P.12.13 <- create.p.vector(atp.names.2013,pbp.12)
atp.P.56.17 <- create.p.vector(atp.names.2017,pbp.56)
atp.P.90.21 <- create.p.vector(atp.names.2021,pbp.90)
wta.P.12.13 <- create.p.vector(wta.names.2013,pbp.12)
wta.P.56.17 <- create.p.vector(wta.names.2017,pbp.56)
wta.P.90.21 <- create.p.vector(wta.names.2021,pbp.90)
for (i in 1:ncol(atp.P.123.14)){
  atp.P.123.14[which(is.na(atp.P.123.14[,i])),i] <- 
    mean(atp.P.123.14[-which(is.na(atp.P.123.14[,i])),i])
}
for (i in 1:ncol(atp.P.567.18)){
  atp.P.567.18[which(is.na(atp.P.567.18[,i])),i] <- 
    mean(atp.P.567.18[-which(is.na(atp.P.567.18[,i])),i])
}
for (i in 1:ncol(atp.P.901.22)){
  atp.P.901.22[which(is.na(atp.P.901.22[,i])),i] <- 
    mean(atp.P.901.22[-which(is.na(atp.P.901.22[,i])),i])
}
for (i in 1:ncol(wta.P.123.14)){
  wta.P.123.14[which(is.na(wta.P.123.14[,i])),i] <- 
    mean(wta.P.123.14[-which(is.na(wta.P.123.14[,i])),i])
}
for (i in 1:ncol(wta.P.567.18)){
  wta.P.567.18[which(is.na(wta.P.567.18[,i])),i] <- 
    mean(wta.P.567.18[-which(is.na(wta.P.567.18[,i])),i])
}
for (i in 1:ncol(wta.P.901.22)){
  wta.P.901.22[which(is.na(wta.P.901.22[,i])),i] <- 
    mean(wta.P.901.22[-which(is.na(wta.P.901.22[,i])),i])
}
for (i in 1:ncol(atp.P.12.14)){
  atp.P.12.14[which(is.na(atp.P.12.14[,i])),i] <- 
    mean(atp.P.12.14[-which(is.na(atp.P.12.14[,i])),i])
}
for (i in 1:ncol(atp.P.56.18)){
  atp.P.56.18[which(is.na(atp.P.56.18[,i])),i] <- 
    mean(atp.P.56.18[-which(is.na(atp.P.56.18[,i])),i])
}
for (i in 1:ncol(atp.P.90.22)){
  atp.P.90.22[which(is.na(atp.P.90.22[,i])),i] <- 
    mean(atp.P.90.22[-which(is.na(atp.P.90.22[,i])),i])
}
for (i in 1:ncol(wta.P.12.14)){
  wta.P.12.14[which(is.na(wta.P.12.14[,i])),i] <- 
    mean(wta.P.12.14[-which(is.na(wta.P.12.14[,i])),i])
}
for (i in 1:ncol(wta.P.56.18)){
  wta.P.56.18[which(is.na(wta.P.56.18[,i])),i] <- 
    mean(wta.P.56.18[-which(is.na(wta.P.56.18[,i])),i])
}
for (i in 1:ncol(wta.P.90.22)){
  wta.P.90.22[which(is.na(wta.P.90.22[,i])),i] <- 
    mean(wta.P.90.22[-which(is.na(wta.P.90.22[,i])),i])
}

for (i in 1:ncol(atp.P.123.13)){
  atp.P.123.13[which(is.na(atp.P.123.13[,i])),i] <- 
    mean(atp.P.123.13[-which(is.na(atp.P.123.13[,i])),i])
}
for (i in 1:ncol(atp.P.567.17)){
  atp.P.567.17[which(is.na(atp.P.567.17[,i])),i] <- 
    mean(atp.P.567.17[-which(is.na(atp.P.567.17[,i])),i])
}
for (i in 1:ncol(atp.P.901.21)){
  atp.P.901.21[which(is.na(atp.P.901.21[,i])),i] <- 
    mean(atp.P.901.21[-which(is.na(atp.P.901.21[,i])),i])
}
for (i in 1:ncol(wta.P.123.13)){
  wta.P.123.13[which(is.na(wta.P.123.13[,i])),i] <- 
    mean(wta.P.123.13[-which(is.na(wta.P.123.13[,i])),i])
}
for (i in 1:ncol(wta.P.567.17)){
  wta.P.567.17[which(is.na(wta.P.567.17[,i])),i] <- 
    mean(wta.P.567.17[-which(is.na(wta.P.567.17[,i])),i])
}
for (i in 1:ncol(wta.P.901.21)){
  wta.P.901.21[which(is.na(wta.P.901.21[,i])),i] <- 
    mean(wta.P.901.21[-which(is.na(wta.P.901.21[,i])),i])
}
for (i in 1:ncol(atp.P.12.13)){
  atp.P.12.13[which(is.na(atp.P.12.13[,i])),i] <- 
    mean(atp.P.12.13[-which(is.na(atp.P.12.13[,i])),i])
}
for (i in 1:ncol(atp.P.56.17)){
  atp.P.56.17[which(is.na(atp.P.56.17[,i])),i] <- 
    mean(atp.P.56.17[-which(is.na(atp.P.56.17[,i])),i])
}
for (i in 1:ncol(atp.P.90.21)){
  atp.P.90.21[which(is.na(atp.P.90.21[,i])),i] <- 
    mean(atp.P.90.21[-which(is.na(atp.P.90.21[,i])),i])
}
for (i in 1:ncol(wta.P.12.13)){
  wta.P.12.13[which(is.na(wta.P.12.13[,i])),i] <- 
    mean(wta.P.12.13[-which(is.na(wta.P.12.13[,i])),i])
}
for (i in 1:ncol(wta.P.56.17)){
  wta.P.56.17[which(is.na(wta.P.56.17[,i])),i] <- 
    mean(wta.P.56.17[-which(is.na(wta.P.56.17[,i])),i])
}
for (i in 1:ncol(wta.P.90.21)){
  wta.P.90.21[which(is.na(wta.P.90.21[,i])),i] <- 
    mean(wta.P.90.21[-which(is.na(wta.P.90.21[,i])),i])
}
```
```{r}
rm(list=c("pbp.12","pbp.123","pbp.56","pbp.567","pbp.90","pbp.901"))
rm (list=c("atp.names.2013","atp.names.2014","atp.names.2017","atp.names.2018",
           "atp.names.2021","atp.names.2022","wta.names.2013","wta.names.2014",
           "wta.names.2017","wta.names.2018","wta.names.2021","wta.names.2022"))
# removing the following as well after settling on train-test-validation approach
rm(list=c("atp.P.123.13","atp.P.12.14","atp.P.567.17","atp.P.56.18",
          "atp.P.901.21","atp.P.90.22","wta.P.123.13","wta.P.12.14",
          "wta.P.567.17","wta.P.56.18","wta.P.901.21","wta.P.90.22"))
```

# Test

## Baselines

```{r}
atp14.base <- readRDS("../Results/Individual/t_atp14_basic")
wta18.base <- readRDS("../Results/Individual/t_wta18_basic")
atp18.base <- readRDS("../Results/Individual/t_atp18_basic")
wta22.base <- readRDS("../Results/Individual/t_wta22_basic")
atp22.base <- readRDS("../Results/Individual/t_atp22_basic")
```

## ATP 14

```{r}
# baseline with no activations
conduct.experiment(1:19,atp.P.123.14,atp.test.2014,
                   mu=mu.atp14,atp=TRUE,test.year=0)$score
# activate
res.u <- conduct.experiment((1:19)[-c()],atp.P.123.14,atp.test.2014,
                            mu=mu.atp14,atp=TRUE,test.year=0)
saveRDS(res.u$exact,"../Results/Individual/t_atp14_psu_rmse")
res.u$score
# deactivate
res.d <- conduct.experiment(c(),atp.P.123.14,atp.test.2014,
                            mu=mu.atp14,atp=TRUE,test.year=0)
saveRDS(res.d$exact,"../Results/Individual/t_atp14_psd_rmse")
res.d$score
```

```{r}
# Hypothesis test with overall basic baseline
ind <- which(!is.na(atp.test.2014$minutes))
t.test(((atp14.base-atp.test.2014$minutes)^2)[ind],
       ((res.u$exact-atp.test.2014$minutes)^2)[ind],
       var.equal=TRUE,alternative="greater")$p.value
# added to see if overall we're overestimating or underestimating
summary((res.u$exact-atp.test.2014$minutes)[ind])
t.test(((atp14.base-atp.test.2014$minutes)^2)[ind],
       ((res.d$exact-atp.test.2014$minutes)^2)[ind],
       var.equal=TRUE,alternative="greater")$p.value
# added to see if overall we're overestimating or underestimating
summary((res.d$exact-atp.test.2014$minutes)[ind])
```
Both overestimate

## WTA 18

```{r}
# baseline with no activations
conduct.experiment(1:19,wta.P.567.18,wta.test.2018,
                   mu=mu.wta18,atp=FALSE,test.year=0)$score
# activate 
res.u <- conduct.experiment((1:19)[-c()],wta.P.567.18,wta.test.2018,
                            mu=mu.wta18,atp=FALSE,test.year=0)
saveRDS(res.u$exact,"../Results/Individual/t_wta18_psu_rmse")
res.u$score
# deactivate 
res.d <- conduct.experiment(c(),wta.P.567.18,wta.test.2018,
                            mu=mu.wta18,atp=FALSE,test.year=0)
saveRDS(res.d$exact,"../Results/Individual/t_wta18_psd_rmse")
res.d$score
```

```{r}
# Hypothesis test with overall basic baseline
ind <- which(!is.na(wta.test.2018$minutes))
t.test(((wta18.base-wta.test.2018$minutes)^2)[ind],
       ((res.u$exact-wta.test.2018$minutes)^2)[ind],
       var.equal=TRUE,alternative="greater")$p.value
# added to see if overall we're overestimating or underestimating
summary((res.u$exact-wta.test.2018$minutes)[ind])
t.test(((wta18.base-wta.test.2018$minutes)^2)[ind],
       ((res.d$exact-wta.test.2018$minutes)^2)[ind],
       var.equal=TRUE,alternative="greater")$p.value
# added to see if overall we're overestimating or underestimating
summary((res.d$exact-wta.test.2018$minutes)[ind])
```

Both overestimate

## ATP 18

```{r}
# baseline with no activations
conduct.experiment(1:19,atp.P.567.18,atp.test.2018,
                   mu=mu.atp18,atp=TRUE,test.year=0)$score
# activate 
res.u <- conduct.experiment((1:19)[-c()],atp.P.567.18,atp.test.2018,
                            mu=mu.atp18,atp=TRUE,test.year=0)
saveRDS(res.u$exact,"../Results/Individual/t_atp18_psu_rmse")
res.u$score
# deactivate 
res.d <- conduct.experiment(c(),atp.P.567.18,atp.test.2018,
                            mu=mu.atp18,atp=TRUE,test.year=0)
saveRDS(res.d$exact,"../Results/Individual/t_atp18_psd_rmse")
res.d$score
```

```{r}
# Hypothesis test with overall basic baseline
ind <- which(!is.na(atp.test.2018$minutes))
t.test(((atp18.base-atp.test.2018$minutes)^2)[ind],
       ((res.u$exact-atp.test.2018$minutes)^2)[ind],
       var.equal=TRUE,alternative="greater")$p.value
# added to see if overall we're overestimating or underestimating
summary((res.u$exact-atp.test.2018$minutes)[ind])
t.test(((atp18.base-atp.test.2018$minutes)^2)[ind],
       ((res.d$exact-atp.test.2018$minutes)^2)[ind],
       var.equal=TRUE,alternative="greater")$p.value
# added to see if overall we're overestimating or underestimating
summary((res.d$exact-atp.test.2018$minutes)[ind])
```

Both overestimate

## WTA 22

```{r}
# baseline with no activations
conduct.experiment(1:19,wta.P.901.22,wta.test.2022,
                   mu=mu.wta22,atp=FALSE,test.year=2)$score
# activate 
res.u <- conduct.experiment((1:19)[-c()],wta.P.901.22,wta.test.2022,
                            mu=mu.wta22,atp=FALSE,test.year=2)
saveRDS(res.u$exact,"../Results/Individual/t_wta22_psu_rmse")
res.u$score
# deactivate 
res.d <- conduct.experiment(c(),wta.P.901.22,wta.test.2022,
                            mu=mu.wta22,atp=FALSE,test.year=2)
saveRDS(res.d$exact,"../Results/Individual/t_wta22_psd_rmse")
res.d$score
```

```{r}
# Hypothesis test with overall basic baseline
ind <- which(!is.na(wta.test.2022$minutes))
t.test(((wta22.base-wta.test.2022$minutes)^2)[ind],
       ((res.u$exact-wta.test.2022$minutes)^2)[ind],
       var.equal=TRUE,alternative="greater")$p.value
# added to see if overall we're overestimating or underestimating
summary((res.u$exact-wta.test.2022$minutes)[ind])
t.test(((wta22.base-wta.test.2022$minutes)^2)[ind],
       ((res.d$exact-wta.test.2022$minutes)^2)[ind],
       var.equal=TRUE,alternative="greater")$p.value
# added to see if overall we're overestimating or underestimating
summary((res.d$exact-wta.test.2022$minutes)[ind])
```

Both overestimate

## ATP 22

```{r}
# baseline with no activations
conduct.experiment(1:19,atp.P.901.22,atp.test.2022,
                   mu=mu.atp22,atp=TRUE,test.year=2)$score
# activate 
res.u <- conduct.experiment((1:19)[-c()],atp.P.901.22,atp.test.2022,
                            mu=mu.atp22,atp=TRUE,test.year=2)
saveRDS(res.u$exact,"../Results/Individual/t_atp22_psu_rmse")
res.u$score
# deactivate 
res.d <- conduct.experiment(c(),atp.P.901.22,atp.test.2022,
                            mu=mu.atp22,atp=TRUE,test.year=2)
saveRDS(res.d$exact,"../Results/Individual/t_atp22_psd_rmse")
res.d$score
```

```{r}
# Hypothesis test with overall basic baseline
ind <- which(!is.na(atp.test.2022$minutes))
t.test(((atp22.base-atp.test.2022$minutes)^2)[ind],
       ((res.u$exact-atp.test.2022$minutes)^2)[ind],
       var.equal=TRUE,alternative="greater")$p.value
# added to see if overall we're overestimating or underestimating
summary((res.u$exact-atp.test.2022$minutes)[ind])
t.test(((atp22.base-atp.test.2022$minutes)^2)[ind],
       ((res.d$exact-atp.test.2022$minutes)^2)[ind],
       var.equal=TRUE,alternative="greater")$p.value
# added to see if overall we're overestimating or underestimating
summary((res.d$exact-atp.test.2022$minutes)[ind])
```
