---
title: "Correlation between Accuracies and RMSEs for Individual Results"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Initial Pass

First, check for correlation of individual methods.

```{r}
# manual accuracy and duration rmse scores from results spreadsheet
accuracy <- c(0.59023,0.63835,0.63415,0.64340,0.5699248, # atp 14
              0.60124,0.63006,0.58138,0.59070,0.5827042, # wta 18
              0.61733,0.63957,0.63395,0.64122,0.5789877, # atp 18
              0.60175,0.63166,0.59055,0.52372,0.5776805, # wta 22
              0.60820,0.65164,0.61471,0.61674,0.554918) # atp 22
rmse <- c(42.83261,40.92694,42.1763,40.73772,40.95182,  # atp 14
          49.37423,49.09437,50.28881,64.90247,49.14777, # wta 18
          43.18453,42.71323,43.56084,46.78802,42.50824, # atp 18
          33.01183,33.07469,32.77271,34.18973,33.0457, # wta 22
          45.13423,44.65613,44.83542,46.22931,44.37147) # atp 22
```

```{r}
cor.test(accuracy,rmse,method="pearson")
cor.test(accuracy,rmse,method="kendall")
cor.test(accuracy,rmse,method="spearman")
```
We prioritize Kendall's tau for this data, but in any case none are signficant.

```{r}
cor.test(accuracy,rmse,alternative="less",method="kendall")
```

Despite some overall similarities, most notably OAF performing best overall, there is no significant negative correlation between the two sets of results.

Next, correlation of mean duration with outcome prediction ensembling counterparts.

```{r}
ens_corr <- read.csv("../New Data/misc/ensemble_corr.csv",)
mean.duration <- c(ens_corr$D.ATP14,ens_corr$D.WTA18,ens_corr$D.ATP18,
                   ens_corr$D.WTA22,ens_corr$D.ATP22)
consensus <- c(ens_corr$C.ATP14,ens_corr$C.WTA18,ens_corr$C.ATP18,
               ens_corr$C.WTA22,ens_corr$C.ATP22)
```
```{r}
cor.test(mean.duration,consensus,method="kendall")
cor.test(mean.duration,consensus,alternative="less",method="kendall")
```
Extremely significant negative Kendall's tau between consensus ensembles and mean durations.

If we were to plot the two, we find the negative correlation is much clearer if not for WTA 2022 which has much lower RMSE than other data sets, and also much lower accuracy. However, within just WTA 2022 itself, the negative correlation is also clear.

```{r}
plot(consensus,mean.duration)
plot(ens_corr$D.WTA22,ens_corr$C.WTA22)
```

Could this be true for the individual models as well?

```{r}
cor.test(accuracy[-c(16:20)],rmse[-c(16:20)],alternative="less",method="kendall")
cor.test(accuracy[c(16:20)],rmse[c(16:20)],alternative="less",method="kendall")
```

```{r}
cor.test(accuracy[-c(16:20)],rmse[-c(16:20)],alternative="less",method="pearson")
cor.test(accuracy[c(16:20)],rmse[c(16:20)],alternative="less",method="pearson")
```

## Normalized Pass

Indeed! So if we were to normalize all data with respect to their dataset and then calculate correlation (both Kendall and Pearson), we expect heavy correlation.

```{r}
# normalization
for (i in 1:5){
  s <- 5*i-3
  e <- 5*i
  accuracy[s:e] <- (accuracy[s:e]-mean(accuracy[s:e]))/sd(accuracy[s:e])
  rmse[s:e] <- (rmse[s:e]-mean(rmse[s:e]))/sd(rmse[s:e])
}
for (i in 2:21){
  valid.idx <- which(!is.na(ens_corr[,i]))
  ens_corr[valid.idx,i] <- (ens_corr[valid.idx,i]-mean(ens_corr[valid.idx,i]))/
    sd(ens_corr[valid.idx,i])
}
mean.duration <- c(ens_corr$D.ATP14,ens_corr$D.WTA18,ens_corr$D.ATP18,
                   ens_corr$D.WTA22,ens_corr$D.ATP22)
maj.idx <- which(!is.na(ens_corr$M.ATP14))
ens_corr.inc <- ens_corr[maj.idx,]
mean.duration.inc <- c(ens_corr.inc$D.ATP14,ens_corr.inc$D.WTA18,
                       ens_corr.inc$D.ATP18,ens_corr.inc$D.WTA22,
                       ens_corr.inc$D.ATP22)
consensus <- c(ens_corr$C.ATP14,ens_corr$C.WTA18,ens_corr$C.ATP18,
               ens_corr$C.WTA22,ens_corr$C.ATP22)
majority <- c(ens_corr.inc$M.ATP14,ens_corr.inc$M.WTA18,
              ens_corr.inc$M.ATP18,ens_corr.inc$M.WTA22,
              ens_corr.inc$M.ATP22)
merges <- c(ens_corr$E.ATP14,ens_corr$E.WTA18,ens_corr$E.ATP18,
           ens_corr$E.WTA22,ens_corr$E.ATP22)
```

### Individual Models

```{r}
cor.test(accuracy,rmse,alternative="less",method="pearson")
cor.test(accuracy,rmse,alternative="less",method="kendall")
```

Now just Basic.

```{r}
idx <- c(1,6,11,16,21)
cor.test(accuracy[idx],rmse[idx],alternative="less",method="pearson")
cor.test(accuracy[idx],rmse[idx],alternative="less",method="kendall")
```

OAF.

```{r}
idx <- idx+1
cor.test(accuracy[idx],rmse[idx],alternative="less",method="pearson")
cor.test(accuracy[idx],rmse[idx],alternative="less",method="kendall")
```

CO.

```{r}
idx <- idx+1
cor.test(accuracy[idx],rmse[idx],alternative="less",method="pearson")
cor.test(accuracy[idx],rmse[idx],alternative="less",method="kendall")
```

H2H.

```{r}
idx <- idx+1
cor.test(accuracy[idx],rmse[idx],alternative="less",method="pearson")
cor.test(accuracy[idx],rmse[idx],alternative="less",method="kendall")
```

PSD.

```{r}
idx <- idx+1
cor.test(accuracy[idx],rmse[idx],alternative="less",method="pearson")
cor.test(accuracy[idx],rmse[idx],alternative="less",method="kendall")
```

### Mean Duration and Consensus Ensembles

```{r}
cor.test(mean.duration,consensus,alternative="less",method="pearson")
cor.test(mean.duration,consensus,alternative="less",method="kendall")
```

### Mean Duration and Majority Ensembles

```{r}
cor.test(mean.duration.inc,majority,alternative="less",method="pearson")
cor.test(mean.duration.inc,majority,alternative="less",method="kendall")
```

### Mean Duration and Merges Ensembles

```{r}
cor.test(mean.duration,merges,alternative="less",method="pearson")
cor.test(mean.duration,merges,alternative="less",method="kendall")
```
