---
title: "Additional Figures"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Figure 2 - Accuracy score plots corresponding to activations and deactivations of states in the point-to-game DTMC.

Want dotted line for the pure basic baselines, significance markings for plateau significance with footnote explaining notation, and the states activated/deactivated marked near the points as well.

```{r data}
u5.atp14 <- readRDS("plateaus/u5_atp_2014.rds")
d5.atp14 <- readRDS("plateaus/d5_atp_2014.rds")
u5.wta14 <- readRDS("plateaus/u5_wta_2014.rds")
d5.wta14 <- readRDS("plateaus/d5_wta_2014.rds")
u5.atp18 <- readRDS("plateaus/u5_atp_2018.rds")
d5.atp18 <- readRDS("plateaus/d5_atp_2018.rds")
u5.wta18 <- readRDS("plateaus/u5_wta_2018.rds")
d5.wta18 <- readRDS("plateaus/d5_wta_2018.rds")
u5.atp22 <- readRDS("plateaus/u5_atp_2022.rds")
d5.atp22 <- readRDS("plateaus/d5_atp_2022.rds")
u5.wta22 <- readRDS("plateaus/u5_wta_2022.rds")
d5.wta22 <- readRDS("plateaus/d5_wta_2022.rds")

# the all/none activated scores are manually inputted here so the 
# big point-specific machinery doesn't need to be all moved here

# ATP 2013
# A: 1, D: 2
# A: 0.5619403, D: 0.5522388

# WTA 2013
# A: 1, D: 7
# A: 0.6468144, D: 0.6371191

# ATP 2017
# A: 12, D: 11
# A: 0.5458045, D: 0.6428022

# WTA 2017
# A: 9, D: 16
# A: 0.5730909, D: 0.5687273

# ATP 2021
# A: 2, D: 12
# A: 0.5797872, D: 0.5797872

# WTA 2021
# A: 9, D: 16
# A: 0.6037609, D: 0.5990598
```

```{r plotting}
get.gg.score <- function(u.res,d.res,u.base,d.base,ylim.lower=0.6,ylim.upper=0.7){
  n.paths <- length(u.res)+length(d.res)
  u.depth <- length(u.res[[1]][[1]])
  d.depth <- length(d.res[[1]][[1]])
  df <- matrix(0,nrow=length(d.res)*d.depth+length(u.res)*u.depth+2,ncol=3)
  row.ptr <- 3
  # # states activated \ Path ID \ Score
  df[1,] <- c(0,1,u.base)
  df[2,] <- c(20,n.paths,d.base)
  for (i in 1:length(u.res)){
    for (j in 1:u.depth){
      df[row.ptr,] <- c(j,i,u.res[[i]][[1]][j])
      row.ptr <- row.ptr + 1
    }
  }
  for (i in 1:length(d.res)){
    for (j in 1:d.depth){
      df[row.ptr,] <- c(20-j,i+length(u.res),d.res[[i]][[1]][j])
      row.ptr <- row.ptr + 1
    }
  }
  df <- data.frame(df)
  gg <- ggplot(data=df,aes(x=X1,y=X3,group=X2)) +
    geom_line() +
    xlab("Number of States Activated") +
    ylab("Score") +
    ylim(ylim.lower,ylim.upper)
    # scale_y_continuous(
    #   breaks = round(seq(min(df$X3),max(df$X3),length.out=3),2)-c(0,0,0.01))
}
```

```{r}
# library(ggplot2)
gg.a13 <- get.gg.score(u5.atp14,d5.atp14,0.5619403,0.5522388,ylim.lower=0.55)+
  annotate("text",x=2,y=0.68,label="*** (State 1)",hjust=0)+
  annotate("text",x=18,y=0.65,label="*** (State 2)",hjust=1)+
  theme(axis.title.x=element_blank())+ggtitle("ATP 2013")+
  theme(plot.title = element_text(hjust = 0.5))
  # geom_hline(yintercept=0.5902256, linetype='dashed', col = 'red')
gg.w13 <- get.gg.score(u5.wta14,d5.wta14,0.6468144,0.6371191,
                       ylim.lower=0.62,ylim.upper=0.67)+
  annotate("text",x=0.5,y=0.66,label="(State 1)",hjust=0)+
  annotate("text",x=20,y=0.635,label="(State 7)",hjust=1)+
  ggtitle("WTA 2013")+
  theme(plot.title = element_text(hjust = 0.5))
gg.a17 <- get.gg.score(u5.atp18,d5.atp18,0.5458045,0.6428022,ylim.lower=0.53)+
  annotate("text",x=1,y=0.675,label="*** (State 12)",hjust=0)+
  annotate("text",x=20,y=0.63,label="(State 11)",hjust=1)+
  theme(axis.title.x=element_blank(),axis.title.y=element_blank())+ggtitle("ATP 2017")+
  theme(plot.title = element_text(hjust = 0.5))
gg.w17 <- get.gg.score(u5.wta18,d5.wta18,0.5730909,0.5687273,
                       ylim.lower=0.565,ylim.upper=0.61)+
  annotate("text",x=1,y=0.585,label="(State 9)",hjust=0)+
  annotate("text",x=18.9,y=0.605,label="(State 16)",hjust=1)+
  theme(axis.title.y=element_blank())+ggtitle("WTA 2017")+
  theme(plot.title = element_text(hjust = 0.5))
gg.a21 <- get.gg.score(u5.atp22,d5.atp22,0.5797872,0.5797872,
                       ylim.lower=0.579,ylim.upper=0.65)+
  annotate("text",x=1,y=0.645,label="** (State 2)",hjust=0)+
  annotate("text",x=20,y=0.635,label="** (State 12)",hjust=1)+
  theme(axis.title.x=element_blank(),axis.title.y=element_blank())+ggtitle("ATP 2021")+
  theme(plot.title = element_text(hjust = 0.5))
gg.w21 <- get.gg.score(u5.wta22,d5.wta22,0.6037609,0.5990598,
                       ylim.lower=0.595,ylim.upper=0.635)+
  annotate("text",x=0,y=0.63,label="(State 9)",hjust=0)+
  annotate("text",x=20,y=0.625,label="(State 16)",hjust=1)+
  theme(axis.title.y=element_blank())+ggtitle("WTA 2021")+
  theme(plot.title = element_text(hjust = 0.5))
# library(patchwork)
gg <- gg.a13 + gg.a17 + gg.a21 + gg.w13 + gg.w17 + gg.w21
gg
```

```{r}
ggsave('figures/fig2.jpg', gg, dpi=300)
```

## Figure 3 - Consensus Coverage vs. Accuracy & Significance

```{r}
consensus <- read.csv("../New Data/misc/ens_consensus_aggregate.csv")
consensus.coverage <- as.numeric(sub("%","",consensus$Coverage))
fit.3a <- lm(consensus$Mean.Accuracy~consensus.coverage)
fib.3b <- lm(consensus$Mean.Significance~consensus.coverage)
majority <- read.csv("../New Data/misc/ens_majority_aggregate.csv")
majority.coverage <- as.numeric(sub("%","",majority$Coverage))
fit.3c <- lm(majority$Mean.Accuracy~majority.coverage)
fib.3d <- lm(majority$Mean.Significance~majority.coverage)
```
```{r}
# library(ggplot2)
data.ab <- data.frame(x=consensus.coverage,
                      y=consensus$Mean.Accuracy,
                      z=consensus$Mean.Significance)
gga <- ggplot(data=data.ab,aes(x,y))+
  geom_smooth(method='lm',formula=y~x,color="black")+
  geom_point()+xlab("Coverage (%)")+ylab("Accuracy (%)")+
  ggtitle("(a)")+
  theme(plot.title = element_text(hjust = 0.5))
ggb <- ggplot(data=data.ab,aes(x,z))+
  geom_smooth(method='lm',formula=y~x,color="black")+
  geom_point()+xlab("Coverage (%)")+ylab("Significance")+
  ggtitle("(b)")+
  theme(plot.title = element_text(hjust = 0.5))
data.cd <- data.frame(x=majority.coverage,
                      y=majority$Mean.Accuracy,
                      z=majority$Mean.Significance)
ggc <- ggplot(data=data.cd,aes(x,y))+
  geom_smooth(method='lm',formula=y~x,color="black")+
  geom_point()+xlab("Coverage (%)")+ylab("Accuracy (%)")+
  ggtitle("(c)")+
  theme(plot.title = element_text(hjust = 0.5))
ggd <- ggplot(data=data.cd,aes(x,z))+
  geom_smooth(method='lm',formula=y~x,color="black")+
  geom_point()+xlab("Coverage (%)")+ylab("Significance")+
  ggtitle("(d)")+
  theme(plot.title = element_text(hjust = 0.5))
# library(patchwork)
gg3 <- gga+ggb+ggc+ggd
gg3
```
```{r}
ggsave('figures/figure3.jpg', gg3, dpi=300)
```

