---
title: "Postscript on Point-Specific Coverage"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose

In the paper, the only individual method that provides full coverage is the point-specific one, as it imputes point win probabilities with the mean of the field for that specific point/state before any training, validation, and testing. This was done despite the ceasing of imputation for basic and OAF methods as it was considered wasteful to remove a player from the dataset if they had sufficient data gathered to calculate a portion of their point-specific win probabilities but not enough to have all 19 probabilities. (E.g., Adrian Ungur in ATP.P.12.13 is only missing p_10.)

If we were to instead do away with this imputation as well, coverage is certainly expected to drop below 100%, but the paper's results are not expected to change drastically anywhere with regards to outcome prediction (duration prediction already enforces full coverage for every method), as --

1. It is shown in the paper through comparing the imputed and non-imputed ("pure") versions of basic and OAF results that there were very few significant changes to accuracy (only ATP 2014, which saw significant decreases **after** imputation).

2. The ensembles of value, predominantly the consensus models as well as the majority models, had their coverages restricted by the lowest coverage of their components, which would never be the full-coverage point-specific results. More importantly, as noted in 5.1, the ensembles start with the imputed versions of OAF as well to obtain as much coverage as possible.

However, for completeness and rigourness, this postscript contains the outcome prediction results done for when the point-specific method is re-done with incomplete coverage. Since the ensembles already use imputed components, they are not reproduced here. Similarly, for results on correlation between outcome prediction and duration prediction, imputed results should be used (as is done for both Basic and OAF in 5.4) as duration prediction uses imputed results. This section's results are thus restricted to the accuracies, coverages, and plateau significances of the non-imputed point-specific method, and are organized under "postscript_results" in "Results".

Code from 4.1, minus the last segment which imputes point-specific win probabilities, is "imported" below. Replacing the last segment is code removing from all P matrices any player entry who contains NaN for any one of the 19 point-specific probabilities. All experiment functions are modified correspondingly to account for when a player is not available for a match in the validation/test set.

# Prep Functions

```{r functions}
# main function is match.win.prob
source("2_1_hierarchical_model_probabilities.R")

# 3 helper functions

get.unique.players <- function(testset){
  # takes the players in the test set and returns vector
  # containing unique players in the test set
  names <- c(testset$winner_name,testset$loser_name)
  names <- unique(names)
  return(names)
}

get.equiv.names <- function(fullname){
  # returns vector of equivalent names in different formats
  # according to the fullname given
  # fullname ideally from get.unique.players output
  # More special examples:
  #   Alejandro Davidovich Fokina -> A Davidovich Fokina & A. Davidovich Fokina
  #   Pierre Hugues Herbert -> P Herbert & Ph Herbert & P. Herbert
  #   Alex De Minaur -> A. De Minaur & Alex de Minaur & A De Minaur
  #   Karolina Pliskova -> K. Pliskova & Ka. Pliskova & Ka Pliskova
  #   Kristyna Pliskova -> K. Pliskova & Kr. Pliskova & Kr Pliskova
  #   some cases manually remediated (see misc. google doc)
  #   but quick manual remediation can't help if player in test set has middle name
  #   and full name isn't in pbp training set.
  #   Function tries to account for this as follows.
  
  # Alex Bee Caine -> c("A. Caine", "A Caine", "A. Bee Caine", "A Bee Caine",
  #                     "Ab Caine", "A Bee-Caine", "A. Bee-Caine")
  
  # This method risks picking up on players with same last name and first letter
  # But this is unlikely as the pbp training set only 1 case of this - Kr&Ka Pliskova
  # And this was picked up since there were 2 characters before the space
  
  parts <- strsplit(fullname,split=" ")[[1]]
  n <- length(parts)
  first.letter <- substr(parts[1],1,1)
  equiv <- c(fullname,
             paste(first.letter," ",parts[n],sep=""),
             paste(first.letter,"."," ",parts[n],sep=""))
  if (n > 2){
    rest <- ""
    rest.dash <- ""
    for (i in 1:(n-1)){
      rest <- paste(rest," ",parts[i+1],sep="")
      rest.dash <- paste(rest.dash,parts[i+1],sep="-")
    }
    rest.dash <- substr(rest.dash,2,nchar(rest.dash)) # get rid of first dash
    first.middle.name.letter <- tolower(substr(parts[2],1,1))
    rest.more <- "" # for if the name has four or more parts
    for (i in 1:(n-2)){
      rest.more <- paste(rest.more," ",parts[i+2],sep="")
    }
    # rest contains the first space, rest.dash doesn't
    equiv <- c(equiv, paste(first.letter,rest,sep=""),
               paste(first.letter,".",rest,sep=""),
               paste(first.letter," ",rest.dash,sep=""),
               paste(first.letter,"."," ",rest.dash,sep=""),
               paste(first.letter,first.middle.name.letter,rest.more,sep=""))
  }
  return(equiv)
}

get.aggr.by.state <- function(entry){
  # extract serve won & serve total fields for a player
  # without surface distinction
  ret <- rep(0,38)
  for (i in 1:18){
    # odd indices for pts won, even for total
    ret[2*i-1] <- entry[[3+4*i]]
    ret[2*i] <- entry[[2+4*i]]
  }
  ret[37] <- entry[[3]]
  ret[38] <- entry[[2]]
  return(ret)
}

create.p.vector <- function(tst.names,pbp){
  # returns a dataframe with the rows in the order of names,
  # the columns being p's for states 1-18 and then t (tiebreak)
  # final column is overall p regardless of state by taking total won / total serve
  # names usually from get.unique.players on test data set
  # pbp is the point-by-point data given
  # note p-vectors not surface specific
  
  n <- length(tst.names)
  m <- nrow(pbp)
  pbp.name <- pbp$name
  aggr <- matrix(0,nrow=n,ncol=38) # 38=2x19, taking won & total to divide later
  for (i in 1:n){
    equiv <- get.equiv.names(tst.names[i])
    p <- length(equiv)
    for (j in 1:p){
      for (l in 1:m){
        # check 1 by 1 since pbp has non-unique names after manual remediation
        if (tolower(equiv[j])==tolower(pbp.name[l])){
          more.aggr <- get.aggr.by.state(pbp[l,])
          aggr[i,] <- aggr[i,]+more.aggr
        }
      }
    }
  }
  # now divide odd cols by even cols to obtain p's
  output <- matrix(0,nrow=n,ncol=20)
  output <- data.frame(output, row.names=tst.names)
  for (i in 1:n){
    for (j in 1:19){
      output[i,j] <- aggr[i,2*j-1]/aggr[i,2*j]
    } # note below first seq() output will end at 37
    output[i,20] <- sum(aggr[i,seq(1,38,by=2)])/sum(aggr[i,seq(2,38,by=2)])
  }
  return(output)
}

grand.slams <- c("Australian Open","Roland Garros","Wimbledon","US Open","Us Open")
get.prob.pre.2022 <- function(p1,p2,match,atp=TRUE){
  if (match %in% grand.slams){
    if (match=="US Open"){
      ret <- match.win.prob.pw(p1,p2,format=0+atp)
    } else {
      ret <- match.win.prob.pw(p1,p2,format=4+atp)
    }
  } else {
    ret <- match.win.prob.pw(p1,p2,format=0)
  }
  return(ret)
}
get.prob.post.2022 <- function(p1,p2,match,atp=TRUE){
  if (match %in% grand.slams){
    ret <- match.win.prob.pw(p1,p2,format=2+atp)
  } else {
    ret <- match.win.prob.pw(p1,p2,format=0)
  }
  return(ret)
}

# overall function to do experiments with
conduct.experiment <- function(inactive.states, P, test.set, atp=TRUE, test.year=0){
  # inactive.states:
  #   vector containing states (19 for tiebreak) to deactivate, i.e. 
  #   replace the state's unique p with the player's overall p
  # P:
  #   data.frame containing players' individual p vectors
  #   usually obtained via create.p.vector output
  # test.set:
  #   data set used to test accuracy of prediction
  # atp:
  #   boolean defaulted to true if test.set is ATP data
  # test.year:
  #   three valid values: 0,1,2
  #   0 for up to 2018, 1 for 2019 to 2021 inclusive, 2 for 2022 beyond
  #   no testing year actually falls between 2019-2021, this new version
  #   just depreciates this, so 1 is not an actual valid input for test.year
  
  # make copy of P and change copy to align with specified inactive.states
  cP <- P[,1:19]
  cP[,inactive.states] <- P[,20]
  
  # record exact probability values from model
  # so we can examine closer if we want
  n <- nrow(test.set)
  # exact <- rep(0,n) below new since exact length not constant (use to determine coverage)
  exact <- c()
  
  # experiment begins
  pbp.names <- rownames(cP)
  for (i in 1:n){
    matchup <- test.set[i,]
    winner <- matchup$winner_name
    loser <- matchup$loser_name
    inds <- match(c(winner,loser),pbp.names)
    ### new to postscript
    if (sum(is.na(inds))) next
    ###
    winner.P <- unname(unlist(cP[inds[1],]))
    loser.P <- unname(unlist(cP[inds[2],]))
    if (test.year==0){
      exact <- c(exact,
                 get.prob.pre.2022(p1=winner.P,p2=loser.P,
                                   matchup$tourney_name,atp))
    } else {
      exact <- c(exact,
                 get.prob.post.2022(p1=winner.P,p2=loser.P,
                                    matchup$tourney_name,atp))
    }
  }
  res <- exact > 0.5
  return(list("score"=mean(res),"result"=res,"exact"=exact))
}

downwards.wrapper <- function(deactivate,P,testset,atp,test.year){
  # atp is boolean for if testset is for ATP
  scores <- rep(0,19)
  if (length(deactivate)==0){
    options <- 1:19
  } else {
    options <- (1:19)[-deactivate]
  }
  for (i in options){
    scores[i] <- conduct.experiment(c(i,deactivate),P,testset,atp,test.year)$score
    # so deactivated state's indices will have 0
  }
  return(list("max"=max(scores),"candidates"=which(scores==max(scores))))
}
upwards.wrapper <- function(activate,P,testset,atp,test.year){
  # atp is boolean for if testset is for ATP
  if (length(activate)==0){
    deactivate <- 1:19
  } else {
    deactivate <- (1:19)[-activate]
  }
  scores <- rep(0,19)
  for (i in deactivate){
    deactivate.no.i <- (1:19)[-c(activate,i)]
    scores[i] <- conduct.experiment(deactivate.no.i,P,testset,atp,test.year)$score
    # activated state's indices will have 0
  }
  return(list("max"=max(scores),"candidates"=which(scores==max(scores))))
}

downwards.experiment <- function(starting.states,P,testset,atp,previous.scores,
                                 depth=18,test.year=2){
  
  diverge.lists <- c()
  deactivate <- starting.states
  
  # through recursion, aim to combine all ovr.lists produced
  ovr.list <- list() # to contain lists containing state & score vectors
  path <- list()
  # if no previous scores, can initialize NULL list element for scores:
  # https://stackoverflow.com/questions/45666451/r-adding-an-empty-vector-to-a-list
  if (length(previous.scores)==0){
    path[1] <- list(NULL)
  } else {
    path[[1]] <- previous.scores # to record best scores of this path
  }
  # path[[2]] to record states deactivated, but does not need initialization
  
  while(length(deactivate) < depth){
    
    res <- downwards.wrapper(deactivate,P,testset,atp,test.year)
    score <- res$max
    cands <- res$candidates
    scores.sofar <- c(path[[1]],score)
    
    l <- length(cands)
    if (l>1){
      # recursion call
      for (i in 2:l){
        diverge.lists <- c(
          diverge.lists,
          downwards.experiment(c(deactivate,cands[i]),P,testset,atp,scores.sofar,
                               depth,test.year))
      }
    }
    path[[1]] <- scores.sofar
    deactivate <- c(deactivate,cands[1])
    path[[2]] <- deactivate
  }
  path[[2]] <- deactivate
  ovr.list[[1]] <- path
  ovr.list <- c(ovr.list,diverge.lists)
  
  return(ovr.list)
}

upwards.experiment <- function(starting.states,P,testset,atp,previous.scores,
                               depth=18,test.year=2){
  
  diverge.lists <- c()
  activate <- starting.states
  
  # through recursion, aim to combine all ovr.lists produced
  ovr.list <- list() # to contain lists containing state & score vectors
  path <- list()
  # if no previous scores, can initialize NULL list element for scores:
  # https://stackoverflow.com/questions/45666451/r-adding-an-empty-vector-to-a-list
  if (length(previous.scores)==0){
    path[1] <- list(NULL)
  } else {
    path[[1]] <- previous.scores # to record best scores of this path
  }
  # path[[2]] to record states deactivated, but does not need initialization
  
  while(length(activate) < depth){
    
    res <- upwards.wrapper(activate,P,testset,atp,test.year)
    score <- res$max
    cands <- res$candidates
    scores.sofar <- c(path[[1]],score)
    
    l <- length(cands)
    if (l>1){
      # recursion call
      for (i in 2:l){
        diverge.lists <- c(
          diverge.lists,
          upwards.experiment(c(activate,cands[i]),P,testset,atp,scores.sofar,
                             depth,test.year))
      }
    }
    path[[1]] <- scores.sofar
    activate <- c(activate,cands[1])
    path[[2]] <- activate
  }
  path[[2]] <- activate
  ovr.list[[1]] <- path
  ovr.list <- c(ovr.list,diverge.lists)
  
  return(ovr.list)
}

plot.path.score <- function(n.down,dat.down,n.up,dat.up,
                      P, test.set, atp=TRUE, main="Score",
                      ylim.lower=0.55,ylim.upper=0.7,hide.axis=FALSE,test.year=0){
  # n - length of path given
  # dat - data saved containing paths
  # ylim.lower(upper) - ylim for plot, set to around 0(20) for type=2
  
  baseline.down <- conduct.experiment(c(),P,test.set,atp,test.year)$score
  baseline.up <- conduct.experiment(1:19,P,test.set,atp,test.year)$score
  
  if (hide.axis) {
    plot(0:n.up,c(baseline.up,dat.up[[1]][[1]]),'l',
         xlim=c(0,20),ylim=c(ylim.lower,ylim.upper),main=main)
  } else {
    plot(0:n.up,c(baseline.up,dat.up[[1]][[1]]),'l',
         xlim=c(0,20),ylim=c(ylim.lower,ylim.upper),main=main,
         ylab="Score",xlab="# States Activated")
  }
  for (i in 1:length(dat.up)){
    lines(0:n.up,c(baseline.up,dat.up[[i]][[1]]))
  }
  for (i in 1:length(dat.down)){
    lines(20:(20-n.down),c(baseline.down,dat.down[[i]][[1]]))
  }
}

plot.path.state <- function(n.down,dat.down,n.up,dat.up,main="States",
                            ylim.lower=0,ylim.upper=20,hide.axis=FALSE){
  # n - length of path given
  # dat - data saved containing paths
  # ylim.lower(upper) - ylim for plot, set to around 0(20) for state
  if (hide.axis) {
    plot(1:n.up,dat.up[[1]][[2]],'l',
         xlim=c(1,19),ylim=c(ylim.lower,ylim.upper),main=main)
  } else {
    plot(1:n.up,dat.up[[1]][[2]],'l',
         xlim=c(1,19),ylim=c(ylim.lower,ylim.upper),main=main,
         ylab="States",xlab="# States Activated")
  }
  for (i in 1:length(dat.up)){
    lines(1:n.up,dat.up[[i]][[2]])
  }
  for (i in 1:length(dat.down)){
    lines(19:(20-n.down),dat.down[[i]][[2]])
  }
}
```

# Data

```{r}
# Testing data
# if Error: no more error handlers available (recursive errors?); invoking 'abort' restart
# Warning: type 29 is unimplemented in 'type2char'Error in pmatch(rw, c("read", "write"), 0L) : 
# INTEGER() can only be applied to a 'integer', not a 'unknown type #29'
# just run again
atp.test.2014 <- read.csv('../New Data/atp/atp_testing_2014.csv')
wta.test.2014 <- read.csv('../New Data/wta/wta_testing_2014.csv')
atp.test.2018 <- read.csv('../New Data/atp/atp_testing_2018.csv')
wta.test.2018 <- read.csv('../New Data/wta/wta_testing_2018.csv')
atp.test.2022 <- read.csv('../New Data/atp/atp_testing_2022.csv')
wta.test.2022 <- read.csv('../New Data/wta/wta_testing_2022.csv')
# following function highlights matches that were incomplete
# this is determined by if the score has letters ("W/O","Def.","RET" etc.)
# takes as input the score column of a dataset and returns indexes
ic.match <- function(score) grep("[A-Za-z]",score)
atp.test.2014 <- atp.test.2014[-ic.match(atp.test.2014$score),]
wta.test.2014 <- wta.test.2014[-ic.match(wta.test.2014$score),]
atp.test.2018 <- atp.test.2018[-ic.match(atp.test.2018$score),]
wta.test.2018 <- wta.test.2018[-ic.match(wta.test.2018$score),]
atp.test.2022 <- atp.test.2022[-ic.match(atp.test.2022$score),]
wta.test.2022 <- wta.test.2022[-ic.match(wta.test.2022$score),]
row.names(atp.test.2014) <- NULL
row.names(wta.test.2014) <- NULL
row.names(atp.test.2018) <- NULL
row.names(wta.test.2018) <- NULL
row.names(atp.test.2022) <- NULL
row.names(wta.test.2022) <- NULL
# Validation data
atp.val.2013 <- read.csv('../New Data/atp/atp_val_2013.csv')
wta.val.2013 <- read.csv('../New Data/wta/wta_val_2013.csv')
atp.val.2017 <- read.csv('../New Data/atp/atp_val_2017.csv')
wta.val.2017 <- read.csv('../New Data/wta/wta_val_2017.csv')
atp.val.2021 <- read.csv('../New Data/atp/atp_val_2021.csv')
wta.val.2021 <- read.csv('../New Data/wta/wta_val_2021.csv')
atp.val.2013 <- atp.val.2013[-ic.match(atp.val.2013$score),]
wta.val.2013 <- wta.val.2013[-ic.match(wta.val.2013$score),]
atp.val.2017 <- atp.val.2017[-ic.match(atp.val.2017$score),]
wta.val.2017 <- wta.val.2017[-ic.match(wta.val.2017$score),]
atp.val.2021 <- atp.val.2021[-ic.match(atp.val.2021$score),]
wta.val.2021 <- wta.val.2021[-ic.match(wta.val.2021$score),]
row.names(atp.val.2013) <- NULL
row.names(wta.val.2013) <- NULL
row.names(atp.val.2017) <- NULL
row.names(wta.val.2017) <- NULL
row.names(atp.val.2021) <- NULL
row.names(wta.val.2021) <- NULL
# Point-by-Point data
pbp.123 <- read.csv('../New Data/pbp/2011-2013_pbp_individual.csv')
pbp.567 <- read.csv('../New Data/pbp/2015-2017_pbp_individual.csv')
pbp.901 <- read.csv('../New Data/pbp/2019-2021_pbp_individual.csv')
pbp.12 <- read.csv('../New Data/pbp/2011-2012_pbp_individual.csv')
pbp.56 <- read.csv('../New Data/pbp/2015-2016_pbp_individual.csv')
pbp.90 <- read.csv('../New Data/pbp/2019-2020_pbp_individual.csv')
# Getting unique names
atp.names.2014 <- get.unique.players(atp.test.2014)
atp.names.2018 <- get.unique.players(atp.test.2018)
atp.names.2022 <- get.unique.players(atp.test.2022)
wta.names.2014 <- get.unique.players(wta.test.2014)
wta.names.2018 <- get.unique.players(wta.test.2018)
wta.names.2022 <- get.unique.players(wta.test.2022)
atp.names.2013 <- get.unique.players(atp.val.2013)
atp.names.2017 <- get.unique.players(atp.val.2017)
atp.names.2021 <- get.unique.players(atp.val.2021)
wta.names.2013 <- get.unique.players(wta.val.2013)
wta.names.2017 <- get.unique.players(wta.val.2017)
wta.names.2021 <- get.unique.players(wta.val.2021)
# create p vectors
atp.P.123.14 <- create.p.vector(atp.names.2014,pbp.123)
atp.P.567.18 <- create.p.vector(atp.names.2018,pbp.567)
atp.P.901.22 <- create.p.vector(atp.names.2022,pbp.901)
wta.P.123.14 <- create.p.vector(wta.names.2014,pbp.123)
wta.P.567.18 <- create.p.vector(wta.names.2018,pbp.567)
wta.P.901.22 <- create.p.vector(wta.names.2022,pbp.901)
atp.P.12.14 <- create.p.vector(atp.names.2014,pbp.12)
atp.P.56.18 <- create.p.vector(atp.names.2018,pbp.56)
atp.P.90.22 <- create.p.vector(atp.names.2022,pbp.90)
wta.P.12.14 <- create.p.vector(wta.names.2014,pbp.12)
wta.P.56.18 <- create.p.vector(wta.names.2018,pbp.56)
wta.P.90.22 <- create.p.vector(wta.names.2022,pbp.90)
atp.P.123.13 <- create.p.vector(atp.names.2013,pbp.123)
atp.P.567.17 <- create.p.vector(atp.names.2017,pbp.567)
atp.P.901.21 <- create.p.vector(atp.names.2021,pbp.901)
wta.P.123.13 <- create.p.vector(wta.names.2013,pbp.123)
wta.P.567.17 <- create.p.vector(wta.names.2017,pbp.567)
wta.P.901.21 <- create.p.vector(wta.names.2021,pbp.901)
atp.P.12.13 <- create.p.vector(atp.names.2013,pbp.12)
atp.P.56.17 <- create.p.vector(atp.names.2017,pbp.56)
atp.P.90.21 <- create.p.vector(atp.names.2021,pbp.90)
wta.P.12.13 <- create.p.vector(wta.names.2013,pbp.12)
wta.P.56.17 <- create.p.vector(wta.names.2017,pbp.56)
wta.P.90.21 <- create.p.vector(wta.names.2021,pbp.90)
```
```{r}
# environment clean-up
rm(list=c("pbp.12","pbp.123","pbp.56","pbp.567","pbp.90","pbp.901"))
rm (list=c("atp.names.2013","atp.names.2014","atp.names.2017","atp.names.2018",
           "atp.names.2021","atp.names.2022","wta.names.2013","wta.names.2014",
           "wta.names.2017","wta.names.2018","wta.names.2021","wta.names.2022"))
rm(list=c("atp.P.123.13","atp.P.12.14","atp.P.567.17","atp.P.56.18",
          "atp.P.901.21","atp.P.90.22","wta.P.123.13","wta.P.12.14",
          "wta.P.567.17","wta.P.56.18","wta.P.901.21","wta.P.90.22"))
```
```{r}
# if P entry contains NaN, remove it altogether
rid.nans <- function(P){
  numrows <- nrow(P)
  contains.nans <- c()
  for (i in 1:numrows){
    if (sum(is.na(P[i,]))>0) contains.nans <- c(contains.nans,i)
  }
  return(P[-contains.nans,])
}
```
```{r}
atp.P.123.14 <- rid.nans(atp.P.123.14)
atp.P.567.18 <- rid.nans(atp.P.567.18)
atp.P.901.22 <- rid.nans(atp.P.901.22)
wta.P.123.14 <- rid.nans(wta.P.123.14)
wta.P.567.18 <- rid.nans(wta.P.567.18)
wta.P.901.22 <- rid.nans(wta.P.901.22)
atp.P.12.13 <- rid.nans(atp.P.12.13)
atp.P.56.17 <- rid.nans(atp.P.56.17)
atp.P.90.21 <- rid.nans(atp.P.90.21)
wta.P.12.13 <- rid.nans(wta.P.12.13)
wta.P.56.17 <- rid.nans(wta.P.56.17)
wta.P.90.21 <- rid.nans(wta.P.90.21)
```


# State Selection / Validation

## WTA 14

```{r}
# d <- downwards.experiment(c(),wta.P.12.13,wta.val.2013,FALSE,c(),depth=5,test.year=0)
# saveRDS(d, file="postscript_plateaus/d5_wta_2014.rds")
```
```{r}
# u <- upwards.experiment(c(),wta.P.12.13,wta.val.2013,FALSE,c(),depth=5,test.year=0)
# saveRDS(u, file="postscript_plateaus/u5_wta_2014.rds")
```
```{r}
d5.wta14 <- readRDS("postscript_plateaus/d5_wta_2014.rds")
u5.wta14 <- readRDS("postscript_plateaus/u5_wta_2014.rds")
```
```{r}
plot.path.score(5,d5.wta14,5,u5.wta14,wta.P.12.13,wta.val.2013,main="WTA 2014",
                ylim.lower=0.65)
```
```{r}
plot.path.state(5,d5.wta14,5,u5.wta14,main="WTA 2014")
```

Activate 3, 9; Deactivate 15

## ATP 14

```{r}
# d <- downwards.experiment(c(),atp.P.12.13,atp.val.2013,TRUE,c(),depth=5,test.year=0)
# saveRDS(d, file="postscript_plateaus/d5_atp_2014.rds")
```
```{r}
# u <- upwards.experiment(c(),atp.P.12.13,atp.val.2013,TRUE,c(),depth=5,test.year=0)
# saveRDS(u, file="postscript_plateaus/u5_atp_2014.rds")
```
```{r}
d5.atp14 <- readRDS("postscript_plateaus/d5_atp_2014.rds")
u5.atp14 <- readRDS("postscript_plateaus/u5_atp_2014.rds")
```
```{r}
plot.path.score(5,d5.atp14,5,u5.atp14,atp.P.12.13,atp.val.2013,main="ATP 2014")
```
```{r}
plot.path.state(5,d5.atp14,5,u5.atp14,main="ATP 2014")
```

Activate 8; Deactivate 4, 9

## WTA 18

```{r}
# d <- downwards.experiment(c(),wta.P.56.17,wta.val.2017,FALSE,c(),depth=5,test.year=0)
# saveRDS(d, file="postscript_plateaus/d5_wta_2018.rds")
```
```{r}
# u <- upwards.experiment(c(),wta.P.56.17,wta.val.2017,FALSE,c(),depth=5,test.year=0)
# saveRDS(u, file="postscript_plateaus/u5_wta_2018.rds")
```
```{r}
d5.wta18 <- readRDS("postscript_plateaus/d5_wta_2018.rds")
u5.wta18 <- readRDS("postscript_plateaus/u5_wta_2018.rds")
```
```{r}
plot.path.score(5,d5.wta18,5,u5.wta18,wta.P.56.17,wta.val.2017,atp=FALSE,main="WTA 2018",
                ylim.upper=0.61)
```
```{r}
plot.path.state(5,d5.wta18,5,u5.wta18,main="WTA 2018")
```

Activate 3, 6; Deactivate 19

## ATP 18

```{r}
# d <- downwards.experiment(c(),atp.P.56.17,atp.val.2017,TRUE,c(),depth=5,test.year=0)
# saveRDS(d, file="postscript_plateaus/d5_atp_2018.rds")
```
```{r}
# u <- upwards.experiment(c(),atp.P.56.17,atp.val.2017,TRUE,c(),depth=5,test.year=0)
# saveRDS(u, file="postscript_plateaus/u5_atp_2018.rds")
```
```{r}
d5.atp18 <- readRDS("postscript_plateaus/d5_atp_2018.rds")
u5.atp18 <- readRDS("postscript_plateaus/u5_atp_2018.rds")
```
```{r}
plot.path.score(5,d5.atp18,5,u5.atp18,atp.P.56.17,atp.val.2017,atp=TRUE,main="ATP 2018",
                ylim.lower = 0.6)
```
```{r}
plot.path.state(5,d5.atp18,5,u5.atp18,main="ATP 2018")
```

Activate 9, 14; Deactivate 19

## WTA 22

```{r}
# d <- downwards.experiment(c(),wta.P.90.21,wta.val.2021,FALSE,c(),depth=5,test.year=2)
# saveRDS(d, file="postscript_plateaus/d5_wta_2022.rds")
```
```{r}
# u <- upwards.experiment(c(),wta.P.90.21,wta.val.2021,FALSE,c(),depth=5,test.year=2)
# saveRDS(u, file="postscript_plateaus/u5_wta_2022.rds")
```
```{r}
d5.wta22 <- readRDS("postscript_plateaus/d5_wta_2022.rds")
u5.wta22 <- readRDS("postscript_plateaus/u5_wta_2022.rds")
```
```{r}
plot.path.score(5,d5.wta22,5,u5.wta22,wta.P.90.21,wta.val.2021,
                atp=FALSE,main="WTA 2022",test.year=2)
```
```{r}
plot.path.state(5,d5.wta22,5,u5.wta22,main="WTA 2022")
```

Activate 19; Deactivate 12

## ATP 22

```{r}
# d <- downwards.experiment(c(),atp.P.90.21,atp.val.2021,TRUE,c(),depth=5,test.year=2)
# saveRDS(d, file="postscript_plateaus/d5_atp_2022.rds")
```
```{r}
# u <- upwards.experiment(c(),atp.P.90.21,atp.val.2021,TRUE,c(),depth=5,test.year=2)
# saveRDS(u, file="postscript_plateaus/u5_atp_2022.rds")
```
```{r}
d5.atp22 <- readRDS("postscript_plateaus/d5_atp_2022.rds")
u5.atp22 <- readRDS("postscript_plateaus/u5_atp_2022.rds")
```
```{r}
plot.path.score(5,d5.atp22,5,u5.atp22,atp.P.90.21,atp.val.2021,
                atp=TRUE,main="ATP 2022",test.year=2)
```
```{r}
plot.path.state(5,d5.atp22,5,u5.atp22,main="ATP 2022")
```

Activate 1, 5; Deactivate 15

# Test (Accuracies & Significance (Compared with Basic Pure) & Coverage)

```{r}
atp14.basic <- readRDS("../Results/Individual/atp14_basic_pure")
wta14.basic <- readRDS("../Results/Individual/wta14_basic_pure")
atp18.basic <- readRDS("../Results/Individual/atp18_basic_pure")
wta18.basic <- readRDS("../Results/Individual/wta18_basic_pure")
atp22.basic <- readRDS("../Results/Individual/atp22_basic_pure")
wta22.basic <- readRDS("../Results/Individual/wta22_basic_pure")
atp14.basic.valid <- atp14.basic[which(atp14.basic>0)]
wta14.basic.valid <- wta14.basic[which(wta14.basic>0)]
atp18.basic.valid <- atp18.basic[which(atp18.basic>0)]
wta18.basic.valid <- wta18.basic[which(wta18.basic>0)]
atp22.basic.valid <- atp22.basic[which(atp22.basic>0)]
wta22.basic.valid <- wta22.basic[which(wta22.basic>0)]
```

## WTA 14

Activate 3, 9; Deactivate 15

```{r}
# baseline with no activations (for reference only, not reported in paper)
conduct.experiment(1:19,wta.P.123.14,wta.test.2014,atp=FALSE,test.year=0)$score

# activate 3, 9
res.up <- conduct.experiment((1:19)[-c(3,9)],wta.P.123.14,wta.test.2014,atp=FALSE,test.year=0)
saveRDS(res.up$exact,"../Results/Individual/wta14_ps_up_postscript")
res.up$score
# H0: point-specific less than or equal to basic pure
prop.test(c(sum(wta14.basic.valid>0.5),sum(res.up$result)),
          c(length(wta14.basic.valid),length(res.up$result)),
          alternative="less",correct=FALSE)$p.value

# deactivate 15
res.down <- conduct.experiment(c(15),wta.P.123.14,wta.test.2014,atp=FALSE,test.year=0)
saveRDS(res.down$exact,"../Results/Individual/wta14_ps_down_postscript")
res.down$score
# H0: point-specific less than or equal to basic pure
prop.test(c(sum(wta14.basic.valid>0.5),sum(res.down$result)),
          c(length(wta14.basic.valid),length(res.down$result)),
          alternative="less",correct=FALSE)$p.value
length(res.down$exact)
```

## ATP 14

Activate 8; Deactivate 4, 9

```{r}
# baseline with no activations (for reference only, not reported in paper)
conduct.experiment(1:19,atp.P.123.14,atp.test.2014,atp=TRUE,test.year=0)$score

# activate 8
res.up <- conduct.experiment((1:19)[-c(8)],atp.P.123.14,atp.test.2014,atp=TRUE,test.year=0)
saveRDS(res.up$exact,"../Results/Individual/atp14_ps_up_postscript")
res.up$score
# H0: point-specific less than or equal to basic pure
prop.test(c(sum(atp14.basic.valid>0.5),sum(res.up$result)),
          c(length(atp14.basic.valid),length(res.up$result)),
          alternative="less",correct=FALSE)$p.value

# deactivate 4, 9
res.down <- conduct.experiment(c(4,9),atp.P.123.14,atp.test.2014,atp=TRUE,test.year=0)
saveRDS(res.down$exact,"../Results/Individual/atp14_ps_down_postscript")
res.down$score
# H0: point-specific less than or equal to basic pure
prop.test(c(sum(atp14.basic.valid>0.5),sum(res.down$result)),
          c(length(atp14.basic.valid),length(res.down$result)),
          alternative="less",correct=FALSE)$p.value
length(res.down$exact)
```

## WTA 18

Activate 3, 6; Deactivate 19

```{r}
# baseline with no activations (for reference only, not reported in paper)
conduct.experiment(1:19,wta.P.567.18,wta.test.2018,atp=FALSE,test.year=0)$score

# activate 3, 6
res.up <- conduct.experiment((1:19)[-c(3,6)],wta.P.567.18,wta.test.2018,atp=FALSE,test.year=0)
saveRDS(res.up$exact,"../Results/Individual/wta18_ps_up_postscript")
res.up$score
# H0: point-specific less than or equal to basic pure
prop.test(c(sum(wta18.basic.valid>0.5),sum(res.up$result)),
          c(length(wta18.basic.valid),length(res.up$result)),
          alternative="less",correct=FALSE)$p.value

# deactivate 19
res.down <- conduct.experiment(c(19),wta.P.567.18,wta.test.2018,atp=FALSE,test.year=0)
saveRDS(res.down$exact,"../Results/Individual/wta18_ps_down_postscript")
res.down$score
# H0: point-specific less than or equal to basic pure
prop.test(c(sum(wta18.basic.valid>0.5),sum(res.down$result)),
          c(length(wta18.basic.valid),length(res.down$result)),
          alternative="less",correct=FALSE)$p.value
length(res.down$exact)
```

## ATP 18

Activate 9, 14; Deactivate 19

```{r}
# baseline with no activations (for reference only, not reported in paper)
conduct.experiment(1:19,atp.P.567.18,atp.test.2018,atp=TRUE,test.year=0)$score

# activate 9, 14
res.up <- conduct.experiment((1:19)[-c(9,14)],atp.P.567.18,atp.test.2018,atp=TRUE,test.year=0)
saveRDS(res.up$exact,"../Results/Individual/atp18_ps_up_postscript")
res.up$score
# H0: point-specific less than or equal to basic pure
prop.test(c(sum(atp18.basic.valid>0.5),sum(res.up$result)),
          c(length(atp18.basic.valid),length(res.up$result)),
          alternative="less",correct=FALSE)$p.value

# deactivate 19
res.down <- conduct.experiment(c(19),atp.P.567.18,atp.test.2018,atp=TRUE,test.year=0)
saveRDS(res.down$exact,"../Results/Individual/atp18_ps_down_postscript")
res.down$score
# H0: point-specific less than or equal to basic pure
prop.test(c(sum(atp18.basic.valid>0.5),sum(res.down$result)),
          c(length(atp18.basic.valid),length(res.down$result)),
          alternative="less",correct=FALSE)$p.value
length(res.down$exact)
```

## WTA 22

Activate 19; Deactivate 12

```{r}
# baseline with no activations (for reference only, not reported in paper)
conduct.experiment(1:19,wta.P.901.22,wta.test.2022,atp=FALSE,test.year=2)$score

# activate 19
res.up <- conduct.experiment((1:19)[-c(19)],wta.P.901.22,wta.test.2022,atp=FALSE,test.year=2)
saveRDS(res.up$exact,"../Results/Individual/wta22_ps_up_postscript")
res.up$score
# H0: point-specific less than or equal to basic pure
prop.test(c(sum(wta22.basic.valid>0.5),sum(res.up$result)),
          c(length(wta22.basic.valid),length(res.up$result)),
          alternative="less",correct=FALSE)$p.value

# deactivate 12
res.down <- conduct.experiment(c(12),wta.P.901.22,wta.test.2022,atp=FALSE,test.year=2)
saveRDS(res.down$exact,"../Results/Individual/wta22_ps_down_postscript")
res.down$score
# H0: point-specific less than or equal to basic pure
prop.test(c(sum(wta22.basic.valid>0.5),sum(res.down$result)),
          c(length(wta22.basic.valid),length(res.down$result)),
          alternative="less",correct=FALSE)$p.value
length(res.down$exact)
```

## ATP 22

Activate 1, 5; Deactivate 15

```{r}
# baseline with no activations (for reference only, not reported in paper)
conduct.experiment(1:19,atp.P.901.22,atp.test.2022,atp=TRUE,test.year=2)$score

# activate 1, 5
res.up <- conduct.experiment((1:19)[-c(1,5)],atp.P.901.22,atp.test.2022,atp=TRUE,test.year=2)
saveRDS(res.up$exact,"../Results/Individual/atp22_ps_up_postscript")
res.up$score
# H0: point-specific less than or equal to basic pure
prop.test(c(sum(atp22.basic.valid>0.5),sum(res.up$result)),
          c(length(atp22.basic.valid),length(res.up$result)),
          alternative="less",correct=FALSE)$p.value

# deactivate 15
res.down <- conduct.experiment(c(15),atp.P.901.22,atp.test.2022,atp=TRUE,test.year=2)
saveRDS(res.down$exact,"../Results/Individual/atp22_ps_down_postscript")
res.down$score
# H0: point-specific less than or equal to basic pure
prop.test(c(sum(atp22.basic.valid>0.5),sum(res.down$result)),
          c(length(atp22.basic.valid),length(res.down$result)),
          alternative="less",correct=FALSE)$p.value
length(res.down$exact)
```

# Significance of Validation Plateaus

## WTA 14

```{r}
# H0: accuracy after activation(deactivation) is less than or equal to initial
#     accuracy with all states deactivated(activated)
n <- length(conduct.experiment(1:19,wta.P.12.13,wta.val.2013,atp=FALSE,test.year=0)$res)
prop.test(c(sum(conduct.experiment(1:19,wta.P.12.13,wta.val.2013,atp=FALSE,test.year=0)$res),
            u5.wta14[[1]][[1]][2]*n),
          c(n,n),alternative="less",correct=FALSE)$p.value
prop.test(c(sum(conduct.experiment(c(),wta.P.12.13,wta.val.2013,atp=FALSE,test.year=0)$res),
            d5.wta14[[1]][[1]][1]*n),
          c(n,n),alternative="less",correct=FALSE)$p.value
```

## ATP 14

```{r}
# H0: accuracy after activation(deactivation) is less than or equal to initial
#     accuracy with all states deactivated(activated)
n <- length(conduct.experiment(1:19,atp.P.12.13,atp.val.2013,atp=TRUE,test.year=0)$res)
prop.test(c(sum(conduct.experiment(1:19,atp.P.12.13,atp.val.2013,atp=TRUE,test.year=0)$res),
            u5.atp14[[1]][[1]][1]*n),
          c(n,n),alternative="less",correct=FALSE)$p.value
prop.test(c(sum(conduct.experiment(c(),atp.P.12.13,atp.val.2013,atp=TRUE,test.year=0)$res),
            d5.atp14[[1]][[1]][2]*n),
          c(n,n),alternative="less",correct=FALSE)$p.value
```

## WTA 18

```{r}
# H0: accuracy after activation(deactivation) is less than or equal to initial
#     accuracy with all states deactivated(activated)
n <- length(conduct.experiment(1:19,wta.P.56.17,wta.val.2017,atp=FALSE,test.year=0)$res)
prop.test(c(sum(conduct.experiment(1:19,wta.P.56.17,wta.val.2017,atp=FALSE,test.year=0)$res),
            u5.wta18[[1]][[1]][2]*n),
          c(n,n),alternative="less",correct=FALSE)$p.value
prop.test(c(sum(conduct.experiment(c(),wta.P.56.17,wta.val.2017,atp=FALSE,test.year=0)$res),
            d5.wta18[[1]][[1]][1]*n),
          c(n,n),alternative="less",correct=FALSE)$p.value
```

## ATP 18

```{r}
# H0: accuracy after activation(deactivation) is less than or equal to initial
#     accuracy with all states deactivated(activated)
n <- length(conduct.experiment(1:19,atp.P.56.17,atp.val.2017,atp=TRUE,test.year=0)$res)
prop.test(c(sum(conduct.experiment(1:19,atp.P.56.17,atp.val.2017,atp=TRUE,test.year=0)$res),
            u5.atp18[[1]][[1]][2]*n),
          c(n,n),alternative="less",correct=FALSE)$p.value
prop.test(c(sum(conduct.experiment(c(),atp.P.56.17,atp.val.2017,atp=TRUE,test.year=0)$res),
            d5.atp18[[1]][[1]][1]*n),
          c(n,n),alternative="less",correct=FALSE)$p.value
```

## WTA 22

```{r}
# H0: accuracy after activation(deactivation) is less than or equal to initial
#     accuracy with all states deactivated(activated)
n <- length(conduct.experiment(1:19,wta.P.90.21,wta.val.2021,atp=FALSE,test.year=2)$res)
prop.test(c(sum(conduct.experiment(1:19,wta.P.90.21,wta.val.2021,atp=FALSE,test.year=2)$res),
            u5.wta22[[1]][[1]][1]*n),
          c(n,n),alternative="less",correct=FALSE)$p.value
prop.test(c(sum(conduct.experiment(c(),wta.P.90.21,wta.val.2021,atp=FALSE,test.year=2)$res),
            d5.wta22[[1]][[1]][1]*n),
          c(n,n),alternative="less",correct=FALSE)$p.value
```

## ATP 22

```{r}
# H0: accuracy after activation(deactivation) is less than or equal to initial
#     accuracy with all states deactivated(activated)
n <- length(conduct.experiment(1:19,atp.P.90.21,atp.val.2021,atp=TRUE,test.year=2)$res)
prop.test(c(sum(conduct.experiment(1:19,atp.P.90.21,atp.val.2021,atp=TRUE,test.year=2)$res),
            u5.atp22[[1]][[1]][2]*n),
          c(n,n),alternative="less",correct=FALSE)$p.value
prop.test(c(sum(conduct.experiment(c(),atp.P.90.21,atp.val.2021,atp=TRUE,test.year=2)$res),
            d5.atp22[[1]][[1]][1]*n),
          c(n,n),alternative="less",correct=FALSE)$p.value
```
