---
title: "Cat 2 (Notebooks 2,5,6,7) Consolidation and Plot Generation"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Prep Functions

```{r functions}
# main function is match.win.prob
source("case_patching.R")

# 3 helper functions

get.unique.players <- function(testset){
  # takes the players in the test set and returns vector
  # containing unique players in the test set
  names <- c(testset$winner_name,testset$loser_name)
  names <- unique(names)
  return(names)
}

get.equiv.names <- function(fullname){
  # returns vector of equivalent names in different formats
  # according to the fullname given
  # fullname ideally from get.unique.players output
  # More special examples:
  #   Alejandro Davidovich Fokina -> A Davidovich Fokina & A. Davidovich Fokina
  #   Pierre Hugues Herbert -> P Herbert & Ph Herbert & P. Herbert
  #   Alex De Minaur -> A. De Minaur & Alex de Minaur & A De Minaur
  #   Karolina Pliskova -> K. Pliskova & Ka. Pliskova & Ka Pliskova
  #   Kristyna Pliskova -> K. Pliskova & Kr. Pliskova & Kr Pliskova
  #   some cases manually remediated (see misc. google doc)
  #   but quick manual remediation can't help if player in test set has middle name
  #   and full name isn't in pbp training set.
  #   Function tries to account for this as follows.
  
  # Alex Bee Caine -> c("A. Caine", "A Caine", "A. Bee Caine", "A Bee Caine",
  #                     "Ab Caine", "A Bee-Caine", "A. Bee-Caine")
  
  # This method risks picking up on players with same last name and first letter
  # But this is unlikely as the pbp training set only 1 case of this - Kr&Ka Pliskova
  # And this was picked up since there were 2 characters before the space
  
  parts <- strsplit(fullname,split=" ")[[1]]
  n <- length(parts)
  first.letter <- substr(parts[1],1,1)
  equiv <- c(fullname,
             paste(first.letter," ",parts[n],sep=""),
             paste(first.letter,"."," ",parts[n],sep=""))
  if (n > 2){
    rest <- ""
    rest.dash <- ""
    for (i in 1:(n-1)){
      rest <- paste(rest," ",parts[i+1],sep="")
      rest.dash <- paste(rest.dash,parts[i+1],sep="-")
    }
    rest.dash <- substr(rest.dash,2,nchar(rest.dash)) # get rid of first dash
    first.middle.name.letter <- tolower(substr(parts[2],1,1))
    rest.more <- "" # for if the name has four or more parts
    for (i in 1:(n-2)){
      rest.more <- paste(rest.more," ",parts[i+2],sep="")
    }
    # rest contains the first space, rest.dash doesn't
    equiv <- c(equiv, paste(first.letter,rest,sep=""),
               paste(first.letter,".",rest,sep=""),
               paste(first.letter," ",rest.dash,sep=""),
               paste(first.letter,"."," ",rest.dash,sep=""),
               paste(first.letter,first.middle.name.letter,rest.more,sep=""))
  }
  return(equiv)
}

get.aggr.by.state <- function(entry){
  # extract serve won & serve total fields for a player
  # without surface distinction
  ret <- rep(0,38)
  for (i in 1:18){
    # odd indices for pts won, even for total
    ret[2*i-1] <- entry[[3+12*i]]+entry[[7+12*i]]+entry[[11+12*i]]
    ret[2*i] <- entry[[2+12*i]]+entry[[6+12*i]]+entry[[10+12*i]]
  }
  ret[37] <- entry[[3]]+entry[[7]]+entry[[11]]
  ret[38] <- entry[[2]]+entry[[6]]+entry[[10]]
  return(ret)
}

create.p.vector <- function(tst.names,pbp){
  # returns a dataframe with the rows in the order of names,
  # the columns being p's for states 1-18 and then t (tiebreak)
  # final column is overall p regardless of state by taking total won / total serve
  # names usually from get.unique.players on test data set
  # pbp is the point-by-point data given
  # note p-vectors not surface specific
  
  n <- length(tst.names)
  m <- nrow(pbp)
  pbp.name <- pbp$name
  aggr <- matrix(0,nrow=n,ncol=38) # 38=2x19, taking won & total to divide later
  for (i in 1:n){
    equiv <- get.equiv.names(tst.names[i])
    p <- length(equiv)
    for (j in 1:p){
      for (l in 1:m){
        # check 1 by 1 since pbp has non-unique names after manual remediation
        if (equiv[j]==pbp.name[l]){
          more.aggr <- get.aggr.by.state(pbp[l,])
          aggr[i,] <- aggr[i,]+more.aggr
        }
      }
    }
  }
  # now divide odd cols by even cols to obtain p's
  output <- matrix(0,nrow=n,ncol=20)
  output <- data.frame(output, row.names=tst.names)
  for (i in 1:n){
    for (j in 1:19){
      output[i,j] <- aggr[i,2*j-1]/aggr[i,2*j]
    } # note below first seq() output will end at 37
    output[i,20] <- sum(aggr[i,seq(1,38,by=2)])/sum(aggr[i,seq(2,38,by=2)])
  }
  return(output)
}

grand.slams <- c("Australian Open","Roland Garros","Wimbledon","US Open","Us Open")
# overall function to do experiments with
conduct.experiment <- function(inactive.states, P, test.set, atp=TRUE, test.year=0){
  # inactive.states:
  #   vector containing states (19 for tiebreak) to deactivate, i.e. 
  #   replace the state's unique p with the player's overall p
  # P:
  #   data.frame containing players' individual p vectors
  #   usually obtained via create.p.vector output
  # test.set:
  #   data set used to test accuracy of prediction
  # atp:
  #   boolean defaulted to true if test.set is ATP data
  # test.year:
  #   three valid values: 0,1,2
  #   0 for up to 2018, 1 for 2019 to 2021 inclusive, 2 for 2022 beyond
  
  # make copy of P and change copy to align with specified inactive.states
  cP <- P[,1:19]
  cP[,inactive.states] <- P[,20]
  
  # record exact probability values from model
  # so we can examine closer if we want
  n <- nrow(test.set)
  exact <- rep(0,n)
  
  # experiment begins
  pbp.names <- rownames(cP)
  for (i in 1:n){
    matchup <- test.set[i,]
    winner <- matchup$winner_name
    loser <- matchup$loser_name
    inds <- match(c(winner,loser),pbp.names)
    winner.P <- unname(unlist(cP[inds[1],]))
    loser.P <- unname(unlist(cP[inds[2],]))
    if (matchup$tourney_name %in% grand.slams){
      if (test.year==0){
        if (matchup$tourney_name=="US Open"){
          # here we do something that many cases below will also do
          # atp is TRUE if the match is an ATP match, x+ATP is a numeric value
          # so x+ATP can be directly used for format without if-statements 
          # this also works because the format codes were wta/atp alternating
          # with the wta/atp code pairs only differing in playing to 3 or 5 sets
          exact[i] <- match.win.prob(p1=winner.P,p2=loser.P,format=0+atp)
        } else {
          exact[i] <- match.win.prob(p1=winner.P,p2=loser.P,format=4+atp)
        }
      } else if (test.year==1){
        # no overlap of rules from 2019 to 2021, so we have to code all cases
        if (matchup$tourney_name=="Australian Open"){
          exact[i] <- match.win.prob(p1=winner.P,p2=loser.P,format=2+atp)
        } else if (matchup$tourney_name=="Roland Garros"){
          exact[i] <- match.win.prob(p1=winner.P,p2=loser.P,format=4+atp)
        } else if (matchup$tourney_name=="Wimbledon"){
          exact[i] <- match.win.prob(p1=winner.P,p2=loser.P,format=6+atp)
        } else { # matchup is from US Open
          exact[i] <- match.win.prob(p1=winner.P,p2=loser.P,format=0+atp)
        }
      } else{ # test.year is 2, all grand slams formats standardized in 2022
        exact[i] <- match.win.prob(p1=winner.P,p2=loser.P,format=2+atp)
      }
    } else {
      exact[i] <- match.win.prob(p1=winner.P,p2=loser.P)
    }
  }
  res <- exact > 0.5
  return(list("score"=mean(res),"result"=res,"exact"=exact))
}

downwards.wrapper <- function(deactivate,P,testset,atp,test.year){
  # atp is boolean for if testset is for ATP
  scores <- rep(0,19)
  if (length(deactivate)==0){
    options <- 1:19
  } else {
    options <- (1:19)[-deactivate]
  }
  for (i in options){
    scores[i] <- conduct.experiment(c(i,deactivate),P,testset,atp,test.year)$score
    # so deactivated state's indices will have 0
  }
  return(list("max"=max(scores),"candidates"=which(scores==max(scores))))
}
upwards.wrapper <- function(activate,P,testset,atp,test.year){
  # atp is boolean for if testset is for ATP
  if (length(activate)==0){
    deactivate <- 1:19
  } else {
    deactivate <- (1:19)[-activate]
  }
  scores <- rep(0,19)
  for (i in deactivate){
    deactivate.no.i <- (1:19)[-c(activate,i)]
    scores[i] <- conduct.experiment(deactivate.no.i,P,testset,atp,test.year)$score
    # activated state's indices will have 0
  }
  return(list("max"=max(scores),"candidates"=which(scores==max(scores))))
}

downwards.experiment <- function(starting.states,P,testset,atp,previous.scores,
                                 depth=18,test.year=2){
  
  diverge.lists <- c()
  deactivate <- starting.states
  
  # through recursion, aim to combine all ovr.lists produced
  ovr.list <- list() # to contain lists containing state & score vectors
  path <- list()
  # if no previous scores, can initialize NULL list element for scores:
  # https://stackoverflow.com/questions/45666451/r-adding-an-empty-vector-to-a-list
  if (length(previous.scores)==0){
    path[1] <- list(NULL)
  } else {
    path[[1]] <- previous.scores # to record best scores of this path
  }
  # path[[2]] to record states deactivated, but does not need initialization
  
  while(length(deactivate) < depth){
    
    res <- downwards.wrapper(deactivate,P,testset,atp,test.year)
    score <- res$max
    cands <- res$candidates
    scores.sofar <- c(path[[1]],score)
    
    l <- length(cands)
    if (l>1){
      # recursion call
      for (i in 2:l){
        diverge.lists <- c(
          diverge.lists,
          downwards.experiment(c(deactivate,cands[i]),P,testset,atp,scores.sofar,
                               depth,test.year))
      }
    }
    path[[1]] <- scores.sofar
    deactivate <- c(deactivate,cands[1])
    path[[2]] <- deactivate
  }
  path[[2]] <- deactivate
  ovr.list[[1]] <- path
  ovr.list <- c(ovr.list,diverge.lists)
  
  return(ovr.list)
}

upwards.experiment <- function(starting.states,P,testset,atp,previous.scores,
                               depth=18,test.year=2){
  
  diverge.lists <- c()
  activate <- starting.states
  
  # through recursion, aim to combine all ovr.lists produced
  ovr.list <- list() # to contain lists containing state & score vectors
  path <- list()
  # if no previous scores, can initialize NULL list element for scores:
  # https://stackoverflow.com/questions/45666451/r-adding-an-empty-vector-to-a-list
  if (length(previous.scores)==0){
    path[1] <- list(NULL)
  } else {
    path[[1]] <- previous.scores # to record best scores of this path
  }
  # path[[2]] to record states deactivated, but does not need initialization
  
  while(length(activate) < depth){
    
    res <- upwards.wrapper(activate,P,testset,atp,test.year)
    score <- res$max
    cands <- res$candidates
    scores.sofar <- c(path[[1]],score)
    
    l <- length(cands)
    if (l>1){
      # recursion call
      for (i in 2:l){
        diverge.lists <- c(
          diverge.lists,
          upwards.experiment(c(activate,cands[i]),P,testset,atp,scores.sofar,
                             depth,test.year))
      }
    }
    path[[1]] <- scores.sofar
    activate <- c(activate,cands[1])
    path[[2]] <- activate
  }
  path[[2]] <- activate
  ovr.list[[1]] <- path
  ovr.list <- c(ovr.list,diverge.lists)
  
  return(ovr.list)
}

plot.path.score <- function(n.down,dat.down,n.up,dat.up,
                      P, test.set, atp=TRUE, main="Score",
                      ylim.lower=0.55,ylim.upper=0.7,hide.axis=FALSE){
  # n - length of path given
  # dat - data saved containing paths
  # ylim.lower(upper) - ylim for plot, set to around 0(20) for type=2
  
  baseline.down <- conduct.experiment(c(),P,test.set,atp)$score
  baseline.up <- conduct.experiment(1:19,P,test.set,atp)$score
  
  if (hide.axis) {
    plot(0:n.up,c(baseline.up,dat.up[[1]][[1]]),'l',
         xlim=c(0,20),ylim=c(ylim.lower,ylim.upper),main=main)
  } else {
    plot(0:n.up,c(baseline.up,dat.up[[1]][[1]]),'l',
         xlim=c(0,20),ylim=c(ylim.lower,ylim.upper),main=main,
         ylab="Score",xlab="# States Activated")
  }
  for (i in 2:length(dat.up)){
    lines(0:n.up,c(baseline.up,dat.up[[i]][[1]]))
  }
  for (i in 1:length(dat.down)){
    lines(20:(20-n.down),c(baseline.down,dat.down[[i]][[1]]))
  }
}

plot.path.state <- function(n.down,dat.down,n.up,dat.up,main="States",
                            ylim.lower=0,ylim.upper=20,hide.axis=FALSE){
  # n - length of path given
  # dat - data saved containing paths
  # ylim.lower(upper) - ylim for plot, set to around 0(20) for state
  if (hide.axis) {
    plot(1:n.up,dat.up[[1]][[2]],'l',
         xlim=c(1,19),ylim=c(ylim.lower,ylim.upper),main=main)
  } else {
    plot(1:n.up,dat.up[[1]][[2]],'l',
         xlim=c(1,19),ylim=c(ylim.lower,ylim.upper),main=main,
         ylab="States",xlab="# States Activated")
  }
  for (i in 2:length(dat.up)){
    lines(1:n.up,dat.up[[i]][[2]])
  }
  for (i in 1:length(dat.down)){
    lines(19:(20-n.down),dat.down[[i]][[2]])
  }
}
```

# Data

```{r data}
# testing data
atp.test.2014 <- read.csv('../Data Lake/Experiments/2014_atp_testing.csv')
wta.test.2014 <- read.csv('../Data Lake/Experiments/2014_wta_testing.csv')
atp.test.2018 <- read.csv('../Data Lake/Experiments/2018_atp_testing.csv')
wta.test.2018 <- read.csv('../Data Lake/Experiments/2018_wta_testing.csv')
atp.test.2022 <- read.csv('../Data Lake/Experiments/2022_atp_testing.csv')
wta.test.2022 <- read.csv('../Data Lake/Experiments/2022_wta_testing.csv')
# remove incomplete matches for test sets
ic.match <- function(score) grep("[A-Za-z]",score)
atp.test.2014 <- atp.test.2014[-ic.match(atp.test.2014$score),]
wta.test.2014 <- wta.test.2014[-ic.match(wta.test.2014$score),]
atp.test.2018 <- atp.test.2018[-ic.match(atp.test.2018$score),]
wta.test.2018 <- wta.test.2018[-ic.match(wta.test.2018$score),]
atp.test.2022 <- atp.test.2022[-ic.match(atp.test.2022$score),]
wta.test.2022 <- wta.test.2022[-ic.match(wta.test.2022$score),]
# Point-by-Point data
pbp.123 <- read.csv('../Data Lake/Players/2011-2013_pbp_individual.csv')
pbp.567 <- read.csv('../Data Lake/Players/2015-2017_pbp_individual.csv')
pbp.901 <- read.csv('../Data Lake/Players/2019-2021_pbp_individual.csv')
# Getting unique names
atp.names.2014 <- get.unique.players(atp.test.2014)
atp.names.2018 <- get.unique.players(atp.test.2018)
atp.names.2022 <- get.unique.players(atp.test.2022)
wta.names.2014 <- get.unique.players(wta.test.2014)
wta.names.2018 <- get.unique.players(wta.test.2018)
wta.names.2022 <- get.unique.players(wta.test.2022)
# create p vectors
atp.P.123 <- create.p.vector(atp.names.2014,pbp.123)
atp.P.567 <- create.p.vector(atp.names.2018,pbp.567)
atp.P.901 <- create.p.vector(atp.names.2022,pbp.901)
wta.P.123 <- create.p.vector(wta.names.2014,pbp.123)
wta.P.567 <- create.p.vector(wta.names.2018,pbp.567)
wta.P.901 <- create.p.vector(wta.names.2022,pbp.901)
for (i in 1:ncol(atp.P.123)){
  atp.P.123[which(is.na(atp.P.123[,i])),i] <- 
    mean(atp.P.123[-which(is.na(atp.P.123[,i])),i])
}
for (i in 1:ncol(atp.P.567)){
  atp.P.567[which(is.na(atp.P.567[,i])),i] <- 
    mean(atp.P.567[-which(is.na(atp.P.567[,i])),i])
}
for (i in 1:ncol(atp.P.901)){
  atp.P.901[which(is.na(atp.P.901[,i])),i] <- 
    mean(atp.P.901[-which(is.na(atp.P.901[,i])),i])
}
for (i in 1:ncol(wta.P.123)){
  wta.P.123[which(is.na(wta.P.123[,i])),i] <- 
    mean(wta.P.123[-which(is.na(wta.P.123[,i])),i])
}
for (i in 1:ncol(wta.P.567)){
  wta.P.567[which(is.na(wta.P.567[,i])),i] <- 
    mean(wta.P.567[-which(is.na(wta.P.567[,i])),i])
}
for (i in 1:ncol(wta.P.901)){
  wta.P.901[which(is.na(wta.P.901[,i])),i] <- 
    mean(wta.P.901[-which(is.na(wta.P.901[,i])),i])
}
```

# Initial Results

## ATP 14

```{r eval=FALSE, include=TRUE}
ld6 <- downwards.experiment(c(),atp.P.123,atp.test.2014,TRUE,c(),depth=6,test.year=0)
```
```{r eval=FALSE, include=TRUE}
saveRDS(ld6, file="cat2_res/ld6_atp_2014.rds")
```
```{r}
ld6.atp.2014 <- readRDS("cat2_res/ld6_atp_2014.rds")
```
```{r eval=FALSE, include=TRUE}
lu6 <- upwards.experiment(c(),atp.P.123,atp.test.2014,TRUE,c(),depth=6,test.year=0)
```
```{r eval=FALSE, include=TRUE}
saveRDS(lu6, file="cat2_res/lu6_atp_2014.rds")
```
```{r}
lu6.atp.2014 <- readRDS("cat2_res/lu6_atp_2014.rds")
```
```{r}
plot.path.score(6,ld6.atp.2014,6,lu6.atp.2014,atp.P.123,atp.test.2014,main="ATP 2014")
```
```{r}
plot.path.state(6,ld6.atp.2014,6,lu6.atp.2014,main="ATP 2014")
```

## WTA 14

```{r eval=FALSE, include=TRUE}
ld7 <- downwards.experiment(c(),wta.P.123,wta.test.2014,TRUE,c(),depth=7,test.year=0)
```
```{r eval=FALSE, include=TRUE}
saveRDS(ld7, file="cat2_res/ld7_wta_2014.rds")
```
```{r}
ld7.wta.2014 <- readRDS("cat2_res/ld7_wta_2014.rds")
```
```{r eval=FALSE, include=TRUE}
lu6 <- upwards.experiment(c(),wta.P.123,wta.test.2014,TRUE,c(),depth=6,test.year=0)
```
```{r eval=FALSE, include=TRUE}
saveRDS(lu6, file="cat2_res/lu6_wta_2014.rds")
```
```{r}
lu6.wta.2014 <- readRDS("cat2_res/lu6_wta_2014.rds")
```
```{r}
plot.path.score(7,ld7.wta.2014,6,lu6.wta.2014,wta.P.123,wta.test.2014,main="WTA 2014")
```
```{r}
plot.path.state(7,ld7.wta.2014,6,lu6.wta.2014,main="WTA 2014")
```

## ATP 18

```{r eval=FALSE, include=TRUE}
ld7 <- downwards.experiment(c(),atp.P.567,atp.test.2018,TRUE,c(),depth=7,test.year=0)
```
```{r eval=FALSE, include=TRUE}
saveRDS(ld7, file="cat2_res/ld7_atp_2018.rds")
```
```{r}
ld7.atp.2018 <- readRDS("cat2_res/ld7_atp_2018.rds")
```
```{r eval=FALSE, include=TRUE}
lu7 <- upwards.experiment(c(),atp.P.567,atp.test.2018,TRUE,c(),depth=7,test.year=0)
```
```{r eval=FALSE, include=TRUE}
saveRDS(lu7, file="cat2_res/lu7_atp_2018.rds")
```
```{r}
lu7.atp.2018 <- readRDS("cat2_res/lu7_atp_2018.rds")
```
```{r}
plot.path.score(7,ld7.atp.2018,7,lu7.atp.2018,atp.P.567,atp.test.2018,main="ATP 2018")
```
```{r}
plot.path.state(7,ld7.atp.2018,7,lu7.atp.2018,main="ATP 2018")
```

## WTA 18

```{r eval=FALSE, include=TRUE}
ld7 <- downwards.experiment(c(),wta.P.567,wta.test.2018,TRUE,c(),depth=7,test.year=0)
```
```{r eval=FALSE, include=TRUE}
saveRDS(ld7, file="cat2_res/ld7_wta_2018.rds")
```
```{r}
ld7.wta.2018 <- readRDS("cat2_res/ld7_wta_2018.rds")
```
```{r eval=FALSE, include=TRUE}
lu7 <- upwards.experiment(c(),wta.P.567,wta.test.2018,TRUE,c(),depth=7,test.year=0)
```
```{r eval=FALSE, include=TRUE}
saveRDS(lu7, file="cat2_res/lu7_wta_2018.rds")
```
```{r}
lu7.wta.2018 <- readRDS("cat2_res/lu7_wta_2018.rds")
```
```{r}
plot.path.score(7,ld7.wta.2018,7,lu7.wta.2018,wta.P.567,wta.test.2018,main="WTA 2018",
                ylim.lower = 0.4, ylim.upper = 0.65)
```
```{r}
plot.path.state(7,ld7.wta.2018,7,lu7.wta.2018,main="WTA 2018")
```

## ATP 22

```{r eval=FALSE, include=TRUE}
ld7 <- downwards.experiment(c(),atp.P.901,atp.test.2022,TRUE,c(),depth=7,test.year=2)
```
```{r eval=FALSE, include=TRUE}
saveRDS(ld7, file="cat2_res/ld7_atp_2022.rds")
```
```{r}
ld7.atp.2022 <- readRDS("cat2_res/ld7_atp_2022.rds")
```
```{r eval=FALSE, include=TRUE}
lu7 <- upwards.experiment(c(),atp.P.901,atp.test.2022,TRUE,c(),depth=7,test.year=2)
```
```{r eval=FALSE, include=TRUE}
saveRDS(lu7, file="cat2_res/lu7_atp_2022.rds")
```
```{r}
lu7.atp.2022 <- readRDS("cat2_res/lu7_atp_2022.rds")
```
```{r}
plot.path.score(7,ld7.atp.2022,7,lu7.atp.2022,atp.P.901,atp.test.2022,main="ATP 2022")
```
```{r}
plot.path.state(7,ld7.atp.2022,7,lu7.atp.2022,main="ATP 2022")
```

## WTA 22

```{r eval=FALSE, include=TRUE}
ld7 <- downwards.experiment(c(),wta.P.901,wta.test.2022,TRUE,c(),depth=7,test.year=2)
```
```{r eval=FALSE, include=TRUE}
saveRDS(ld7, file="cat2_res/ld7_wta_2022.rds")
```
```{r}
ld7.wta.2022 <- readRDS("cat2_res/ld7_wta_2022.rds")
```
```{r eval=FALSE, include=TRUE}
lu7 <- upwards.experiment(c(),wta.P.901,wta.test.2022,TRUE,c(),depth=7,test.year=2)
```
```{r eval=FALSE, include=TRUE}
saveRDS(lu7, file="cat2_res/lu7_wta_2022.rds")
```
```{r}
lu7.wta.2022 <- readRDS("cat2_res/lu7_wta_2022.rds")
```
```{r}
plot.path.score(7,ld7.wta.2022,7,lu7.wta.2022,wta.P.901,wta.test.2022,main="WTA 2022")
```
```{r}
plot.path.state(7,ld7.wta.2022,7,lu7.wta.2022,main="WTA 2022")
```

## Plots (Scores & States) 2x3 Together

```{r}
par(mfrow=c(2,3))
plot.path.score(6,ld6.atp.2014,6,lu6.atp.2014,atp.P.123,atp.test.2014,main="ATP 2014")
plot.path.score(7,ld7.atp.2018,7,lu7.atp.2018,atp.P.567,atp.test.2018,main="ATP 2018")
plot.path.score(7,ld7.atp.2022,7,lu7.atp.2022,atp.P.901,atp.test.2022,main="ATP 2022")
plot.path.score(7,ld7.wta.2014,6,lu6.wta.2014,wta.P.123,wta.test.2014,main="WTA 2014")
plot.path.score(7,ld7.wta.2018,7,lu7.wta.2018,wta.P.567,wta.test.2018,main="WTA 2018",
                ylim.lower = 0.4, ylim.upper = 0.65)
plot.path.score(7,ld7.wta.2022,7,lu7.wta.2022,wta.P.901,wta.test.2022,main="WTA 2022")
```

```{r}
par(mfrow=c(2,3))
plot.path.state(6,ld6.atp.2014,6,lu6.atp.2014,main="ATP 2014")
plot.path.state(7,ld7.atp.2018,7,lu7.atp.2018,main="ATP 2018")
plot.path.state(7,ld7.atp.2022,7,lu7.atp.2022,main="ATP 2022")
plot.path.state(7,ld7.wta.2014,6,lu6.wta.2014,main="WTA 2014")
plot.path.state(7,ld7.wta.2018,7,lu7.wta.2018,main="WTA 2018")
plot.path.state(7,ld7.wta.2022,7,lu7.wta.2022,main="WTA 2022")
```

# Initial Results Drilldown 

(players after * only due to duplicates or one strong entry) ([]names for particularly strong evidence)

## ATP 14

Activate: 1,8.
S: * Novak Djokovic
W: * Milos Raonic

Deactivate: 19,13.
S: Novak Djokovic * David Ferrer, Roger Federer
W: Ernests Gulbis * Milos Raonic, Philipp Kohlschreiber, Tommy Robredo

```{r}
ex <- atp.test.2014[,c(3,5,6)]
ex$all.deact <- conduct.experiment(1:19,atp.P.123,atp.test.2014,test.year=0)$result
ex$all.act <- conduct.experiment(c(),atp.P.123,atp.test.2014,test.year=0)$result
ex$act <- conduct.experiment((1:19)[-c(1,8)],atp.P.123,atp.test.2014,test.year=0)$result
ex$deact <- conduct.experiment(c(13,19),atp.P.123,atp.test.2014,test.year=0)$result
ex$plat <- ex$act & ex$deact
```
```{r}
# tmp <- ex[which(ex$all.deact!=ex$act),c(1,2,3,4,6)]
# tmp <- ex[which(ex$all.act!=ex$deact),c(1,2,3,5,7)]
```

## WTA 14

Activate: 17.
S: Caroline Wozniacki * Petra Kvitova
W: * Maria Sharapova, Agnieszka Radwanska

Deactivate: 18,2.
S: Lucie Safarova, Sara Errani * Caroline Wozniacki, Caroline Garcia
W: * Agnieszka Radwanska

```{r}
ex <- wta.test.2014[,c(3,5,6)]
ex$all.deact <- conduct.experiment(1:19,wta.P.123,wta.test.2014,test.year=0)$result
ex$all.act <- conduct.experiment(c(),wta.P.123,wta.test.2014,test.year=0)$result
ex$act <- conduct.experiment((1:19)[-c(17)],wta.P.123,wta.test.2014,test.year=0)$result
ex$deact <- conduct.experiment(c(2,18),wta.P.123,wta.test.2014,test.year=0)$result
ex$plat <- ex$act & ex$deact
```
```{r}
# tmp <- ex[which(ex$all.deact!=ex$act),c(1,2,3,4,6)]
# tmp <- ex[which(ex$all.act!=ex$deact),c(1,2,3,5,7)]
```

## ATP 18

Activate: 16,15.
S: Stefanos Tsitsipas * Kei Nishikori, Novak Djokovic
W: * Philipp Kohlschreiber, Marin Cilic

Deactivate: 9,19,18.
S: [Alexander Zverev], [Dominic Thiem], [Rafael Nadal] * 
W: Karen Khachanov, David Goffin, Pablo Carreno Busta * 

```{r}
ex <- atp.test.2018[,c(3,5,6)]
ex$all.deact <- conduct.experiment(1:19,atp.P.567,atp.test.2018,test.year=0)$result
ex$all.act <- conduct.experiment(c(),atp.P.567,atp.test.2018,test.year=0)$result
ex$act <- conduct.experiment((1:19)[-c(15,16)],atp.P.567,atp.test.2018,test.year=0)$result
ex$deact <- conduct.experiment(c(9,18,19),atp.P.567,atp.test.2018,test.year=0)$result
ex$plat <- ex$act & ex$deact
```
```{r}
# tmp <- ex[which(ex$all.deact!=ex$act),c(1,2,3,4,6)]
# tmp <- ex[which(ex$all.act!=ex$deact),c(1,2,3,5,7)]
```

## WTA 18

Activate: (19,18).
S: [Sloane Stephens], Elina Svitolina, Angelique Kerber * Petra Kvitova
W: Anett Kontaveit, Caroline Wozniacki, Naomi Osaka * Karolina Pliskova

Deactivate: 1,8,9.
S: Katerina Siniakova, Sloane Stephens * Simona Halep
W: * Caroline Garcia, Angelique Kerber

```{r}
ex <- wta.test.2018[,c(3,5,6)]
ex$all.deact <- conduct.experiment(1:19,wta.P.567,wta.test.2018,test.year=0)$result
ex$all.act <- conduct.experiment(c(),wta.P.567,wta.test.2018,test.year=0)$result
ex$act <- conduct.experiment((1:19)[-c(18,19)],wta.P.567,wta.test.2018,test.year=0)$result
ex$deact <- conduct.experiment(c(1,8,9),wta.P.567,wta.test.2018,test.year=0)$result
ex$plat <- ex$act & ex$deact
```
```{r}
# tmp <- ex[which(ex$all.deact!=ex$act),c(1,2,3,4,6)]
# tmp <- ex[which(ex$all.act!=ex$deact),c(1,2,3,5,7)]
```

## ATP 22

Activate: 18,13,14.
S: Andrey Rublev, [Casper Ruud] * 
W: Stefanos Tsitsipas *

Deactivate: 16,19,4.
S: [Casper Ruud] * 
W: [Alexander Zverev], [Felix Auger Aliassime] * Hubert Hurkacz

```{r}
ex <- atp.test.2022[,c(3,5,6)]
ex$all.deact <- conduct.experiment(1:19,atp.P.901,atp.test.2022,test.year=0)$result
ex$all.act <- conduct.experiment(c(),atp.P.901,atp.test.2022,test.year=0)$result
ex$act <- conduct.experiment((1:19)[-c(13,14,18)],atp.P.901,atp.test.2022,test.year=0)$result
ex$deact <- conduct.experiment(c(4,16,19),atp.P.901,atp.test.2022,test.year=0)$result
ex$plat <- ex$act & ex$deact
```
```{r}
# tmp <- ex[which(ex$all.deact!=ex$act),c(1,2,3,4,6)]
# tmp <- ex[which(ex$all.act!=ex$deact),c(1,2,3,5,7)]
```

## WTA 22

Activate: 18,3,14.
S: [Aryna Sabalenka], [Iga Swiatek] * 
W: [Cori Gauff] * 

Deactivate: 1,5.
S: [Maria Sakkari]
W: Cori Gauff

**deprecated**
Deactivate: 13,14.
S: Caroline Garcia * 
W: Aryna Sabalenka, Iga Swiatek * 

```{r}
ex <- wta.test.2022[,c(2,4,5)]
ex$all.deact <- conduct.experiment(1:19,wta.P.901,wta.test.2022,test.year=0)$result
ex$all.act <- conduct.experiment(c(),wta.P.901,wta.test.2022,test.year=0)$result
ex$act <- conduct.experiment((1:19)[-c(3,14,18)],wta.P.901,wta.test.2022,test.year=0)$result
ex$deact <- conduct.experiment(c(1,5),wta.P.901,wta.test.2022,test.year=0)$result
ex$plat <- ex$act & ex$deact
```
```{r}
tmp <- ex[which(ex$all.deact!=ex$act),c(1,2,3,4,6)]
# tmp <- ex[which(ex$all.act!=ex$deact),c(1,2,3,5,7)]
```
