---
title: "Notebook 1n"
subtitle: "To organize into Latex"
always_allow_html: true
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

!!! This markdown is not for knitting/reading purposes !!!
Instead here the training/testing file sources are switched for their 2011-2014 counterparts. The purpose is purely to extract experiment results, so variable names will not be changed. For example atp.test.2014 will actually be 2014 data.

```{r}
source("case_patching.R")
grand.slams <- c("Australian Open","Roland Garros","Wimbledon","US Open")
get.prob.2014 <- function(p1,p2,match,atp=TRUE){
  if (is.na(p1)||is.na(p2)){
    return(NA)
  }
  if (match %in% grand.slams){
    if (match=="US Open"){
      ret <- match.win.prob.nonpw(p1,p2,format=0+atp)
    } else {
      ret <- match.win.prob.nonpw(p1,p2,format=4+atp)
    }
  } else {
    ret <- match.win.prob.nonpw(p1,p2,format=0)
  }
  return(ret)
}
```

## Experiments

```{r}
# testing data
atp.test.2014 <- read.csv('../Data Lake/Experiments/2014_atp_testing.csv')
wta.test.2014 <- read.csv('../Data Lake/Experiments/2014_wta_testing.csv')
```
```{r}
# following function highlights matches that were incomplete
# this is determined by if the score has letters ("W/O","Def.","RET" etc.)
# takes as input the score column of a dataset and returns indexes
ic.match <- function(score) grep("[A-Za-z]",score)
ic.atp <- ic.match(atp.test.2014$score)
ic.wta <- ic.match(wta.test.2014$score)
```
```{r}
# training data
atp.train.2013 <- read.csv('../Data Lake/Players/2013_atp_individual.csv')
atp.train.3yrs <- read.csv('../Data Lake/Players/2011-2013_atp_individual.csv')
wta.train.2013 <- read.csv('../Data Lake/Players/2013_wta_individual.csv')
wta.train.3yrs <- read.csv('../Data Lake/Players/2011-2013_wta_individual.csv')
atp.h2h.2013 <- read.csv('../Data Lake/Players/2013_atp_h2h.csv')
atp.h2h.3yrs <- read.csv('../Data Lake/Players/2011-2013_atp_h2h.csv')
atp.co.2013 <- read.csv('../Data Lake/Players/2013_atp_co.csv')
atp.co.3yrs <- read.csv('../Data Lake/Players/2011-2013_atp_co.csv')
wta.h2h.2013 <- read.csv('../Data Lake/Players/2013_wta_h2h.csv')
wta.h2h.3yrs <- read.csv('../Data Lake/Players/2011-2013_wta_h2h.csv')
wta.co.2013 <- read.csv('../Data Lake/Players/2013_wta_co.csv')
wta.co.3yrs <- read.csv('../Data Lake/Players/2011-2013_wta_co.csv')
# for the match specific datasets, they also need ic entries removed
atp.h2h.2013 <- atp.h2h.2013[-ic.atp,]
atp.h2h.3yrs <- atp.h2h.3yrs[-ic.atp,]
atp.co.2013 <- atp.co.2013[-ic.atp,]
atp.co.3yrs <- atp.co.3yrs[-ic.atp,]
wta.h2h.2013 <- wta.h2h.2013[-ic.wta,]
wta.h2h.3yrs <- wta.h2h.3yrs[-ic.wta,]
wta.co.2013 <- wta.co.2013[-ic.wta,]
wta.co.3yrs <- wta.co.3yrs[-ic.wta,]
```
```{r}
# remove incomplete matches for test sets
atp.test.2014 <- atp.test.2014[-ic.atp,]
wta.test.2014 <- wta.test.2014[-ic.wta,]
```


### Baseline ATP (estimating the p1,p2s with observed means)

#### 1 - 2013 Data - No Surface Distinction - General Data

```{r}
# augmentations to training set
# reload set after experiment
atp.train.2013$total_pts_served <- atp.train.2013$grass_pts_served +
  atp.train.2013$clay_pts_served + atp.train.2013$hard_pts_served
atp.train.2013$total_service_pts_won <- atp.train.2013$grass_service_pts_won +
  atp.train.2013$clay_service_pts_won + atp.train.2013$hard_service_pts_won
atp.train.2013$p.estimate <- atp.train.2013$total_service_pts_won / 
  atp.train.2013$total_pts_served
# 2 players found not to have data prior to 2014, resulting in estimates of NaN
# For these the average of the remaining players was plugged in
atp.train.2013$p.estimate[which(is.na(atp.train.2013$p.estimate))] <- 
  mean(atp.train.2013$p.estimate[-which(is.na(atp.train.2013$p.estimate))])
```
```{r}
n <- nrow(atp.test.2014)
res1 <- rep(0,n)
for (i in 1:n){
  winner <- atp.test.2014$winner_name[i]
  loser <- atp.test.2014$loser_name[i]
  winner.idx <- which(atp.train.2013$name==winner)
  loser.idx <- which(atp.train.2013$name==loser)
  if (atp.train.2013$p.estimate[winner.idx]>atp.train.2013$p.estimate[loser.idx]) res1[i]<-1
}
mean(res1)
```
So in terms of accuracy, the absolute baseline is 60%. Better than random guessing, but not by much. This is also in line with the results of the paper *Searching for the GOAT of tennis win prediction*, which had the various methods' accuracy in the low 60%s overall.

#### 2 - 2013 Data - Surface Distinction - General Data

```{r}
# augmentations to training set
# reload set after experiment
atp.train.2013$grass_p <- atp.train.2013$grass_service_pts_won/
  atp.train.2013$grass_pts_served
atp.train.2013$hard_p <- atp.train.2013$hard_service_pts_won/
  atp.train.2013$hard_pts_served
atp.train.2013$clay_p <- atp.train.2013$clay_service_pts_won/
  atp.train.2013$clay_pts_served
# like before, filling in NaNs (slightly more now, since some players did not play that
# surface in 2013) with corresponding averages
atp.train.2013$grass_p[which(is.na(atp.train.2013$grass_p))] <- 
  mean(atp.train.2013$grass_p[-which(is.na(atp.train.2013$grass_p))])
atp.train.2013$hard_p[which(is.na(atp.train.2013$hard_p))] <- 
  mean(atp.train.2013$hard_p[-which(is.na(atp.train.2013$hard_p))])
atp.train.2013$clay_p[which(is.na(atp.train.2013$clay_p))] <- 
  mean(atp.train.2013$clay_p[-which(is.na(atp.train.2013$clay_p))])
```
```{r}
n <- nrow(atp.test.2014)
res2 <- rep(0,n)
for (i in 1:n){
  winner <- atp.test.2014$winner_name[i]
  loser <- atp.test.2014$loser_name[i]
  winner.idx <- which(atp.train.2013$name==winner)
  loser.idx <- which(atp.train.2013$name==loser)
  if (atp.test.2014$surface[i]=="Grass") {
    res2[i] <- atp.train.2013$grass_p[winner.idx]>atp.train.2013$grass_p[loser.idx]
  } else if (atp.test.2014$surface[i]=="Hard") {
    res2[i] <- atp.train.2013$hard_p[winner.idx]>atp.train.2013$hard_p[loser.idx]
  } else if (atp.test.2014$surface[i]=="Clay") {
    res2[i] <- atp.train.2013$clay_p[winner.idx]>atp.train.2013$clay_p[loser.idx]
  } else {
    print("something wrong")
  }
}
mean(res2)
```
An increase in accuracy of 2% is incredibly encouraging given the simple approach being deployed. It aligns with previous studies' assertions of surface being of particular importance in predictions.

#### 3 - 2011-2013 Data - No Surface Distinction - General Data

```{r}
# augmentations to training set
# reload set after experiment
atp.train.3yrs$total_pts_served <- atp.train.3yrs$grass_pts_served +
  atp.train.3yrs$clay_pts_served + atp.train.3yrs$hard_pts_served
atp.train.3yrs$total_service_pts_won <- atp.train.3yrs$grass_service_pts_won +
  atp.train.3yrs$clay_service_pts_won + atp.train.3yrs$hard_service_pts_won
atp.train.3yrs$p.estimate <- atp.train.3yrs$total_service_pts_won / 
  atp.train.3yrs$total_pts_served
# 2 players found not to have data prior to 2014, resulting in estimates of NaN
# For these the average of the remaining players was plugged in
atp.train.3yrs$p.estimate[which(is.na(atp.train.3yrs$p.estimate))] <-
  mean(atp.train.3yrs$p.estimate[-which(is.na(atp.train.3yrs$p.estimate))])
```
```{r}
n <- nrow(atp.test.2014)
res3 <- rep(0,n)
for (i in 1:n){
  winner <- atp.test.2014$winner_name[i]
  loser <- atp.test.2014$loser_name[i]
  winner.idx <- which(atp.train.3yrs$name==winner)
  loser.idx <- which(atp.train.3yrs$name==loser)
  if (atp.train.3yrs$p.estimate[winner.idx]>atp.train.3yrs$p.estimate[loser.idx]) res3[i]<-1
}
mean(res3)
```
Here we see a decrease from the already not-very-good 60% in the very first experiment. This is evidence for the existence of the aforementioned tradeoff between data quantity and recency, and furthermore makes a strong case for recency over quantity. This will be kept in mind for future experiments, but this tradeoff will also have to be re-evaluated when H2H data is used and the need for quantity may increase.

#### 4 - 2011-2013 Data - Surface Distinction - General Data

```{r}
# augmentations to training set
# reload set after experiment
atp.train.3yrs$grass_p <- atp.train.3yrs$grass_service_pts_won/
  atp.train.3yrs$grass_pts_served
atp.train.3yrs$hard_p <- atp.train.3yrs$hard_service_pts_won/
  atp.train.3yrs$hard_pts_served
atp.train.3yrs$clay_p <- atp.train.3yrs$clay_service_pts_won/
  atp.train.3yrs$clay_pts_served
# like before, filling in NaNs (slightly more now, since some players did not play that
# surface in 2013) with corresponding averages
atp.train.3yrs$grass_p[which(is.na(atp.train.3yrs$grass_p))] <- 
  mean(atp.train.3yrs$grass_p[-which(is.na(atp.train.3yrs$grass_p))])
atp.train.3yrs$hard_p[which(is.na(atp.train.3yrs$hard_p))] <- 
  mean(atp.train.3yrs$hard_p[-which(is.na(atp.train.3yrs$hard_p))])
atp.train.3yrs$clay_p[which(is.na(atp.train.3yrs$clay_p))] <- 
  mean(atp.train.3yrs$clay_p[-which(is.na(atp.train.3yrs$clay_p))])
```
```{r}
n <- nrow(atp.test.2014)
res4 <- rep(0,n)
for (i in 1:n){
  winner <- atp.test.2014$winner_name[i]
  loser <- atp.test.2014$loser_name[i]
  winner.idx <- which(atp.train.3yrs$name==winner)
  loser.idx <- which(atp.train.3yrs$name==loser)
  if (atp.test.2014$surface[i]=="Grass") {
    res4[i] <- atp.train.3yrs$grass_p[winner.idx]>atp.train.3yrs$grass_p[loser.idx]
  } else if (atp.test.2014$surface[i]=="Hard") {
    res4[i] <- atp.train.3yrs$hard_p[winner.idx]>atp.train.3yrs$hard_p[loser.idx]
  } else if (atp.test.2014$surface[i]=="Clay") {
    res4[i] <- atp.train.3yrs$clay_p[winner.idx]>atp.train.3yrs$clay_p[loser.idx]
  } else {
    print("something wrong")
  }
}
mean(res4)
```
Thankfully both observations from before hold in this result. Making the surface distinction significantly increases prediction accuracy (again by 2%), and sacrificing data recency for data quantity again results in a decrease in accuracy of around 2%.

### Baseline WTA (estimating the p1,p2s with observed means)

#### 5 - 2013 Data - No Surface Distinction - General Data

```{r}
# reload dataset after using this block
wta.train.2013$total_pts_served <- wta.train.2013$grass_pts_served +
  wta.train.2013$clay_pts_served + wta.train.2013$hard_pts_served
wta.train.2013$total_service_pts_won <- wta.train.2013$grass_service_pts_won +
  wta.train.2013$clay_service_pts_won + wta.train.2013$hard_service_pts_won
wta.train.2013$p.estimate <- wta.train.2013$total_service_pts_won / 
  wta.train.2013$total_pts_served
wta.train.2013$p.estimate[which(is.na(wta.train.2013$p.estimate))] <- 
  mean(wta.train.2013$p.estimate[-which(is.na(wta.train.2013$p.estimate))])
n <- nrow(wta.test.2014)
res5 <- rep(0,n)
for (i in 1:n){
  winner <- wta.test.2014$winner_name[i]
  loser <- wta.test.2014$loser_name[i]
  winner.idx <- which(wta.train.2013$name==winner)
  loser.idx <- which(wta.train.2013$name==loser)
  if (wta.train.2013$p.estimate[winner.idx]>wta.train.2013$p.estimate[loser.idx]) res5[i]<-1
}
mean(res5)
```

#### 6 - 2013 Data - Surface Distinction - General Data

```{r}
# reload dataset after using this block
wta.train.2013$grass_p <- wta.train.2013$grass_service_pts_won/
  wta.train.2013$grass_pts_served
wta.train.2013$hard_p <- wta.train.2013$hard_service_pts_won/
  wta.train.2013$hard_pts_served
wta.train.2013$clay_p <- wta.train.2013$clay_service_pts_won/
  wta.train.2013$clay_pts_served
wta.train.2013$grass_p[which(is.na(wta.train.2013$grass_p))] <- 
  mean(wta.train.2013$grass_p[-which(is.na(wta.train.2013$grass_p))])
wta.train.2013$hard_p[which(is.na(wta.train.2013$hard_p))] <- 
  mean(wta.train.2013$hard_p[-which(is.na(wta.train.2013$hard_p))])
wta.train.2013$clay_p[which(is.na(wta.train.2013$clay_p))] <- 
  mean(wta.train.2013$clay_p[-which(is.na(wta.train.2013$clay_p))])
n <- nrow(wta.test.2014)
res6 <- rep(0,n)
for (i in 1:n){
  winner <- wta.test.2014$winner_name[i]
  loser <- wta.test.2014$loser_name[i]
  winner.idx <- which(wta.train.2013$name==winner)
  loser.idx <- which(wta.train.2013$name==loser)
  if (wta.test.2014$surface[i]=="Grass") {
    res6[i] <- wta.train.2013$grass_p[winner.idx]>wta.train.2013$grass_p[loser.idx]
  } else if (wta.test.2014$surface[i]=="Hard") {
    res6[i] <- wta.train.2013$hard_p[winner.idx]>wta.train.2013$hard_p[loser.idx]
  } else if (wta.test.2014$surface[i]=="Clay") {
    res6[i] <- wta.train.2013$clay_p[winner.idx]>wta.train.2013$clay_p[loser.idx]
  } else {
    print("something wrong")
  }
}
mean(res6)
```

#### 7 - 2011-2013 Data - No Surface Distinction - General Data

```{r}
# reload dataset after using this block
wta.train.3yrs$total_pts_served <- wta.train.3yrs$grass_pts_served +
  wta.train.3yrs$clay_pts_served + wta.train.3yrs$hard_pts_served
wta.train.3yrs$total_service_pts_won <- wta.train.3yrs$grass_service_pts_won +
  wta.train.3yrs$clay_service_pts_won + wta.train.3yrs$hard_service_pts_won
wta.train.3yrs$p.estimate <- wta.train.3yrs$total_service_pts_won / 
  wta.train.3yrs$total_pts_served
wta.train.3yrs$p.estimate[which(is.na(wta.train.3yrs$p.estimate))] <-
  mean(wta.train.3yrs$p.estimate[-which(is.na(wta.train.3yrs$p.estimate))])
n <- nrow(wta.test.2014)
res7 <- rep(0,n)
for (i in 1:n){
  winner <- wta.test.2014$winner_name[i]
  loser <- wta.test.2014$loser_name[i]
  winner.idx <- which(wta.train.3yrs$name==winner)
  loser.idx <- which(wta.train.3yrs$name==loser)
  if (wta.train.3yrs$p.estimate[winner.idx]>wta.train.3yrs$p.estimate[loser.idx]) res7[i]<-1
}
mean(res7)
```

#### 8 - 2011-2013 Data - Surface Distinction - General Data

```{r}
# reload dataset after using this block
wta.train.3yrs$grass_p <- wta.train.3yrs$grass_service_pts_won/
  wta.train.3yrs$grass_pts_served
wta.train.3yrs$hard_p <- wta.train.3yrs$hard_service_pts_won/
  wta.train.3yrs$hard_pts_served
wta.train.3yrs$clay_p <- wta.train.3yrs$clay_service_pts_won/
  wta.train.3yrs$clay_pts_served
wta.train.3yrs$grass_p[which(is.na(wta.train.3yrs$grass_p))] <- 
  mean(wta.train.3yrs$grass_p[-which(is.na(wta.train.3yrs$grass_p))])
wta.train.3yrs$hard_p[which(is.na(wta.train.3yrs$hard_p))] <- 
  mean(wta.train.3yrs$hard_p[-which(is.na(wta.train.3yrs$hard_p))])
wta.train.3yrs$clay_p[which(is.na(wta.train.3yrs$clay_p))] <- 
  mean(wta.train.3yrs$clay_p[-which(is.na(wta.train.3yrs$clay_p))])
n <- nrow(wta.test.2014)
res8 <- rep(0,n)
for (i in 1:n){
  winner <- wta.test.2014$winner_name[i]
  loser <- wta.test.2014$loser_name[i]
  winner.idx <- which(wta.train.3yrs$name==winner)
  loser.idx <- which(wta.train.3yrs$name==loser)
  if (wta.test.2014$surface[i]=="Grass") {
    res8[i] <- wta.train.3yrs$grass_p[winner.idx]>wta.train.3yrs$grass_p[loser.idx]
  } else if (wta.test.2014$surface[i]=="Hard") {
    res8[i] <- wta.train.3yrs$hard_p[winner.idx]>wta.train.3yrs$hard_p[loser.idx]
  } else if (wta.test.2014$surface[i]=="Clay") {
    res8[i] <- wta.train.3yrs$clay_p[winner.idx]>wta.train.3yrs$clay_p[loser.idx]
  } else {
    print("something wrong")
  }
}
mean(res8)
```

The first 3 WTA baseline experiments all reflect the same trends with slightly higher prediction accuracy, though still in the same overall range. Accuracy increases when training data is separated by surface, and decreases when recent training data is diluted by older data. But the drop in accuracy in the 4th WTA experiment, where older data was already added to the training data and the key change was to make distinctions between surface, is the first evidence against separating training data by surface. It is possible this speaks more strongly to the chaos older data can additionally have on results, and for the time being will be chalked up to be so. Still, we will have to keep an eye out for similar results in the future and come back to examine more closely if necessary.

### Opponent-Adjusted ATP

The main method for adjusting for opponent returning ability found in the literature is deducting from $p$ the difference between the opponent's returning ability (hereafter denoting $q$) and the average returning ability. We will see if this results in increase in accuracy, as well as compare with another way of adjusting for opponent ability - directly restricting the training set to head-to-head (H2H) data. Previous studies (Monte Carlo simulation) have noted this approach's lack of data, but we will attempt to remedy this by augmenting with common-opponent data (CO) (cite). Remaining 'holes' in the data fabric, which we do not expect to be numerous, will finally be patched with common data.

#### 9 - 2013 Data - No Surface Distinction - Opponent-Adjusted Formula

$\hat{p_1}=p_1-(q_2-\bar{q})$

```{r}
# same augmentation as [1]
# augmentations to training set
# reload set after experiment
atp.train.2013$total_pts_served <- atp.train.2013$grass_pts_served +
  atp.train.2013$clay_pts_served + atp.train.2013$hard_pts_served
atp.train.2013$total_service_pts_won <- atp.train.2013$grass_service_pts_won +
  atp.train.2013$clay_service_pts_won + atp.train.2013$hard_service_pts_won
atp.train.2013$p.estimate <- atp.train.2013$total_service_pts_won / 
  atp.train.2013$total_pts_served
# 2 players found not to have data prior to 2014, resulting in estimates of NaN
# For these the average of the remaining players was plugged in
atp.train.2013$p.estimate[which(is.na(atp.train.2013$p.estimate))] <- 
  mean(atp.train.2013$p.estimate[-which(is.na(atp.train.2013$p.estimate))])

# get q estimates as well
atp.train.2013$total_pts_received <- atp.train.2013$grass_pts_received +
  atp.train.2013$hard_pts_received + atp.train.2013$clay_pts_received
atp.train.2013$total_receiving_pts_won <- atp.train.2013$grass_receiving_pts_won +
  atp.train.2013$hard_receiving_pts_won + atp.train.2013$clay_receiving_pts_won
atp.train.2013$q.estimate <- atp.train.2013$total_receiving_pts_won /
  atp.train.2013$total_pts_received
atp.train.2013$q.estimate[which(is.na(atp.train.2013$q.estimate))] <- 
  mean(atp.train.2013$q.estimate[-which(is.na(atp.train.2013$q.estimate))])

q.bar <- mean(atp.train.2013$q.estimate)
n <- nrow(atp.test.2014)
res9 <- rep(0,n)
exact.res9 <- rep(0,n) # added much later in
for (i in 1:n){
  winner <- atp.test.2014$winner_name[i]
  loser <- atp.test.2014$loser_name[i]
  winner.idx <- which(atp.train.2013$name==winner)
  loser.idx <- which(atp.train.2013$name==loser)
  winner.adj.p <- atp.train.2013$p.estimate[winner.idx] - 
    (atp.train.2013$q.estimate[loser.idx] - q.bar)
  loser.adj.p <- atp.train.2013$p.estimate[loser.idx] - 
    (atp.train.2013$q.estimate[winner.idx] - q.bar)
  res9[i] <- winner.adj.p > loser.adj.p
  exact.res9[i] <- get.prob.2014(winner.adj.p,loser.adj.p,
                                 atp.test.2014$tourney_name[i],atp=TRUE)
}
mean(res9)
saveRDS(exact.res9,"p_est_exact_probs/atp2014_1y_ns_oaf_exact.rds")
```
A very strong jump in accuracy.

#### 10 - 2013 Data - Surface Distinction - Opponent-Adjusted Formula

```{r}
# same augmentation as [2]
# augmentations to training set
# reload set after experiment
# p's
atp.train.2013$grass_p <- atp.train.2013$grass_service_pts_won/
  atp.train.2013$grass_pts_served
atp.train.2013$hard_p <- atp.train.2013$hard_service_pts_won/
  atp.train.2013$hard_pts_served
atp.train.2013$clay_p <- atp.train.2013$clay_service_pts_won/
  atp.train.2013$clay_pts_served
atp.train.2013$grass_p[which(is.na(atp.train.2013$grass_p))] <- 
  mean(atp.train.2013$grass_p[-which(is.na(atp.train.2013$grass_p))])
atp.train.2013$hard_p[which(is.na(atp.train.2013$hard_p))] <- 
  mean(atp.train.2013$hard_p[-which(is.na(atp.train.2013$hard_p))])
atp.train.2013$clay_p[which(is.na(atp.train.2013$clay_p))] <- 
  mean(atp.train.2013$clay_p[-which(is.na(atp.train.2013$clay_p))])
# q's
atp.train.2013$grass_q <- atp.train.2013$grass_receiving_pts_won /
  atp.train.2013$grass_pts_received
atp.train.2013$hard_q <- atp.train.2013$hard_receiving_pts_won /
  atp.train.2013$hard_pts_received
atp.train.2013$clay_q <- atp.train.2013$clay_receiving_pts_won /
  atp.train.2013$clay_pts_received
atp.train.2013$grass_q[which(is.na(atp.train.2013$grass_q))] <- 
  mean(atp.train.2013$grass_q[-which(is.na(atp.train.2013$grass_q))])
atp.train.2013$hard_q[which(is.na(atp.train.2013$hard_q))] <- 
  mean(atp.train.2013$hard_q[-which(is.na(atp.train.2013$hard_q))])
atp.train.2013$clay_q[which(is.na(atp.train.2013$clay_q))] <- 
  mean(atp.train.2013$clay_q[-which(is.na(atp.train.2013$clay_q))])
q.bar.grass <- mean(atp.train.2013$grass_q)
q.bar.hard <- mean(atp.train.2013$hard_q)
q.bar.clay <- mean(atp.train.2013$clay_q)

n <- nrow(atp.test.2014)
res10 <- rep(0,n)
exact.res10 <- rep(0,n) # added much later in
for (i in 1:n){
  winner <- atp.test.2014$winner_name[i]
  loser <- atp.test.2014$loser_name[i]
  winner.idx <- which(atp.train.2013$name==winner)
  loser.idx <- which(atp.train.2013$name==loser)
  surf <- atp.test.2014$surface[i]
  if (surf=="Grass") {
    winner.adj.p <- atp.train.2013$grass_p[winner.idx] - 
      (atp.train.2013$grass_q[loser.idx] - q.bar.grass)
    loser.adj.p <- atp.train.2013$grass_p[loser.idx] - 
      (atp.train.2013$grass_q[winner.idx] - q.bar.grass)
    res10[i] <- winner.adj.p > loser.adj.p
  } else if (surf=="Hard"){
    winner.adj.p <- atp.train.2013$hard_p[winner.idx] - 
      (atp.train.2013$hard_q[loser.idx] - q.bar.hard)
    loser.adj.p <- atp.train.2013$hard_p[loser.idx] - 
      (atp.train.2013$hard_q[winner.idx] - q.bar.hard)
    res10[i] <- winner.adj.p > loser.adj.p
  } else if (surf=="Clay"){
    winner.adj.p <- atp.train.2013$clay_p[winner.idx] - 
      (atp.train.2013$clay_q[loser.idx] - q.bar.clay)
    loser.adj.p <- atp.train.2013$clay_p[loser.idx] - 
      (atp.train.2013$clay_q[winner.idx] - q.bar.clay)
    res10[i] <- winner.adj.p > loser.adj.p
  }
  exact.res10[i] <- get.prob.2014(winner.adj.p,loser.adj.p,
                                  atp.test.2014$tourney_name[i],atp=TRUE)
}
mean(res10)
saveRDS(exact.res10,"p_est_exact_probs/atp2014_1y_s_oaf_exact.rds")
```
Still positive compared to previous general data results, but disappointing as separating by surface decreased instead of increased the accuracy. Would be interesting to see if results are the same on the wta side. As well if future tests with 2015-2018 data corroborate results. (More thoughts on this in #12)

#### 11 - 2011-2013 Data - No Surface Distinction - Opponent-Adjusted Formula

```{r}
# same augmentation as [1]
# augmentations to training set
# reload set after experiment
atp.train.3yrs$total_pts_served <- atp.train.3yrs$grass_pts_served +
  atp.train.3yrs$clay_pts_served + atp.train.3yrs$hard_pts_served
atp.train.3yrs$total_service_pts_won <- atp.train.3yrs$grass_service_pts_won +
  atp.train.3yrs$clay_service_pts_won + atp.train.3yrs$hard_service_pts_won
atp.train.3yrs$p.estimate <- atp.train.3yrs$total_service_pts_won / 
  atp.train.3yrs$total_pts_served
# 2 players found not to have data prior to 2014, resulting in estimates of NaN
# For these the average of the remaining players was plugged in
atp.train.3yrs$p.estimate[which(is.na(atp.train.3yrs$p.estimate))] <- 
  mean(atp.train.3yrs$p.estimate[-which(is.na(atp.train.3yrs$p.estimate))])

# get q estimates as well
atp.train.3yrs$total_pts_received <- atp.train.3yrs$grass_pts_received +
  atp.train.3yrs$hard_pts_received + atp.train.3yrs$clay_pts_received
atp.train.3yrs$total_receiving_pts_won <- atp.train.3yrs$grass_receiving_pts_won +
  atp.train.3yrs$hard_receiving_pts_won + atp.train.3yrs$clay_receiving_pts_won
atp.train.3yrs$q.estimate <- atp.train.3yrs$total_receiving_pts_won /
  atp.train.3yrs$total_pts_received
atp.train.3yrs$q.estimate[which(is.na(atp.train.3yrs$q.estimate))] <- 
  mean(atp.train.3yrs$q.estimate[-which(is.na(atp.train.3yrs$q.estimate))])

q.bar <- mean(atp.train.3yrs$q.estimate)
n <- nrow(atp.test.2014)
res11 <- rep(0,n)
exact.res11 <- rep(0,n) # added much later in
for (i in 1:n){
  winner <- atp.test.2014$winner_name[i]
  loser <- atp.test.2014$loser_name[i]
  winner.idx <- which(atp.train.3yrs$name==winner)
  loser.idx <- which(atp.train.3yrs$name==loser)
  winner.adj.p <- atp.train.3yrs$p.estimate[winner.idx] - 
    (atp.train.3yrs$q.estimate[loser.idx] - q.bar)
  loser.adj.p <- atp.train.3yrs$p.estimate[loser.idx] - 
    (atp.train.3yrs$q.estimate[winner.idx] - q.bar)
  res11[i] <- winner.adj.p > loser.adj.p
  exact.res11[i] <- get.prob.2014(winner.adj.p,loser.adj.p,
                                  atp.test.2014$tourney_name[i],atp=TRUE)
}
mean(res11)
saveRDS(exact.res11,"p_est_exact_probs/atp2014_3y_ns_oaf_exact.rds")
```
Good to see that at least one of the trends identified as before still hold, that using more data at the expense of data recency decreases accuracy substantially (3 points here).

#### 12 - 2011-2013 Data - Surface Distinction - Opponent-Adjusted Formula

```{r}
# same augmentation as [2]
# augmentations to training set
# reload set after experiment
# p's
atp.train.3yrs$grass_p <- atp.train.3yrs$grass_service_pts_won/
  atp.train.3yrs$grass_pts_served
atp.train.3yrs$hard_p <- atp.train.3yrs$hard_service_pts_won/
  atp.train.3yrs$hard_pts_served
atp.train.3yrs$clay_p <- atp.train.3yrs$clay_service_pts_won/
  atp.train.3yrs$clay_pts_served
atp.train.3yrs$grass_p[which(is.na(atp.train.3yrs$grass_p))] <- 
  mean(atp.train.3yrs$grass_p[-which(is.na(atp.train.3yrs$grass_p))])
atp.train.3yrs$hard_p[which(is.na(atp.train.3yrs$hard_p))] <- 
  mean(atp.train.3yrs$hard_p[-which(is.na(atp.train.3yrs$hard_p))])
atp.train.3yrs$clay_p[which(is.na(atp.train.3yrs$clay_p))] <- 
  mean(atp.train.3yrs$clay_p[-which(is.na(atp.train.3yrs$clay_p))])
# q's
atp.train.3yrs$grass_q <- atp.train.3yrs$grass_receiving_pts_won /
  atp.train.3yrs$grass_pts_received
atp.train.3yrs$hard_q <- atp.train.3yrs$hard_receiving_pts_won /
  atp.train.3yrs$hard_pts_received
atp.train.3yrs$clay_q <- atp.train.3yrs$clay_receiving_pts_won /
  atp.train.3yrs$clay_pts_received
atp.train.3yrs$grass_q[which(is.na(atp.train.3yrs$grass_q))] <- 
  mean(atp.train.3yrs$grass_q[-which(is.na(atp.train.3yrs$grass_q))])
atp.train.3yrs$hard_q[which(is.na(atp.train.3yrs$hard_q))] <- 
  mean(atp.train.3yrs$hard_q[-which(is.na(atp.train.3yrs$hard_q))])
atp.train.3yrs$clay_q[which(is.na(atp.train.3yrs$clay_q))] <- 
  mean(atp.train.3yrs$clay_q[-which(is.na(atp.train.3yrs$clay_q))])
q.bar.grass <- mean(atp.train.3yrs$grass_q)
q.bar.hard <- mean(atp.train.3yrs$hard_q)
q.bar.clay <- mean(atp.train.3yrs$clay_q)

n <- nrow(atp.test.2014)
res12 <- rep(0,n)
exact.res12 <- rep(0,n) # added much later in
for (i in 1:n){
  winner <- atp.test.2014$winner_name[i]
  loser <- atp.test.2014$loser_name[i]
  winner.idx <- which(atp.train.3yrs$name==winner)
  loser.idx <- which(atp.train.3yrs$name==loser)
  surf <- atp.test.2014$surface[i]
  if (surf=="Grass") {
    winner.adj.p <- atp.train.3yrs$grass_p[winner.idx] - 
      (atp.train.3yrs$grass_q[loser.idx] - q.bar.grass)
    loser.adj.p <- atp.train.3yrs$grass_p[loser.idx] - 
      (atp.train.3yrs$grass_q[winner.idx] - q.bar.grass)
    res12[i] <- winner.adj.p > loser.adj.p
  } else if (surf=="Hard"){
    winner.adj.p <- atp.train.3yrs$hard_p[winner.idx] - 
      (atp.train.3yrs$hard_q[loser.idx] - q.bar.hard)
    loser.adj.p <- atp.train.3yrs$hard_p[loser.idx] - 
      (atp.train.3yrs$hard_q[winner.idx] - q.bar.hard)
    res12[i] <- winner.adj.p > loser.adj.p
  } else if (surf=="Clay"){
    winner.adj.p <- atp.train.3yrs$clay_p[winner.idx] - 
      (atp.train.3yrs$clay_q[loser.idx] - q.bar.clay)
    loser.adj.p <- atp.train.3yrs$clay_p[loser.idx] - 
      (atp.train.3yrs$clay_q[winner.idx] - q.bar.clay)
    res12[i] <- winner.adj.p > loser.adj.p
  }
  exact.res12[i] <- get.prob.2014(winner.adj.p,loser.adj.p,
                                  atp.test.2014$tourney_name[i],atp=TRUE)
}
mean(res12)
saveRDS(exact.res12,"p_est_exact_probs/atp2014_3y_s_oaf_exact.rds")
```
All in line with most recent observations, though perhaps not surprisingly as experiments 10 and 12 are not completely independent, if separating by surface in 10 decreases accuracy, then doing the same in 12, which has 1/3 of its data as 10's training data, very well may result in the same. However, this invalidates data volume as an excuse for the drop in 10.
Or does it completely? We have a reasonable amount of evidence pointing to the fact that data volume in the form of older data does not make up for data recency. Perhaps the problem is still a lack of recent data if we were to separate data by surface. It is notable that comparing #2 and #10, #10 still performs noticeably better.

#### 13 - 2013 Data - No Surface Distinction - H2H Data With CO Support

```{r}
# make a copy where co augmentation will go
data.13 <- atp.h2h.2013
# in h2h/co datasets, p1 is always the winner
data.13$w_total_pts_served <- data.13$grass_pts_served1 + 
  data.13$hard_pts_served1 + data.13$clay_pts_served1
data.13$w_total_service_pts_won <- data.13$grass_service_pts_won1 +
  data.13$hard_service_pts_won1 + data.13$clay_service_pts_won1
data.13$w_p <- data.13$w_total_service_pts_won/data.13$w_total_pts_served
data.13$l_total_pts_served <- data.13$grass_pts_served2 + 
  data.13$hard_pts_served2 + data.13$clay_pts_served2
data.13$l_total_service_pts_won <- data.13$grass_service_pts_won2 +
  data.13$hard_service_pts_won2 + data.13$clay_service_pts_won2
data.13$l_p <- data.13$l_total_service_pts_won/data.13$l_total_pts_served

# first see accuracy for entries where h2h data is available
h2h.valid <- which(!is.na(data.13$w_p)) #l_p also works
res13.h2h <- rep(0,length(h2h.valid))
exact13.h2h <- rep(0,length(h2h.valid))
for (i in 1:length(h2h.valid)){
  res13.h2h[i] <- data.13$w_p[h2h.valid[i]] > data.13$l_p[h2h.valid[i]]
  exact13.h2h[i] <- get.prob.2014(data.13$w_p[h2h.valid[i]],data.13$l_p[h2h.valid[i]],
                                  atp.test.2014$tourney_name[h2h.valid[i]],atp=TRUE)
}
mean(res13.h2h) # 0.8703704 very high, but also small testing set size

# next see accuracy for all entries where co data is available 
data.13$w_total_pts_served_co <- atp.co.2013$grass_pts_served1 + 
  atp.co.2013$hard_pts_served1 + atp.co.2013$clay_pts_served1
data.13$w_total_service_pts_won_co <- atp.co.2013$grass_service_pts_won1 +
  atp.co.2013$hard_service_pts_won1 + atp.co.2013$clay_service_pts_won1
data.13$w_p_co <- data.13$w_total_service_pts_won_co/data.13$w_total_pts_served_co
data.13$l_total_pts_served_co <- atp.co.2013$grass_pts_served2 + 
  atp.co.2013$hard_pts_served2 + atp.co.2013$clay_pts_served2
data.13$l_total_service_pts_won_co <- atp.co.2013$grass_service_pts_won2 +
  atp.co.2013$hard_service_pts_won2 + atp.co.2013$clay_service_pts_won2
data.13$l_p_co <- data.13$l_total_service_pts_won_co/data.13$l_total_pts_served_co
co.valid <- which(!is.na(data.13$w_p_co) & !is.na(data.13$l_p_co)) #l_p_co also works
res13.co <- rep(0,length(co.valid))
exact13.co <- rep(0,length(co.valid))
for (i in 1:length(co.valid)){
  res13.co[i] <- data.13$w_p_co[co.valid[i]] > data.13$l_p_co[co.valid[i]]
  exact13.co[i] <- get.prob.2014(data.13$w_p_co[co.valid[i]],data.13$l_p_co[co.valid[i]],
                                 atp.test.2014$tourney_name[co.valid[i]],atp=TRUE)
}
mean(res13.co) # 6258065 substantial decrease, a little better than absolute baseline

# finally h2h with co support
res13 <- res1 # first use general data and apply new results on top
res13[co.valid] <- res13.co
res13[h2h.valid] <- res13.h2h
mean(res13)
```
Summarizing results and comments above: Pure H2H data yields extremely high accuracy, though this can't be taken in its entirety as the number of entries with pure H2H data is by comparison very small. For pure CO data, accuracy is only a little better than baseline, raising the question of if augmenting with general data would be enough. This, though a little disappointing, aligns with the searching for GOAT prediction paper's results where common opponent data does not make any significant difference. The final result is essentially a weighted combination of the previous 2 results with a little (3 entries in this specific case) general results (#13 corresponds to to #1), and a final result of 70% is still pretty encouraging and early evidence for how valuable H2H data is.
```{r}
# Just to see if we left out CO data
res13.no_co <- res1
res13.no_co[h2h.valid] <- res13.h2h
mean(res13.no_co)
```
As expected since as noted above, this is just a weighted sum of the 3 pure data results, and we saw that in this case, common opponent data was a little bit helpful.

```{r}
# later added to save results
res13.h2h.sv <- rep(-1,nrow(atp.test.2014))
res13.h2h.sv[h2h.valid] <- res13.h2h
res13.co.sv <- rep(-1,nrow(atp.test.2014))
res13.co.sv[co.valid] <- res13.co
exact13.h2h.sv <- rep(-1,nrow(atp.test.2014))
exact13.h2h.sv[h2h.valid] <- exact13.h2h
exact13.co.sv <- rep(-1,nrow(atp.test.2014))
exact13.co.sv[co.valid] <- exact13.co
saveRDS(exact13.h2h.sv,"p_est_exact_probs/atp2014_1y_ns_h2h.rds")
saveRDS(exact13.co.sv,"p_est_exact_probs/atp2014_1y_ns_co.rds")
```


#### 14 - 2013 Data - Surface Distinction - H2H Data With CO Support

```{r}
data.14 <- atp.h2h.2013
# g for grass_p, h for hard_p, c for clay_p
data.14$w_g <- data.14$grass_service_pts_won1/data.14$grass_pts_served1
data.14$w_h <- data.14$hard_service_pts_won1/data.14$hard_pts_served1
data.14$w_c <- data.14$clay_service_pts_won1/data.14$clay_pts_served1
data.14$l_g <- data.14$grass_service_pts_won2/data.14$grass_pts_served2
data.14$l_h <- data.14$hard_service_pts_won2/data.14$hard_pts_served2
data.14$l_c <- data.14$clay_service_pts_won2/data.14$clay_pts_served2

h2h.valid <- rep(0,nrow(atp.test.2014))
# see performance for pure h2h data separated by surface
res14.h2h <- c() # initialize and add elements by res14.h2h <- c(res14.h2h,...)
exact14.h2h <- c()
for (i in 1:nrow(atp.test.2014)){
  if (atp.test.2014$surface[i]=="Grass" && !is.na(data.14$w_g[i])){
    res14.h2h <- c(res14.h2h, data.14$w_g[i] > data.14$l_g[i])
    exact14.h2h <- c(exact14.h2h,
                     get.prob.2014(data.14$w_g[i],data.14$l_g[i],
                                   atp.test.2014$tourney_name[i],atp=TRUE))
    h2h.valid[i] <- 1
  } else if (atp.test.2014$surface[i]=="Hard" && !is.na(data.14$w_h[i])){
    res14.h2h <- c(res14.h2h, data.14$w_h[i] > data.14$l_h[i])
    exact14.h2h <- c(exact14.h2h,
                     get.prob.2014(data.14$w_h[i],data.14$l_h[i],
                                   atp.test.2014$tourney_name[i],atp=TRUE))
    h2h.valid[i] <- 1
  } else if (atp.test.2014$surface[i]=="Clay" && !is.na(data.14$w_c[i])){
    res14.h2h <- c(res14.h2h, data.14$w_c[i] > data.14$l_c[i])
    exact14.h2h <- c(exact14.h2h,
                     get.prob.2014(data.14$w_c[i],data.14$l_c[i],
                                   atp.test.2014$tourney_name[i],atp=TRUE))
    h2h.valid[i] <- 1
  }
}
h2h.valid <- which(h2h.valid==1)
mean(res14.h2h) # 0.81481
```
81% is a very large decrease compared to the 87% achieved previously. These early results indicate that not only is h2h data more valuable than surface-separated data, but that sacrificing data volume for surface-specific quality may be detrimental when H2H is at hand.
Can this be remediated using lesser quality older data? (Will see in #16)
```{r}
# see performance for pure co data separated by surface
data.14$w_g_co <- atp.co.2013$grass_service_pts_won1/atp.co.2013$grass_pts_served1
data.14$w_h_co <- atp.co.2013$hard_service_pts_won1/atp.co.2013$hard_pts_served1
data.14$w_c_co <- atp.co.2013$clay_service_pts_won1/atp.co.2013$clay_pts_served1
data.14$l_g_co <- atp.co.2013$grass_service_pts_won2/atp.co.2013$grass_pts_served2
data.14$l_h_co <- atp.co.2013$hard_service_pts_won2/atp.co.2013$hard_pts_served2
data.14$l_c_co <- atp.co.2013$clay_service_pts_won2/atp.co.2013$clay_pts_served2
res14.co <- c() # same method as before
exact14.co <- c()
co.valid <- rep(0,nrow(atp.test.2014))
for (i in 1:nrow(atp.test.2014)){
  if (atp.test.2014$surface[i]=="Grass" & 
      !is.na(data.14$w_g_co[i]) & !is.na(data.14$l_g_co[i])){
    res14.co <- c(res14.co, data.14$w_g_co[i] > data.14$l_g_co[i])
    exact14.co <- c(exact14.co,
                    get.prob.2014(data.14$w_g_co[i],data.14$l_g_co[i],
                                  atp.test.2014$tourney_name[i],atp=TRUE))
    co.valid[i] <- 1
  } else if (atp.test.2014$surface[i]=="Hard" &
             !is.na(data.14$w_h_co[i]) & !is.na(data.14$l_h_co[i])){
    res14.co <- c(res14.co, data.14$w_h_co[i] > data.14$l_h_co[i])
    exact14.co <- c(exact14.co,
                    get.prob.2014(data.14$w_h_co[i],data.14$l_h_co[i],
                                  atp.test.2014$tourney_name[i],atp=TRUE))
    co.valid[i] <- 1
  } else if (atp.test.2014$surface[i]=="Clay" & 
             !is.na(data.14$w_c_co[i]) & !is.na(data.14$l_c_co[i])){
    res14.co <- c(res14.co, data.14$w_c_co[i] > data.14$l_c_co[i])
    exact14.co <- c(exact14.co,
                    get.prob.2014(data.14$w_c_co[i],data.14$l_c_co[i],
                                  atp.test.2014$tourney_name[i],atp=TRUE))
    co.valid[i] <- 1
  }
}
co.valid <- which(co.valid==1)
mean(res14.co)
# mean(res14.co) NA initially, discovered 6 entries where only 1 player in a match had stats
# so above edited to check for both w_*_co and l_*_co 
# reason for this was noted previously during collection or in notes
```
Here (when comparing with #2) we see an instance of common-opponent data directly outperforming general data.

```{r}
# Now combine h2h data with co/general data
# first overlap with co results
res14 <- res2
res14[co.valid] <- res14.co
res14[h2h.valid] <- res14.h2h
mean(res14)
```
In the same ballpark as final results in #13, but slightly worse, as is expected looking at the pure h2h and co results that are both slightly worse as well. Again to get a feel for the effect of the co data's effect, we will also only overlay h2h results onto general results from #2.
```{r}
res14.no_co <- res2
res14.no_co[h2h.valid] <- res14.h2h
mean(res14.no_co)
```
Here there is entirely no difference between the entries' results. But note that the actual match predictions are different. The # of correct predictions on the whole hasn't changed.
```{r}
which(res14!=res14.no_co)
```
```{r}
# later added to save results
res14.h2h.sv <- rep(-1,nrow(atp.test.2014))
res14.h2h.sv[h2h.valid] <- res14.h2h
res14.co.sv <- rep(-1,nrow(atp.test.2014))
res14.co.sv[co.valid] <- res14.co
exact14.h2h.sv <- rep(-1,nrow(atp.test.2014))
exact14.h2h.sv[h2h.valid] <- exact14.h2h
exact14.co.sv <- rep(-1,nrow(atp.test.2014))
exact14.co.sv[co.valid] <- exact14.co
saveRDS(exact14.h2h.sv,"p_est_exact_probs/atp2014_1y_s_h2h.rds")
saveRDS(exact14.co.sv,"p_est_exact_probs/atp2014_1y_s_co.rds")
```

#### 15 - 2011-2013 Data - No Surface Distinction - H2H Data With CO Support

```{r}
# make a copy where co augmentation will go
data.15 <- atp.h2h.3yrs
# in h2h/co datasets, p1 is always the winner
data.15$w_total_pts_served <- data.15$grass_pts_served1 + 
  data.15$hard_pts_served1 + data.15$clay_pts_served1
data.15$w_total_service_pts_won <- data.15$grass_service_pts_won1 +
  data.15$hard_service_pts_won1 + data.15$clay_service_pts_won1
data.15$w_p <- data.15$w_total_service_pts_won/data.15$w_total_pts_served
data.15$l_total_pts_served <- data.15$grass_pts_served2 + 
  data.15$hard_pts_served2 + data.15$clay_pts_served2
data.15$l_total_service_pts_won <- data.15$grass_service_pts_won2 +
  data.15$hard_service_pts_won2 + data.15$clay_service_pts_won2
data.15$l_p <- data.15$l_total_service_pts_won/data.15$l_total_pts_served

# first see accuracy for entries where h2h data is available
h2h.valid <- which(!is.na(data.15$w_p)) #l_p also works
res15.h2h <- rep(0,length(h2h.valid))
exact15.h2h <- rep(0,length(h2h.valid))
for (i in 1:length(h2h.valid)){
  res15.h2h[i] <- data.15$w_p[h2h.valid[i]] > data.15$l_p[h2h.valid[i]]
  exact15.h2h[i] <- get.prob.2014(data.15$w_p[h2h.valid[i]],data.15$l_p[h2h.valid[i]],
                                  atp.test.2014$tourney_name[h2h.valid[i]],atp=TRUE)
}
mean(res15.h2h)

# next see accuracy for all entries where co data is available 
data.15$w_total_pts_served_co <- atp.co.3yrs$grass_pts_served1 + 
  atp.co.3yrs$hard_pts_served1 + atp.co.3yrs$clay_pts_served1
data.15$w_total_service_pts_won_co <- atp.co.3yrs$grass_service_pts_won1 +
  atp.co.3yrs$hard_service_pts_won1 + atp.co.3yrs$clay_service_pts_won1
data.15$w_p_co <- data.15$w_total_service_pts_won_co/data.15$w_total_pts_served_co
data.15$l_total_pts_served_co <- atp.co.3yrs$grass_pts_served2 + 
  atp.co.3yrs$hard_pts_served2 + atp.co.3yrs$clay_pts_served2
data.15$l_total_service_pts_won_co <- atp.co.3yrs$grass_service_pts_won2 +
  atp.co.3yrs$hard_service_pts_won2 + atp.co.3yrs$clay_service_pts_won2
data.15$l_p_co <- data.15$l_total_service_pts_won_co/data.15$l_total_pts_served_co
co.valid <- which(!is.na(data.15$w_p_co)) #l_p_co also works
res15.co <- rep(0,length(co.valid))
exact15.co <- rep(0,length(co.valid))
for (i in 1:length(co.valid)){
  res15.co[i] <- data.15$w_p_co[co.valid[i]] > data.15$l_p_co[co.valid[i]]
  exact15.co[i] <- get.prob.2014(data.15$w_p_co[co.valid[i]],data.15$l_p_co[co.valid[i]],
                                 atp.test.2014$tourney_name[co.valid[i]],atp=TRUE)
}
mean(res15.co)

# finally h2h with co support
res15 <- res3 # first use general data and apply new results on top
res15[co.valid] <- res15.co
res15[h2h.valid] <- res15.h2h
mean(res15)
```
We see an increase for all 3 - pure h2h subset, pure co subset, proposed (h2h->co->general) approach. When it comes to matchup-specific data, it seems data recency becomes less of an issue. #16's results will probably be in-line with this conclusion since, as noted before in #12, the training sets overlap quite a lot. Again like in #13, we also look at accuracy when the CO layer is removed:
```{r}
res15.no_co <- res3
res15.no_co[h2h.valid] <- res15.h2h
mean(res15.no_co)
```
A slight decrease, exactly the same as before.

```{r}
# later added to save results
res15.h2h.sv <- rep(-1,nrow(atp.test.2014))
res15.h2h.sv[h2h.valid] <- res15.h2h
res15.co.sv <- rep(-1,nrow(atp.test.2014))
res15.co.sv[co.valid] <- res15.co
exact15.h2h.sv <- rep(-1,nrow(atp.test.2014))
exact15.h2h.sv[h2h.valid] <- exact15.h2h
exact15.co.sv <- rep(-1,nrow(atp.test.2014))
exact15.co.sv[co.valid] <- exact15.co
saveRDS(exact15.h2h.sv,"p_est_exact_probs/atp2014_3y_ns_h2h.rds")
saveRDS(exact15.co.sv,"p_est_exact_probs/atp2014_3y_ns_co.rds")
```

#### 16 - 2011-2013 Data - Surface Distinction - H2H Data With CO Support

```{r}
data.16 <- atp.h2h.3yrs
# g for grass_p, h for hard_p, c for clay_p
data.16$w_g <- data.16$grass_service_pts_won1/data.16$grass_pts_served1
data.16$w_h <- data.16$hard_service_pts_won1/data.16$hard_pts_served1
data.16$w_c <- data.16$clay_service_pts_won1/data.16$clay_pts_served1
data.16$l_g <- data.16$grass_service_pts_won2/data.16$grass_pts_served2
data.16$l_h <- data.16$hard_service_pts_won2/data.16$hard_pts_served2
data.16$l_c <- data.16$clay_service_pts_won2/data.16$clay_pts_served2

# see performance for pure h2h data separated by surface
h2h.valid <- rep(0,nrow(atp.test.2014))
res16.h2h <- c() # initialize and add elements by res14.h2h <- c(res14.h2h,...)
exact16.h2h <- c()
for (i in 1:nrow(atp.test.2014)){
  if (atp.test.2014$surface[i]=="Grass" && !is.na(data.16$w_g[i])){
    res16.h2h <- c(res16.h2h, data.16$w_g[i] > data.16$l_g[i])
    exact16.h2h <- c(exact16.h2h,
                     get.prob.2014(data.16$w_g[i],data.16$l_g[i],
                                   atp.test.2014$tourney_name[i],atp=TRUE))
    h2h.valid[i] <- 1
  } else if (atp.test.2014$surface[i]=="Hard" && !is.na(data.16$w_h[i])){
    res16.h2h <- c(res16.h2h, data.16$w_h[i] > data.16$l_h[i])
    exact16.h2h <- c(exact16.h2h,
                     get.prob.2014(data.16$w_h[i],data.16$l_h[i],
                                   atp.test.2014$tourney_name[i],atp=TRUE))
    h2h.valid[i] <- 1
  } else if (atp.test.2014$surface[i]=="Clay" && !is.na(data.16$w_c[i])){
    res16.h2h <- c(res16.h2h, data.16$w_c[i] > data.16$l_c[i])
    exact16.h2h <- c(exact16.h2h,
                     get.prob.2014(data.16$w_c[i],data.16$l_c[i],
                                   atp.test.2014$tourney_name[i],atp=TRUE))
    h2h.valid[i] <- 1
  }
}
h2h.valid <- which(h2h.valid==1)
mean(res16.h2h)

# see performance for pure co data separated by surface
data.16$w_g_co <- atp.co.3yrs$grass_service_pts_won1/atp.co.3yrs$grass_pts_served1
data.16$w_h_co <- atp.co.3yrs$hard_service_pts_won1/atp.co.3yrs$hard_pts_served1
data.16$w_c_co <- atp.co.3yrs$clay_service_pts_won1/atp.co.3yrs$clay_pts_served1
data.16$l_g_co <- atp.co.3yrs$grass_service_pts_won2/atp.co.3yrs$grass_pts_served2
data.16$l_h_co <- atp.co.3yrs$hard_service_pts_won2/atp.co.3yrs$hard_pts_served2
data.16$l_c_co <- atp.co.3yrs$clay_service_pts_won2/atp.co.3yrs$clay_pts_served2
co.valid <- rep(0,nrow(atp.test.2014))
res16.co <- c() # same method as before
exact16.co <- c()
for (i in 1:nrow(atp.test.2014)){
  if (atp.test.2014$surface[i]=="Grass" & 
      !is.na(data.16$w_g_co[i]) & !is.na(data.16$l_g_co[i])){
    res16.co <- c(res16.co, data.16$w_g_co[i] > data.16$l_g_co[i])
    exact16.co <- c(exact16.co,
                    get.prob.2014(data.16$w_g_co[i],data.16$l_g_co[i],
                                  atp.test.2014$tourney_name[i],atp=TRUE))
    co.valid[i] <- 1
  } else if (atp.test.2014$surface[i]=="Hard" &
             !is.na(data.16$w_h_co[i]) & !is.na(data.16$l_h_co[i])){
    res16.co <- c(res16.co, data.16$w_h_co[i] > data.16$l_h_co[i])
    exact16.co <- c(exact16.co,
                    get.prob.2014(data.16$w_h_co[i],data.16$l_h_co[i],
                                  atp.test.2014$tourney_name[i],atp=TRUE))
    co.valid[i] <- 1
  } else if (atp.test.2014$surface[i]=="Clay" & 
             !is.na(data.16$w_c_co[i]) & !is.na(data.16$l_c_co[i])){
    res16.co <- c(res16.co, data.16$w_c_co[i] > data.16$l_c_co[i])
    exact16.co <- c(exact16.co,
                    get.prob.2014(data.16$w_c_co[i],data.16$l_c_co[i],
                                  atp.test.2014$tourney_name[i],atp=TRUE))
    co.valid[i] <- 1
  }
}
co.valid <- which(co.valid==1)
mean(res16.co)

res16 <- res4
res16[co.valid] <- res16.co
res16[h2h.valid] <- res16.h2h
mean(res16)
```
Substantial increase for all 3 compared to #14. Though this was partly expected, as noted in #15. Will see if same trends present in wta equivalent.
```{r}
# again see difference if co layer removed
res16.no_co <- res4
res16.no_co[h2h.valid] <- res16.h2h
mean(res16.no_co)
```

```{r}
# later added to save results
res16.h2h.sv <- rep(-1,nrow(atp.test.2014))
res16.h2h.sv[h2h.valid] <- res16.h2h
res16.co.sv <- rep(-1,nrow(atp.test.2014))
res16.co.sv[co.valid] <- res16.co
exact16.h2h.sv <- rep(-1,nrow(atp.test.2014))
exact16.h2h.sv[h2h.valid] <- exact16.h2h
exact16.co.sv <- rep(-1,nrow(atp.test.2014))
exact16.co.sv[co.valid] <- exact16.co
saveRDS(exact16.h2h.sv,"p_est_exact_probs/atp2014_3y_s_h2h.rds")
saveRDS(exact16.co.sv,"p_est_exact_probs/atp2014_3y_s_co.rds")
```

### Opponent Adjusted WTA

Conclusions to be drawn all together after #24.

#### 17 - 2013 Data - No Surface Distinction - Opponent-Adjusted Formula

```{r}
# same augmentation as [5]
# augmentations to training set
# reload set after experiment
wta.train.2013$total_pts_served <- wta.train.2013$grass_pts_served +
  wta.train.2013$clay_pts_served + wta.train.2013$hard_pts_served
wta.train.2013$total_service_pts_won <- wta.train.2013$grass_service_pts_won +
  wta.train.2013$clay_service_pts_won + wta.train.2013$hard_service_pts_won
wta.train.2013$p.estimate <- wta.train.2013$total_service_pts_won / 
  wta.train.2013$total_pts_served
wta.train.2013$p.estimate[which(is.na(wta.train.2013$p.estimate))] <- 
  mean(wta.train.2013$p.estimate[-which(is.na(wta.train.2013$p.estimate))])

# get q estimates as well
wta.train.2013$total_pts_received <- wta.train.2013$grass_pts_received +
  wta.train.2013$hard_pts_received + wta.train.2013$clay_pts_received
wta.train.2013$total_receiving_pts_won <- wta.train.2013$grass_receiving_pts_won +
  wta.train.2013$hard_receiving_pts_won + wta.train.2013$clay_receiving_pts_won
wta.train.2013$q.estimate <- wta.train.2013$total_receiving_pts_won /
  wta.train.2013$total_pts_received
wta.train.2013$q.estimate[which(is.na(wta.train.2013$q.estimate))] <- 
  mean(wta.train.2013$q.estimate[-which(is.na(wta.train.2013$q.estimate))])

q.bar <- mean(wta.train.2013$q.estimate)
n <- nrow(wta.test.2014)
res17 <- rep(0,n)
exact.res17 <- rep(0,n) # added much later in
for (i in 1:n){
  winner <- wta.test.2014$winner_name[i]
  loser <- wta.test.2014$loser_name[i]
  winner.idx <- which(wta.train.2013$name==winner)
  loser.idx <- which(wta.train.2013$name==loser)
  winner.adj.p <- wta.train.2013$p.estimate[winner.idx] - 
    (wta.train.2013$q.estimate[loser.idx] - q.bar)
  loser.adj.p <- wta.train.2013$p.estimate[loser.idx] - 
    (wta.train.2013$q.estimate[winner.idx] - q.bar)
  res17[i] <- winner.adj.p > loser.adj.p
  exact.res17[i] <- get.prob.2014(winner.adj.p,loser.adj.p,
                                  wta.test.2014$tourney_name[i],atp=FALSE)
}
mean(res17)
saveRDS(exact.res17,"p_est_exact_probs/wta2014_1y_ns_oaf_exact.rds")
```

#### 18 - 2013 Data - Surface Distinction - Opponent-Adjusted Formula

```{r}
# p's
wta.train.2013$grass_p <- wta.train.2013$grass_service_pts_won/
  wta.train.2013$grass_pts_served
wta.train.2013$hard_p <- wta.train.2013$hard_service_pts_won/
  wta.train.2013$hard_pts_served
wta.train.2013$clay_p <- wta.train.2013$clay_service_pts_won/
  wta.train.2013$clay_pts_served
wta.train.2013$grass_p[which(is.na(wta.train.2013$grass_p))] <- 
  mean(wta.train.2013$grass_p[-which(is.na(wta.train.2013$grass_p))])
wta.train.2013$hard_p[which(is.na(wta.train.2013$hard_p))] <- 
  mean(wta.train.2013$hard_p[-which(is.na(wta.train.2013$hard_p))])
wta.train.2013$clay_p[which(is.na(wta.train.2013$clay_p))] <- 
  mean(wta.train.2013$clay_p[-which(is.na(wta.train.2013$clay_p))])
# q's
wta.train.2013$grass_q <- wta.train.2013$grass_receiving_pts_won /
  wta.train.2013$grass_pts_received
wta.train.2013$hard_q <- wta.train.2013$hard_receiving_pts_won /
  wta.train.2013$hard_pts_received
wta.train.2013$clay_q <- wta.train.2013$clay_receiving_pts_won /
  wta.train.2013$clay_pts_received
wta.train.2013$grass_q[which(is.na(wta.train.2013$grass_q))] <- 
  mean(wta.train.2013$grass_q[-which(is.na(wta.train.2013$grass_q))])
wta.train.2013$hard_q[which(is.na(wta.train.2013$hard_q))] <- 
  mean(wta.train.2013$hard_q[-which(is.na(wta.train.2013$hard_q))])
wta.train.2013$clay_q[which(is.na(wta.train.2013$clay_q))] <- 
  mean(wta.train.2013$clay_q[-which(is.na(wta.train.2013$clay_q))])
q.bar.grass <- mean(wta.train.2013$grass_q)
q.bar.hard <- mean(wta.train.2013$hard_q)
q.bar.clay <- mean(wta.train.2013$clay_q)

n <- nrow(wta.test.2014)
res18 <- rep(0,n)
exact.res18 <- rep(0,n) # added much later in
for (i in 1:n){
  winner <- wta.test.2014$winner_name[i]
  loser <- wta.test.2014$loser_name[i]
  winner.idx <- which(wta.train.2013$name==winner)
  loser.idx <- which(wta.train.2013$name==loser)
  surf <- wta.test.2014$surface[i]
  if (surf=="Grass") {
    winner.adj.p <- wta.train.2013$grass_p[winner.idx] - 
      (wta.train.2013$grass_q[loser.idx] - q.bar.grass)
    loser.adj.p <- wta.train.2013$grass_p[loser.idx] - 
      (wta.train.2013$grass_q[winner.idx] - q.bar.grass)
    res18[i] <- winner.adj.p > loser.adj.p
  } else if (surf=="Hard"){
    winner.adj.p <- wta.train.2013$hard_p[winner.idx] - 
      (wta.train.2013$hard_q[loser.idx] - q.bar.hard)
    loser.adj.p <- wta.train.2013$hard_p[loser.idx] - 
      (wta.train.2013$hard_q[winner.idx] - q.bar.hard)
    res18[i] <- winner.adj.p > loser.adj.p
  } else if (surf=="Clay"){
    winner.adj.p <- wta.train.2013$clay_p[winner.idx] - 
      (wta.train.2013$clay_q[loser.idx] - q.bar.clay)
    loser.adj.p <- wta.train.2013$clay_p[loser.idx] - 
      (wta.train.2013$clay_q[winner.idx] - q.bar.clay)
    res18[i] <- winner.adj.p > loser.adj.p
  }
  exact.res18[i] <- get.prob.2014(winner.adj.p,loser.adj.p,
                                  wta.test.2014$tourney_name[i],atp=FALSE)
}
mean(res18)
saveRDS(exact.res18,"p_est_exact_probs/wta2014_1y_s_oaf_exact.rds")
```

#### 19 - 2011-2013 Data - No Surface Distinction - Opponent-Adjusted Formula

```{r}
wta.train.3yrs$total_pts_served <- wta.train.3yrs$grass_pts_served +
  wta.train.3yrs$clay_pts_served + wta.train.3yrs$hard_pts_served
wta.train.3yrs$total_service_pts_won <- wta.train.3yrs$grass_service_pts_won +
  wta.train.3yrs$clay_service_pts_won + wta.train.3yrs$hard_service_pts_won
wta.train.3yrs$p.estimate <- wta.train.3yrs$total_service_pts_won / 
  wta.train.3yrs$total_pts_served
wta.train.3yrs$p.estimate[which(is.na(wta.train.3yrs$p.estimate))] <- 
  mean(wta.train.3yrs$p.estimate[-which(is.na(wta.train.3yrs$p.estimate))])

# get q estimates as well
wta.train.3yrs$total_pts_received <- wta.train.3yrs$grass_pts_received +
  wta.train.3yrs$hard_pts_received + wta.train.3yrs$clay_pts_received
wta.train.3yrs$total_receiving_pts_won <- wta.train.3yrs$grass_receiving_pts_won +
  wta.train.3yrs$hard_receiving_pts_won + wta.train.3yrs$clay_receiving_pts_won
wta.train.3yrs$q.estimate <- wta.train.3yrs$total_receiving_pts_won /
  wta.train.3yrs$total_pts_received
wta.train.3yrs$q.estimate[which(is.na(wta.train.3yrs$q.estimate))] <- 
  mean(wta.train.3yrs$q.estimate[-which(is.na(wta.train.3yrs$q.estimate))])

q.bar <- mean(wta.train.3yrs$q.estimate)
n <- nrow(wta.test.2014)
res19 <- rep(0,n)
exact.res19 <- rep(0,n) # added much later in
for (i in 1:n){
  winner <- wta.test.2014$winner_name[i]
  loser <- wta.test.2014$loser_name[i]
  winner.idx <- which(wta.train.3yrs$name==winner)
  loser.idx <- which(wta.train.3yrs$name==loser)
  winner.adj.p <- wta.train.3yrs$p.estimate[winner.idx] - 
    (wta.train.3yrs$q.estimate[loser.idx] - q.bar)
  loser.adj.p <- wta.train.3yrs$p.estimate[loser.idx] - 
    (wta.train.3yrs$q.estimate[winner.idx] - q.bar)
  res19[i] <- winner.adj.p > loser.adj.p
  exact.res19[i] <- get.prob.2014(winner.adj.p,loser.adj.p,
                                  wta.test.2014$tourney_name[i],atp=FALSE)
}
mean(res19)
saveRDS(exact.res19,"p_est_exact_probs/wta2014_3y_ns_oaf_exact.rds")
```

#### 20 - 2011-2013 Data - Surface Distinction - Opponent-Adjusted Formula

```{r}
# p's
wta.train.3yrs$grass_p <- wta.train.3yrs$grass_service_pts_won/
  wta.train.3yrs$grass_pts_served
wta.train.3yrs$hard_p <- wta.train.3yrs$hard_service_pts_won/
  wta.train.3yrs$hard_pts_served
wta.train.3yrs$clay_p <- wta.train.3yrs$clay_service_pts_won/
  wta.train.3yrs$clay_pts_served
wta.train.3yrs$grass_p[which(is.na(wta.train.3yrs$grass_p))] <- 
  mean(wta.train.3yrs$grass_p[-which(is.na(wta.train.3yrs$grass_p))])
wta.train.3yrs$hard_p[which(is.na(wta.train.3yrs$hard_p))] <- 
  mean(wta.train.3yrs$hard_p[-which(is.na(wta.train.3yrs$hard_p))])
wta.train.3yrs$clay_p[which(is.na(wta.train.3yrs$clay_p))] <- 
  mean(wta.train.3yrs$clay_p[-which(is.na(wta.train.3yrs$clay_p))])
# q's
wta.train.3yrs$grass_q <- wta.train.3yrs$grass_receiving_pts_won /
  wta.train.3yrs$grass_pts_received
wta.train.3yrs$hard_q <- wta.train.3yrs$hard_receiving_pts_won /
  wta.train.3yrs$hard_pts_received
wta.train.3yrs$clay_q <- wta.train.3yrs$clay_receiving_pts_won /
  wta.train.3yrs$clay_pts_received
wta.train.3yrs$grass_q[which(is.na(wta.train.3yrs$grass_q))] <- 
  mean(wta.train.3yrs$grass_q[-which(is.na(wta.train.3yrs$grass_q))])
wta.train.3yrs$hard_q[which(is.na(wta.train.3yrs$hard_q))] <- 
  mean(wta.train.3yrs$hard_q[-which(is.na(wta.train.3yrs$hard_q))])
wta.train.3yrs$clay_q[which(is.na(wta.train.3yrs$clay_q))] <- 
  mean(wta.train.3yrs$clay_q[-which(is.na(wta.train.3yrs$clay_q))])
q.bar.grass <- mean(wta.train.3yrs$grass_q)
q.bar.hard <- mean(wta.train.3yrs$hard_q)
q.bar.clay <- mean(wta.train.3yrs$clay_q)

n <- nrow(wta.test.2014)
res20 <- rep(0,n)
exact.res20 <- rep(0,n) # added much later in
for (i in 1:n){
  winner <- wta.test.2014$winner_name[i]
  loser <- wta.test.2014$loser_name[i]
  winner.idx <- which(wta.train.3yrs$name==winner)
  loser.idx <- which(wta.train.3yrs$name==loser)
  surf <- wta.test.2014$surface[i]
  if (surf=="Grass") {
    winner.adj.p <- wta.train.3yrs$grass_p[winner.idx] - 
      (wta.train.3yrs$grass_q[loser.idx] - q.bar.grass)
    loser.adj.p <- wta.train.3yrs$grass_p[loser.idx] - 
      (wta.train.3yrs$grass_q[winner.idx] - q.bar.grass)
    res20[i] <- winner.adj.p > loser.adj.p
  } else if (surf=="Hard"){
    winner.adj.p <- wta.train.3yrs$hard_p[winner.idx] - 
      (wta.train.3yrs$hard_q[loser.idx] - q.bar.hard)
    loser.adj.p <- wta.train.3yrs$hard_p[loser.idx] - 
      (wta.train.3yrs$hard_q[winner.idx] - q.bar.hard)
    res20[i] <- winner.adj.p > loser.adj.p
  } else if (surf=="Clay"){
    winner.adj.p <- wta.train.3yrs$clay_p[winner.idx] - 
      (wta.train.3yrs$clay_q[loser.idx] - q.bar.clay)
    loser.adj.p <- wta.train.3yrs$clay_p[loser.idx] - 
      (wta.train.3yrs$clay_q[winner.idx] - q.bar.clay)
    res20[i] <- winner.adj.p > loser.adj.p
  }
  exact.res20[i] <- get.prob.2014(winner.adj.p,loser.adj.p,
                                  wta.test.2014$tourney_name[i],atp=FALSE)
}
mean(res20)
saveRDS(exact.res20,"p_est_exact_probs/wta2014_3y_s_oaf_exact.rds")
```

#### 21 - 2013 Data - No Surface Distinction - H2H Data With CO Support

```{r}
# make a copy where co augmentation will go
data.21 <- wta.h2h.2013
# in h2h/co datasets, p1 is always the winner
data.21$w_total_pts_served <- data.21$grass_pts_served1 + 
  data.21$hard_pts_served1 + data.21$clay_pts_served1
data.21$w_total_service_pts_won <- data.21$grass_service_pts_won1 +
  data.21$hard_service_pts_won1 + data.21$clay_service_pts_won1
data.21$w_p <- data.21$w_total_service_pts_won/data.21$w_total_pts_served
data.21$l_total_pts_served <- data.21$grass_pts_served2 + 
  data.21$hard_pts_served2 + data.21$clay_pts_served2
data.21$l_total_service_pts_won <- data.21$grass_service_pts_won2 +
  data.21$hard_service_pts_won2 + data.21$clay_service_pts_won2
data.21$l_p <- data.21$l_total_service_pts_won/data.21$l_total_pts_served

# first see accuracy for entries where h2h data is available
h2h.valid <- which(!is.na(data.21$w_p)) #l_p also works
res21.h2h <- rep(0,length(h2h.valid))
exact21.h2h <- rep(0,length(h2h.valid))
for (i in 1:length(h2h.valid)){
  res21.h2h[i] <- data.21$w_p[h2h.valid[i]] > data.21$l_p[h2h.valid[i]]
  exact21.h2h[i] <- get.prob.2014(data.21$w_p[h2h.valid[i]],data.21$l_p[h2h.valid[i]],
                                  wta.test.2014$tourney_name[h2h.valid[i]],atp=FALSE)
}
mean(res21.h2h) # 0.84483

# next see accuracy for all entries where co data is available 
data.21$w_total_pts_served_co <- wta.co.2013$grass_pts_served1 + 
  wta.co.2013$hard_pts_served1 + wta.co.2013$clay_pts_served1
data.21$w_total_service_pts_won_co <- wta.co.2013$grass_service_pts_won1 +
  wta.co.2013$hard_service_pts_won1 + wta.co.2013$clay_service_pts_won1
data.21$w_p_co <- data.21$w_total_service_pts_won_co/data.21$w_total_pts_served_co
data.21$l_total_pts_served_co <- wta.co.2013$grass_pts_served2 + 
  wta.co.2013$hard_pts_served2 + wta.co.2013$clay_pts_served2
data.21$l_total_service_pts_won_co <- wta.co.2013$grass_service_pts_won2 +
  wta.co.2013$hard_service_pts_won2 + wta.co.2013$clay_service_pts_won2
data.21$l_p_co <- data.21$l_total_service_pts_won_co/data.21$l_total_pts_served_co
co.valid <- which(!is.na(data.21$w_p_co) & !is.na(data.21$l_p_co)) #l_p_co also works
res21.co <- rep(0,length(co.valid))
exact21.co <- rep(0,length(co.valid))
for (i in 1:length(co.valid)){
  res21.co[i] <- data.21$w_p_co[co.valid[i]] > data.21$l_p_co[co.valid[i]]
  exact21.co[i] <- get.prob.2014(data.21$w_p_co[co.valid[i]],data.21$l_p_co[co.valid[i]],
                                 wta.test.2014$tourney_name[co.valid[i]],atp=FALSE)
}
mean(res21.co) # 0.628

res21.no_co <- res5
res21.no_co[h2h.valid] <- res21.h2h
mean(res21.no_co) # 0.675

# finally h2h with co support
res21 <- res5 # first use general data and apply new results on top
res21[co.valid] <- res21.co
res21[h2h.valid] <- res21.h2h
mean(res21)
```
```{r}
# later added to save results
res21.h2h.sv <- rep(-1,nrow(wta.test.2014))
res21.h2h.sv[h2h.valid] <- res21.h2h
res21.co.sv <- rep(-1,nrow(wta.test.2014))
res21.co.sv[co.valid] <- res21.co
exact21.h2h.sv <- rep(-1,nrow(wta.test.2014))
exact21.h2h.sv[h2h.valid] <- exact21.h2h
exact21.co.sv <- rep(-1,nrow(wta.test.2014))
exact21.co.sv[co.valid] <- exact21.co
saveRDS(exact21.h2h.sv,"p_est_exact_probs/wta2014_1y_ns_h2h.rds")
saveRDS(exact21.co.sv,"p_est_exact_probs/wta2014_1y_ns_co.rds")
```

#### 22 - 2013 Data - Surface Distinction - H2H Data With CO Support

```{r}
data.22 <- wta.h2h.2013
# g for grass_p, h for hard_p, c for clay_p
data.22$w_g <- data.22$grass_service_pts_won1/data.22$grass_pts_served1
data.22$w_h <- data.22$hard_service_pts_won1/data.22$hard_pts_served1
data.22$w_c <- data.22$clay_service_pts_won1/data.22$clay_pts_served1
data.22$l_g <- data.22$grass_service_pts_won2/data.22$grass_pts_served2
data.22$l_h <- data.22$hard_service_pts_won2/data.22$hard_pts_served2
data.22$l_c <- data.22$clay_service_pts_won2/data.22$clay_pts_served2

# see performance for pure h2h data separated by surface
res22.h2h <- c() # initialize and add elements by res14.h2h <- c(res14.h2h,...)
exact22.h2h <- c()
h2h.valid <- rep(0,nrow(wta.test.2014))
for (i in 1:nrow(wta.test.2014)){
  if (wta.test.2014$surface[i]=="Grass" && !is.na(data.22$w_g[i])){
    res22.h2h <- c(res22.h2h, data.22$w_g[i] > data.22$l_g[i])
    exact22.h2h <- c(exact22.h2h,
                     get.prob.2014(data.22$w_g[i],data.22$l_g[i],
                                   wta.test.2014$tourney_name[i],atp=FALSE))
    h2h.valid[i] <- 1
  } else if (wta.test.2014$surface[i]=="Hard" && !is.na(data.22$w_h[i])){
    res22.h2h <- c(res22.h2h, data.22$w_h[i] > data.22$l_h[i])
    exact22.h2h <- c(exact22.h2h,
                     get.prob.2014(data.22$w_h[i],data.22$l_h[i],
                                   wta.test.2014$tourney_name[i],atp=FALSE))
    h2h.valid[i] <- 1
  } else if (wta.test.2014$surface[i]=="Clay" && !is.na(data.22$w_c[i])){
    res22.h2h <- c(res22.h2h, data.22$w_c[i] > data.22$l_c[i])
    exact22.h2h <- c(exact22.h2h,
                     get.prob.2014(data.22$w_c[i],data.22$l_c[i],
                                   wta.test.2014$tourney_name[i],atp=FALSE))
    h2h.valid[i] <- 1
  }
}
h2h.valid <- which(h2h.valid==1)
mean(res22.h2h) # 0.867

# see performance for pure co data separated by surface
data.22$w_g_co <- wta.co.2013$grass_service_pts_won1/wta.co.2013$grass_pts_served1
data.22$w_h_co <- wta.co.2013$hard_service_pts_won1/wta.co.2013$hard_pts_served1
data.22$w_c_co <- wta.co.2013$clay_service_pts_won1/wta.co.2013$clay_pts_served1
data.22$l_g_co <- wta.co.2013$grass_service_pts_won2/wta.co.2013$grass_pts_served2
data.22$l_h_co <- wta.co.2013$hard_service_pts_won2/wta.co.2013$hard_pts_served2
data.22$l_c_co <- wta.co.2013$clay_service_pts_won2/wta.co.2013$clay_pts_served2
res22.co <- c() # same method as before
exact22.co <- c()
co.valid <- rep(0,nrow(wta.test.2014))
for (i in 1:nrow(wta.test.2014)){
  if (wta.test.2014$surface[i]=="Grass" & 
      !is.na(data.22$w_g_co[i]) & !is.na(data.22$l_g_co[i])){
    res22.co <- c(res22.co, data.22$w_g_co[i] > data.22$l_g_co[i])
    exact22.co <- c(exact22.co,
                    get.prob.2014(data.22$w_g_co[i],data.22$l_g_co[i],
                                  wta.test.2014$tourney_name[i],atp=FALSE))
    co.valid[i] <- 1
  } else if (wta.test.2014$surface[i]=="Hard" &
             !is.na(data.22$w_h_co[i]) & !is.na(data.22$l_h_co[i])){
    res22.co <- c(res22.co, data.22$w_h_co[i] > data.22$l_h_co[i])
    exact22.co <- c(exact22.co,
                    get.prob.2014(data.22$w_h_co[i],data.22$l_h_co[i],
                                  wta.test.2014$tourney_name[i],atp=FALSE))
    co.valid[i] <- 1
  } else if (wta.test.2014$surface[i]=="Clay" & 
             !is.na(data.22$w_c_co[i]) & !is.na(data.22$l_c_co[i])){
    res22.co <- c(res22.co, data.22$w_c_co[i] > data.22$l_c_co[i])
    exact22.co <- c(exact22.co,
                    get.prob.2014(data.22$w_c_co[i],data.22$l_c_co[i],
                                  wta.test.2014$tourney_name[i],atp=FALSE))
    co.valid[i] <- 1
  }
}
co.valid <- which(co.valid==1)
mean(res22.co) # 0.605

# h2h overlaid on general data
res22.no_co <- res6
res22.no_co[h2h.valid] <- res22.h2h
mean(res22.no_co) # 0.679

# h2h -> co -> general
res22 <- res6
res22[co.valid] <- res22.co
res22[h2h.valid] <- res22.h2h
mean(res22)
```

```{r}
# later added to save results
res22.h2h.sv <- rep(-1,nrow(wta.test.2014))
res22.h2h.sv[h2h.valid] <- res22.h2h
res22.co.sv <- rep(-1,nrow(wta.test.2014))
res22.co.sv[co.valid] <- res22.co
exact22.h2h.sv <- rep(-1,nrow(wta.test.2014))
exact22.h2h.sv[h2h.valid] <- exact22.h2h
exact22.co.sv <- rep(-1,nrow(wta.test.2014))
exact22.co.sv[co.valid] <- exact22.co
saveRDS(exact22.h2h.sv,"p_est_exact_probs/wta2014_1y_s_h2h.rds")
saveRDS(exact22.co.sv,"p_est_exact_probs/wta2014_1y_s_co.rds")
```

#### 23 - 2011-2013 Data - No Surface Distinction - H2H Data With CO Support

```{r}
# make a copy where co augmentation will go
data.23 <- wta.h2h.3yrs
# in h2h/co datasets, p1 is always the winner
data.23$w_total_pts_served <- data.23$grass_pts_served1 + 
  data.23$hard_pts_served1 + data.23$clay_pts_served1
data.23$w_total_service_pts_won <- data.23$grass_service_pts_won1 +
  data.23$hard_service_pts_won1 + data.23$clay_service_pts_won1
data.23$w_p <- data.23$w_total_service_pts_won/data.23$w_total_pts_served
data.23$l_total_pts_served <- data.23$grass_pts_served2 + 
  data.23$hard_pts_served2 + data.23$clay_pts_served2
data.23$l_total_service_pts_won <- data.23$grass_service_pts_won2 +
  data.23$hard_service_pts_won2 + data.23$clay_service_pts_won2
data.23$l_p <- data.23$l_total_service_pts_won/data.23$l_total_pts_served

# first see accuracy for entries where h2h data is available
h2h.valid <- which(!is.na(data.23$w_p)) #l_p also works
res23.h2h <- rep(0,length(h2h.valid))
exact23.h2h <- rep(0,length(h2h.valid))
for (i in 1:length(h2h.valid)){
  res23.h2h[i] <- data.23$w_p[h2h.valid[i]] > data.23$l_p[h2h.valid[i]]
  exact23.h2h[i] <- get.prob.2014(data.23$w_p[h2h.valid[i]],data.23$l_p[h2h.valid[i]],
                                  wta.test.2014$tourney_name[h2h.valid[i]],atp=FALSE)
}
mean(res23.h2h) # 0.951

# next see accuracy for all entries where co data is available 
data.23$w_total_pts_served_co <- wta.co.3yrs$grass_pts_served1 + 
  wta.co.3yrs$hard_pts_served1 + wta.co.3yrs$clay_pts_served1
data.23$w_total_service_pts_won_co <- wta.co.3yrs$grass_service_pts_won1 +
  wta.co.3yrs$hard_service_pts_won1 + wta.co.3yrs$clay_service_pts_won1
data.23$w_p_co <- data.23$w_total_service_pts_won_co/data.23$w_total_pts_served_co
data.23$l_total_pts_served_co <- wta.co.3yrs$grass_pts_served2 + 
  wta.co.3yrs$hard_pts_served2 + wta.co.3yrs$clay_pts_served2
data.23$l_total_service_pts_won_co <- wta.co.3yrs$grass_service_pts_won2 +
  wta.co.3yrs$hard_service_pts_won2 + wta.co.3yrs$clay_service_pts_won2
data.23$l_p_co <- data.23$l_total_service_pts_won_co/data.23$l_total_pts_served_co
co.valid <- which(!is.na(data.23$w_p_co) & !is.na(data.23$l_p_co)) 
res23.co <- rep(0,length(co.valid))
exact23.co <- rep(0,length(co.valid))
for (i in 1:length(co.valid)){
  res23.co[i] <- data.23$w_p_co[co.valid[i]] > data.23$l_p_co[co.valid[i]]
  exact23.co[i] <- get.prob.2014(data.23$w_p_co[co.valid[i]],data.23$l_p_co[co.valid[i]],
                                 wta.test.2014$tourney_name[co.valid[i]],atp=FALSE)
}
mean(res23.co) # 0.606

# just h2h and general data
res23.no_co <- res7
res23.no_co[h2h.valid] <- res23.h2h
mean(res23.no_co) # 0.715

# finally h2h with co support
res23 <- res7 
res23[co.valid] <- res23.co
res23[h2h.valid] <- res23.h2h
mean(res23)
```
```{r}
# later added to save results
res23.h2h.sv <- rep(-1,nrow(wta.test.2014))
res23.h2h.sv[h2h.valid] <- res23.h2h
res23.co.sv <- rep(-1,nrow(wta.test.2014))
res23.co.sv[co.valid] <- res23.co
exact23.h2h.sv <- rep(-1,nrow(wta.test.2014))
exact23.h2h.sv[h2h.valid] <- exact23.h2h
exact23.co.sv <- rep(-1,nrow(wta.test.2014))
exact23.co.sv[co.valid] <- exact23.co
saveRDS(exact23.h2h.sv,"p_est_exact_probs/wta2014_3y_ns_h2h.rds")
saveRDS(exact23.co.sv,"p_est_exact_probs/wta2014_3y_ns_co.rds")
```

#### 24 - 2011-2013 Data - Surface Distinction - H2H Data With CO Support

```{r}
data.24 <- wta.h2h.3yrs
# g for grass_p, h for hard_p, c for clay_p
data.24$w_g <- data.24$grass_service_pts_won1/data.24$grass_pts_served1
data.24$w_h <- data.24$hard_service_pts_won1/data.24$hard_pts_served1
data.24$w_c <- data.24$clay_service_pts_won1/data.24$clay_pts_served1
data.24$l_g <- data.24$grass_service_pts_won2/data.24$grass_pts_served2
data.24$l_h <- data.24$hard_service_pts_won2/data.24$hard_pts_served2
data.24$l_c <- data.24$clay_service_pts_won2/data.24$clay_pts_served2

# see performance for pure h2h data separated by surface
res24.h2h <- c() # initialize and add elements by res14.h2h <- c(res14.h2h,...)
exact24.h2h <- c()
h2h.valid <- rep(0,nrow(wta.test.2014))
for (i in 1:nrow(wta.test.2014)){
  if (wta.test.2014$surface[i]=="Grass" && !is.na(data.24$w_g[i])){
    res24.h2h <- c(res24.h2h, data.24$w_g[i] > data.24$l_g[i])
    exact24.h2h <- c(exact24.h2h,
                     get.prob.2014(data.24$w_g[i],data.24$l_g[i],
                                   wta.test.2014$tourney_name[i],atp=FALSE))
    h2h.valid[i] <- 1
  } else if (wta.test.2014$surface[i]=="Hard" && !is.na(data.24$w_h[i])){
    res24.h2h <- c(res24.h2h, data.24$w_h[i] > data.24$l_h[i])
    exact24.h2h <- c(exact24.h2h,
                     get.prob.2014(data.24$w_h[i],data.24$l_h[i],
                                   wta.test.2014$tourney_name[i],atp=FALSE))
    h2h.valid[i] <- 1
  } else if (wta.test.2014$surface[i]=="Clay" && !is.na(data.24$w_c[i])){
    res24.h2h <- c(res24.h2h, data.24$w_c[i] > data.24$l_c[i])
    exact24.h2h <- c(exact24.h2h,
                     get.prob.2014(data.24$w_c[i],data.24$l_c[i],
                                   wta.test.2014$tourney_name[i],atp=FALSE))
    h2h.valid[i] <- 1
  }
}
h2h.valid <- which(h2h.valid==1)
mean(res24.h2h) # 0.926

# see performance for pure co data separated by surface
data.24$w_g_co <- wta.co.3yrs$grass_service_pts_won1/wta.co.3yrs$grass_pts_served1
data.24$w_h_co <- wta.co.3yrs$hard_service_pts_won1/wta.co.3yrs$hard_pts_served1
data.24$w_c_co <- wta.co.3yrs$clay_service_pts_won1/wta.co.3yrs$clay_pts_served1
data.24$l_g_co <- wta.co.3yrs$grass_service_pts_won2/wta.co.3yrs$grass_pts_served2
data.24$l_h_co <- wta.co.3yrs$hard_service_pts_won2/wta.co.3yrs$hard_pts_served2
data.24$l_c_co <- wta.co.3yrs$clay_service_pts_won2/wta.co.3yrs$clay_pts_served2
res24.co <- c() # same method as before
exact24.co <- c()
co.valid <- rep(0,nrow(wta.test.2014))
for (i in 1:nrow(wta.test.2014)){
  if (wta.test.2014$surface[i]=="Grass" & 
      !is.na(data.24$w_g_co[i]) & !is.na(data.24$l_g_co[i])){
    res24.co <- c(res24.co, data.24$w_g_co[i] > data.24$l_g_co[i])
    exact24.co <- c(exact24.co,
                    get.prob.2014(data.24$w_g_co[i],data.24$l_g_co[i],
                                  wta.test.2014$tourney_name[i],atp=FALSE))
    co.valid[i] <- 1
  } else if (wta.test.2014$surface[i]=="Hard" &
             !is.na(data.24$w_h_co[i]) & !is.na(data.24$l_h_co[i])){
    res24.co <- c(res24.co, data.24$w_h_co[i] > data.24$l_h_co[i])
    exact24.co <- c(exact24.co,
                    get.prob.2014(data.24$w_h_co[i],data.24$l_h_co[i],
                                  wta.test.2014$tourney_name[i],atp=FALSE))
    co.valid[i] <- 1
  } else if (wta.test.2014$surface[i]=="Clay" & 
             !is.na(data.24$w_c_co[i]) & !is.na(data.24$l_c_co[i])){
    res24.co <- c(res24.co, data.24$w_c_co[i] > data.24$l_c_co[i])
    exact24.co <- c(exact24.co,
                    get.prob.2014(data.24$w_c_co[i],data.24$l_c_co[i],
                                  wta.test.2014$tourney_name[i],atp=FALSE))
    co.valid[i] <- 1
  }
}
co.valid <- which(co.valid==1)
mean(res24.co) # 0.606

# again see difference if co layer removed
res24.no_co <- res8
res24.no_co[h2h.valid] <- res24.h2h
mean(res24.no_co) # 0.656

res24 <- res8
res24[co.valid] <- res24.co
res24[h2h.valid] <- res24.h2h
mean(res24)
```

```{r}
# later added to save results
res24.h2h.sv <- rep(-1,nrow(wta.test.2014))
res24.h2h.sv[h2h.valid] <- res24.h2h
res24.co.sv <- rep(-1,nrow(wta.test.2014))
res24.co.sv[co.valid] <- res24.co
exact24.h2h.sv <- rep(-1,nrow(wta.test.2014))
exact24.h2h.sv[h2h.valid] <- exact24.h2h
exact24.co.sv <- rep(-1,nrow(wta.test.2014))
exact24.co.sv[co.valid] <- exact24.co
saveRDS(exact24.h2h.sv,"p_est_exact_probs/wta2014_3y_s_h2h.rds")
saveRDS(exact24.co.sv,"p_est_exact_probs/wta2014_3y_s_co.rds")
```

### Note On Further Categories

For knitting/compilation purposes, this notebook will end here and each category going forward will have their own notebook. Further investigations regarding category will also continue in a new notebook.

```{r}
# storing of results for future overlay
saveRDS(res1,file="res14atp_1yr_g_ns.rds")
saveRDS(res2,file="res14atp_1yr_g_s.rds")
saveRDS(res3,file="res14atp_3yr_g_ns.rds")
saveRDS(res4,file="res14atp_3yr_g_s.rds")
saveRDS(res5,file="res14wta_1yr_g_ns.rds")
saveRDS(res6,file="res14wta_1yr_g_s.rds")
saveRDS(res7,file="res14wta_3yr_g_ns.rds")
saveRDS(res8,file="res14wta_3yr_g_s.rds")
saveRDS(res9,file="res14atp_1yr_oaf_ns.rds")
saveRDS(res10,file="res14atp_1yr_oaf_s.rds")
saveRDS(res11,file="res14atp_3yr_oaf_ns.rds")
saveRDS(res12,file="res14atp_3yr_oaf_s.rds")
saveRDS(res17,file="res14wta_1yr_oaf_ns.rds")
saveRDS(res18,file="res14wta_1yr_oaf_s.rds")
saveRDS(res19,file="res14wta_3yr_oaf_ns.rds")
saveRDS(res20,file="res14wta_3yr_oaf_s.rds")
saveRDS(res13.h2h.sv,file="res14atp_1yr_h2h_ns.rds")
saveRDS(res13.co.sv,file="res14atp_1yr_co_ns.rds")
saveRDS(res14.h2h.sv,file="res14atp_1yr_h2h_s.rds")
saveRDS(res14.co.sv,file="res14atp_1yr_co_s.rds")
saveRDS(res15.h2h.sv,file="res14atp_3yr_h2h_ns.rds")
saveRDS(res15.co.sv,file="res14atp_3yr_co_ns.rds")
saveRDS(res16.h2h.sv,file="res14atp_3yr_h2h_s.rds")
saveRDS(res16.co.sv,file="res14atp_3yr_co_s.rds")
saveRDS(res21.h2h.sv,file="res14wta_1yr_h2h_ns.rds")
saveRDS(res21.co.sv,file="res14wta_1yr_co_ns.rds")
saveRDS(res22.h2h.sv,file="res14wta_1yr_h2h_s.rds")
saveRDS(res22.co.sv,file="res14wta_1yr_co_s.rds")
saveRDS(res23.h2h.sv,file="res14wta_3yr_h2h_ns.rds")
saveRDS(res23.co.sv,file="res14wta_3yr_co_ns.rds")
saveRDS(res24.h2h.sv,file="res14wta_3yr_h2h_s.rds")
saveRDS(res24.co.sv,file="res14wta_3yr_co_s.rds")
```