---
title: "Scrap Paper Equivalent"
output: pdf_document
date: "2022-10-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# R Markdown Compiling
{without backslash}

\{with backslash\}

# Names For Python Script

```{r}
dat <- read.csv('../Data Lake/Experiments/2014_atp_testing.csv')
ic.match <- function(score) grep("[A-Za-z]",score)
ic <- ic.match(dat$score)
dat <- dat[-ic,]
names <- unique(c(dat$winner_name,dat$loser_name))
#feed <- paste(names,collapse='","')
feed <- paste(names,collapse="\n")
cat(feed)
```

# Outdated Cat1 Experiments

```{r}
extra <- res18
j <- 1
for (i in 1:nrow(data.22)){
  if (atp.test.2022$surface[i]=="Grass" && !is.na(data.22$w_g[i])){
    extra[i] <- res22.h2h[j]
    j <- j+1
  } else if (atp.test.2022$surface[i]=="Hard" && !is.na(data.22$w_h[i])){
    extra[i] <- res22.h2h[j]
    j <- j+1
  } else if (atp.test.2022$surface[i]=="Clay" && !is.na(data.22$w_c[i])){
    extra[i] <- res22.h2h[j]
    j <- j+1
  }
}
mean(extra)
```
```{r}
extra <- res20
j <- 1
for (i in 1:nrow(data.24)){
  if (atp.test.2022$surface[i]=="Grass" && !is.na(data.24$w_g[i])){
    extra[i] <- res24.h2h[j]
    j <- j+1
  } else if (atp.test.2022$surface[i]=="Hard" && !is.na(data.24$w_h[i])){
    extra[i] <- res24.h2h[j]
    j <- j+1
  } else if (atp.test.2022$surface[i]=="Clay" && !is.na(data.24$w_c[i])){
    extra[i] <- res24.h2h[j]
    j <- j+1
  }
}
mean(extra)
```
```{r}
extra <- res17
h2h.valid <- which(!is.na(data.21$w_p))
extra[h2h.valid] <- res21.h2h
mean(extra)
```
```{r}
extra <- res19
h2h.valid <- which(!is.na(data.23$w_p))
extra[h2h.valid] <- res23.h2h
mean(extra)
```

# Early Plotting of State Paths

```{r}
# depth n plotting
n <- 7
dat <- lu7.atp.2022
plot(1:n,dat[[1]][[2]],'l')#, ylim=c(0.55,0.7)) # adjust ylim on ad-hoc basis
for (i in 2:length(dat)){
  lines(1:n,dat[[i]][[2]])
}
```

# More Cat1 Results

```{r}
res18atp.1yr.h2h.ns <- readRDS("res18atp_1yr_h2h_ns.rds")
res18atp.1yr.h2h.s <- readRDS("res18atp_1yr_h2h_s.rds")
res18atp.3yr.h2h.ns <- readRDS("res18atp_3yr_h2h_ns.rds")
res18atp.3yr.h2h.s <- readRDS("res18atp_3yr_h2h_s.rds")
res18atp.1yr.co.ns <- readRDS("res18atp_1yr_co_ns.rds")
res18atp.1yr.co.s <- readRDS("res18atp_1yr_co_s.rds")
res18atp.3yr.co.ns <- readRDS("res18atp_3yr_co_ns.rds")
res18atp.3yr.co.s <- readRDS("res18atp_3yr_co_s.rds")
res18atp.1yr.oaf.ns <- readRDS("res18atp_1yr_oaf_ns.rds")
res18atp.1yr.oaf.s <- readRDS("res18atp_1yr_oaf_s.rds")
res18atp.3yr.oaf.ns <- readRDS("res18atp_3yr_oaf_ns.rds")
res18atp.3yr.oaf.s <- readRDS("res18atp_3yr_oaf_s.rds")
res18wta.1yr.h2h.ns <- readRDS("res18wta_1yr_h2h_ns.rds")
res18wta.1yr.h2h.s <- readRDS("res18wta_1yr_h2h_s.rds")
res18wta.3yr.h2h.ns <- readRDS("res18wta_3yr_h2h_ns.rds")
res18wta.3yr.h2h.s <- readRDS("res18wta_3yr_h2h_s.rds")
res18wta.1yr.co.ns <- readRDS("res18wta_1yr_co_ns.rds")
res18wta.1yr.co.s <- readRDS("res18wta_1yr_co_s.rds")
res18wta.3yr.co.ns <- readRDS("res18wta_3yr_co_ns.rds")
res18wta.3yr.co.s <- readRDS("res18wta_3yr_co_s.rds")
res18wta.1yr.oaf.ns <- readRDS("res18wta_1yr_oaf_ns.rds")
res18wta.1yr.oaf.s <- readRDS("res18wta_1yr_oaf_s.rds")
res18wta.3yr.oaf.ns <- readRDS("res18wta_3yr_oaf_ns.rds")
res18wta.3yr.oaf.s <- readRDS("res18wta_3yr_oaf_s.rds")
```
```{r}
overlay.h2h.oaf <- function(h2h,oaf){
  h2h.valid <- which(!(h2h==-1))
  res <- oaf
  res[h2h.valid] <- h2h[h2h.valid]
  mean(res)
}
```
```{r}
overlay.h2h.oaf(res18atp.1yr.h2h.ns,res18atp.1yr.oaf.ns)
overlay.h2h.oaf(res18atp.1yr.h2h.s,res18atp.1yr.oaf.s)
overlay.h2h.oaf(res18atp.3yr.h2h.ns,res18atp.3yr.oaf.ns)
overlay.h2h.oaf(res18atp.3yr.h2h.s,res18atp.3yr.oaf.s)
overlay.h2h.oaf(res18wta.1yr.h2h.ns,res18wta.1yr.oaf.ns)
overlay.h2h.oaf(res18wta.1yr.h2h.s,res18wta.1yr.oaf.s)
overlay.h2h.oaf(res18wta.3yr.h2h.ns,res18wta.3yr.oaf.ns)
overlay.h2h.oaf(res18wta.3yr.h2h.s,res18wta.3yr.oaf.s)
```
```{r}
overlay.h2h.co.oaf <- function(h2h,co,oaf){
  h2h.valid <- which(!(h2h==-1))
  co.valid <- which(!(co==-1))
  res <- oaf
  res[co.valid] <- co[co.valid]
  res[h2h.valid] <- h2h[h2h.valid]
  mean(res)
}
```
```{r}
overlay.h2h.co.oaf(res18atp.1yr.h2h.ns,res18atp.1yr.co.ns,res18atp.1yr.oaf.ns)
overlay.h2h.co.oaf(res18atp.1yr.h2h.s,res18atp.1yr.co.s,res18atp.1yr.oaf.s)
overlay.h2h.co.oaf(res18atp.3yr.h2h.ns,res18atp.3yr.co.ns,res18atp.3yr.oaf.ns)
overlay.h2h.co.oaf(res18atp.3yr.h2h.s,res18atp.3yr.co.s,res18atp.3yr.oaf.s)
overlay.h2h.co.oaf(res18wta.1yr.h2h.ns,res18wta.1yr.co.ns,res18wta.1yr.oaf.ns)
overlay.h2h.co.oaf(res18wta.1yr.h2h.s,res18wta.1yr.co.s,res18wta.1yr.oaf.s)
overlay.h2h.co.oaf(res18wta.3yr.h2h.ns,res18wta.3yr.co.ns,res18wta.3yr.oaf.ns)
overlay.h2h.co.oaf(res18wta.3yr.h2h.s,res18wta.3yr.co.s,res18wta.3yr.oaf.s)
```
# Testing Patched match.win.prob

```{r}
# NON-REPEATABLE FOR NOW
# list of grand slams as their Men's singles are played to best 3 of 5 sets
# naming convention following that found in the test sets
grand.slams <- c("Australian Open","Roland Garros","Wimbledon","US Open")

# overall function to do experiments with
conduct.experiment.2014 <- function(inactive.states, P, test.set, atp=TRUE){
  # inactive.states:
  #   vector containing states (19 for tiebreak) to deactivate, i.e. 
  #   replace the state's unique p with the player's overall p
  # P:
  #   data.frame containing players' individual p vectors
  #   usually obtained via create.p.vector output
  # test.set:
  #   data set used to test accuracy of prediction
  # atp:
  #   boolean defaulted to true if test.set is ATP data
  
  # make copy of P and change copy to align with specified inactive.states
  cP <- P[,1:19]
  cP[,inactive.states] <- P[,20]
  
  # record exact probability values from model
  # so we can examine closer if we want
  n <- nrow(test.set)
  exact <- rep(0,n)
  
  # experiment begins
  pbp.names <- rownames(cP)
  for (i in 1:n){
    matchup <- test.set[i,]
    winner <- matchup$winner_name
    loser <- matchup$loser_name
    inds <- match(c(winner,loser),pbp.names)
    winner.P <- unname(unlist(cP[inds[1],]))
    loser.P <- unname(unlist(cP[inds[2],]))
    if (matchup$tourney_name %in% grand.slams){
      if (atp){
        if (matchup$tourney_name=="US Open") {
          exact[i] <- match.win.prob(p1=winner.P,p2=loser.P,format=1)
        } else {
          exact[i] <- match.win.prob(p1=winner.P,p2=loser.P,format=5)
        }
      } else {
        if (matchup$tourney_name=="US Open") {
          exact[i] <- match.win.prob(p1=winner.P,p2=loser.P,format=0)
        } else {
          exact[i] <- match.win.prob(p1=winner.P,p2=loser.P,format=4)
        }
      }
    } else {
      exact[i] <- match.win.prob(p1=winner.P,p2=loser.P)
    }
  }
  res <- exact > 0.5
  return(list("score"=mean(res),"result"=res,"exact"=exact))
}
```

# Observed p's resulting accuracy

```{r}
wta.14 <- read.csv('../Data Lake/Experiments/2014_wta_testing.csv')
wta.18 <- read.csv('../Data Lake/Experiments/2018_wta_testing.csv')
wta.22 <- read.csv('../Data Lake/Experiments/2022_wta_testing.csv')
atp.14 <- read.csv('../Data Lake/Experiments/2014_atp_testing.csv')
atp.18 <- read.csv('../Data Lake/Experiments/2018_atp_testing.csv')
atp.22 <- read.csv('../Data Lake/Experiments/2022_atp_testing.csv')
ic.match <- function(score) grep("[A-Za-z]",score)
wta.14 <- wta.14[-ic.match(wta.14$score),]
wta.18 <- wta.18[-ic.match(wta.18$score),]
wta.22 <- wta.22[-ic.match(wta.22$score),]
atp.14 <- atp.14[-ic.match(atp.14$score),]
atp.18 <- atp.18[-ic.match(atp.18$score),]
atp.22 <- atp.22[-ic.match(atp.22$score),]
```
```{r}
testsets <- list(wta.14,wta.18,wta.22,atp.14,atp.18,atp.22)
for (i in 1:6){
  ts <- testsets[[i]]
  ts$w_p <- (ts$w_1stWon+ts$w_2ndWon)/ts$w_svpt
  ts$l_p <- (ts$l_1stWon+ts$l_2ndWon)/ts$l_svpt
  ts$pred <- ts$w_p > ts$l_p
  print(mean(ts$pred[which(!is.na(ts$pred))]))
}
```

# Percentage of overlapping names in test sets

```{r}
n <- length(c)
perc <- rep(0,n)
for (i in 1:n){
  if (c[i] %in% b){
    perc[i]=1
  }
}
mean(perc)
# 43.284% names preserved ATP 2014 -> 2018
```

# Looking At 3 Surface Scores Separatedly

```{r ATP 1 Year}
dat <- atp.test.2022
dat$atp1yr <- res2
mean(dat$atp1yr) # aggregated, col 28 
mean(dat[which(dat$surface=="Clay"),28])
mean(dat[which(dat$surface=="Hard"),28])
mean(dat[which(dat$surface=="Grass"),28])
```
```{r ATP 3 Years}
dat$atp3yr <- res4
mean(dat$atp3yr) # aggregated, col 29 
mean(dat[which(dat$surface=="Clay"),29])
mean(dat[which(dat$surface=="Hard"),29])
mean(dat[which(dat$surface=="Grass"),29])
```
```{r WTA 1 Year}
# sample sizes:
# 2014 clay-43, hard-150, grass-15
dat <- wta.test.2022
dat$wta1yr <- res6
mean(dat$wta1yr) # aggregated, col 28 
mean(dat[which(dat$surface=="Clay"),28])
mean(dat[which(dat$surface=="Hard"),28])
mean(dat[which(dat$surface=="Grass"),28])
```

# Momentum Set Matrix Scrap

```{r}
source("matrices/set_matrices.R")
library(expm)
p.a <- 10
p.b <- 100
Ms <- game.to.set.matrices(p=p.a,q=p.b)
I <- diag(5)
Z <- matrix(0,nrow=5,ncol=38)
M <- cbind(rbind(Ms$Q,Z),rbind(Ms$R,I))
colnames(M) <- c("0-0","1-0","0-1","2-0","1-1","0-2","3-0","2-1","1-2",
                 "0-3","4-0","3-1","2-2","1-3","0-4",rep("T",28))
```
```{r}
(M%^%3)[1,]
```
```{r}
MAlt <- M
MAlt <- cbind(rbind(MAlt,matrix(0,nrow=2,ncol=43)),
              rbind(matrix(0,nrow=43,ncol=2),diag(2)))
MAlt[6,10] <- 0
MAlt[6,45] <- 1-p.a
MAlt[7,11] <- 0
MAlt[7,44] <- 1-p.b
MAlt[8,44] <- p.a*(1-p.b)*(1-p.b)
MAlt[8,12] <- (1-p.b)*(1-p.a+p.a*p.b)
```
```{r}
(MAlt%^%4)[1,]
```
```{r}
demo <- function(x,y){
  ret <- (1-x)*(1-y)/(2*(1-x)*(1-y)+x*y)
}
```


# Random H2H Examination

```{r}
d <- readRDS("res18atp_3yr_h2h_ns.rds")
dat <- read.csv('../Data Lake/Experiments/2018_atp_testing.csv')
ic.match <- function(score) grep("[A-Za-z]",score)
ic.atp <- ic.match(dat$score)
dat <- dat[-ic.atp,]
row.names(dat) <- NULL
dat$H2H <- d
dat <- dat[,c(2,4:8,28)]
```
```{r}
v1 <- read.csv('../Data Lake/Players/crucial_h2h_error/2017_atp_co.csv')
v2 <- read.csv('../Data Lake/Players/2017_atp_co.csv')
v3 <- read.csv('../Data Lake/CO Examination/2017_atp_co.csv')
length(which(v1<v3))
```
```{r}
e2 <- read.csv('../Data Lake/Players/2017_atp_h2h.csv')
e3 <- read.csv('../Data Lake/CO Examination/2017_atp_h2h.csv')
length(which(e2!=e3))
```

# CO(OAF)
```{r}
source("case_patching.R")
# grand.slams <- c("Australian Open","Roland Garros","Wimbledon","US Open")
grand.slams <- c("Australian Open","Roland Garros","Wimbledon","Us Open") # 2022
# "Us Open" specific to 2022 test sets
get.prob.2022 <- function(p1,p2,match,atp=TRUE){
  if (is.na(p1)||is.na(p2)){
    return(NA)
  }
  if (match %in% grand.slams){
    ret <- match.win.prob.nonpw(p1,p2,format=2+atp)
  } else {
    ret <- match.win.prob.nonpw(p1,p2,format=0)
  }
  return(ret)
}
```
```{r}
dat <- read.csv('../Data Lake/Players/2019-2021_wta_co.csv')
test.matches <- read.csv('../Data Lake/Experiments/2022_wta_testing.csv')
ns.exact.a <- "p_est_exact_probs/wta2022_3y_ns_cooaf.rds"
s.exact.a <- "p_est_exact_probs/wta2022_3y_s_cooaf.rds"
ns.a <- "res22wta_3yr_cooaf_ns.rds"
s.a <- "res22wta_3yr_cooaf_s.rds"
atp <- FALSE
ic.match <- function(score) grep("[A-Za-z]",score)
ic <- ic.match(test.matches$score)
dat <- dat[-ic,]
test.matches <- test.matches[-ic,]
dat$surface <- test.matches$surface
dat$tour <- test.matches$tourney_name
rm(ic.match,ic,test.matches)

# p's and q's for oaf applied to co
dat$co.w.p <- (dat$grass_service_pts_won1
               +dat$hard_service_pts_won1
               +dat$clay_service_pts_won1)/(
                 dat$grass_pts_served1
                 +dat$hard_pts_served1
                 +dat$clay_pts_served1)
dat$co.l.p <- (dat$grass_service_pts_won2
               +dat$hard_service_pts_won2
               +dat$clay_service_pts_won2)/(
                 dat$grass_pts_served2
                 +dat$hard_pts_served2
                 +dat$clay_pts_served2)
dat$co.w.q <- (dat$grass_receiving_pts_won1
               +dat$hard_receiving_pts_won1
               +dat$clay_receiving_pts_won1)/(
                 dat$grass_pts_received1
                 +dat$hard_pts_received1
                 +dat$clay_pts_received1)
dat$co.l.q <- (dat$grass_receiving_pts_won2
               +dat$hard_receiving_pts_won2
               +dat$clay_receiving_pts_won2)/(
                 dat$grass_pts_received2
                 +dat$hard_pts_received2
                 +dat$clay_pts_received2)
# with the average q of all the testset players
# we can now calculate the non-surface co results
# won't use the combined index above where both winner and loser has data
# for the q average, instead will use all the q's available 
co.avg.q <- mean(c(dat$co.w.q[which(!is.na(dat$co.w.q))],
                   dat$co.l.q[which(!is.na(dat$co.l.q))]))
dat$co.ns <- dat$co.w.p - (dat$co.l.q - co.avg.q) > 
  dat$co.l.p - (dat$co.w.q - co.avg.q)
### added for exact additions, e.g. H2H+CO(OAF) ###
dat$exact.ns <- NA
for (i in 1:(nrow(dat))){
  dat$exact.ns[i] <- get.prob.2018(dat$co.w.p[i] - (dat$co.l.q[i] - co.avg.q),
                                   dat$co.l.p[i] - (dat$co.w.q[i] - co.avg.q),
                                   match=dat$tour[i],atp=atp)
  if (is.na(dat$exact.ns[i])) {
    dat$exact.ns[i] <- -1
  }
}
ns.exact.f <- dat$exact.ns
saveRDS(ns.exact.f,ns.exact.a)
###################################################
mean(dat$co.ns[which(!is.na(dat$co.ns))])
nrow(dat)-length(which(is.na(dat$co.ns)))


dat$co.w.grass.p <- dat$grass_service_pts_won1/dat$grass_pts_served1
dat$co.w.hard.p <- dat$hard_service_pts_won1/dat$hard_pts_served1
dat$co.w.clay.p <- dat$clay_service_pts_won1/dat$clay_pts_served1
dat$co.l.grass.p <- dat$grass_service_pts_won2/dat$grass_pts_served2
dat$co.l.hard.p <- dat$hard_service_pts_won2/dat$hard_pts_served2
dat$co.l.clay.p <- dat$clay_service_pts_won2/dat$clay_pts_served2
dat$co.w.grass.q <- dat$grass_receiving_pts_won1/dat$grass_pts_received1
dat$co.w.hard.q <- dat$hard_receiving_pts_won1/dat$hard_pts_received1
dat$co.w.clay.q <- dat$clay_receiving_pts_won1/dat$clay_pts_received1
dat$co.l.grass.q <- dat$grass_receiving_pts_won2/dat$grass_pts_received2
dat$co.l.hard.q <- dat$hard_receiving_pts_won2/dat$hard_pts_received2
dat$co.l.clay.q <- dat$clay_receiving_pts_won2/dat$clay_pts_received2
# get oaf co results by surface
co.avg.grass.q <- mean(c(dat$co.w.grass.q[which(!is.na(dat$co.w.grass.q))],
                         dat$co.l.grass.q[which(!is.na(dat$co.l.grass.q))]))
co.avg.hard.q <- mean(c(dat$co.w.hard.q[which(!is.na(dat$co.w.hard.q))],
                        dat$co.l.hard.q[which(!is.na(dat$co.l.hard.q))]))
co.avg.clay.q <- mean(c(dat$co.w.clay.q[which(!is.na(dat$co.w.clay.q))],
                        dat$co.l.clay.q[which(!is.na(dat$co.l.clay.q))]))
# calculating surface
dat$co.s <- NA
dat$exact.s <- NA
for (i in 1:nrow(dat)){
  surface <- dat$surface[i]
  if (surface=="Grass"){
    dat$co.s[i] <- dat$co.w.grass.p[i] - (dat$co.l.grass.q[i] - co.avg.grass.q) >
      dat$co.l.grass.p[i] - (dat$co.w.grass.q[i] - co.avg.grass.q)
    dat$exact.s[i] <- get.prob.2018(
      dat$co.w.grass.p[i] - (dat$co.l.grass.q[i] - co.avg.grass.q),
      dat$co.l.grass.p[i] - (dat$co.w.grass.q[i] - co.avg.grass.q),
      match=dat$tour[i],atp=atp)
  } else if (surface=="Hard"){
    dat$co.s[i] <- dat$co.w.hard.p[i] - (dat$co.l.hard.q[i] - co.avg.hard.q) >
      dat$co.l.hard.p[i] - (dat$co.w.hard.q[i] - co.avg.hard.q)
    dat$exact.s[i] <- get.prob.2018(
      dat$co.w.hard.p[i] - (dat$co.l.hard.q[i] - co.avg.hard.q),
      dat$co.l.hard.p[i] - (dat$co.w.hard.q[i] - co.avg.hard.q),
      match=dat$tour[i],atp=atp)
  } else if (surface=="Clay"){
    dat$co.s[i] <- dat$co.w.clay.p[i] - (dat$co.l.clay.q[i] - co.avg.clay.q) >
      dat$co.l.clay.p[i] - (dat$co.w.clay.q[i] - co.avg.clay.q)
    dat$exact.s[i] <- get.prob.2018(
      dat$co.w.clay.p[i] - (dat$co.l.clay.q[i] - co.avg.clay.q),
      dat$co.l.clay.p[i] - (dat$co.w.clay.q[i] - co.avg.clay.q),
      match=dat$tour[i],atp=atp)
  }
}
mean(dat$co.s[which(!is.na(dat$co.s))])
nrow(dat)-length(which(is.na(dat$co.s)))


# saving files for overlays
res.ns <- dat$co.ns
s.exact.f <- dat$exact.s
res.ns[which(is.na(res.ns))] <- -1
s.exact.f[which(is.na(s.exact.f))] <- -1
saveRDS(s.exact.f,s.exact.a)
saveRDS(res.ns,file=ns.a)
res.s <- dat$co.s
res.s[which(is.na(res.s))] <- -1
saveRDS(res.s,file=s.a)
```

# CO2

```{r}
atp14.1y <- read.csv('../Data Lake/Players/2013_atp_co2.csv')
atp14.3y <- read.csv('../Data Lake/Players/2011-2013_atp_co2.csv')
wta14.1y <- read.csv('../Data Lake/Players/2013_wta_co2.csv')
wta14.3y <- read.csv('../Data Lake/Players/2011-2013_wta_co2.csv')
atp18.1y <- read.csv('../Data Lake/Players/2017_atp_co2.csv')
atp18.3y <- read.csv('../Data Lake/Players/2015-2017_atp_co2.csv')
wta18.1y <- read.csv('../Data Lake/Players/2017_wta_co2.csv')
wta18.3y <- read.csv('../Data Lake/Players/2015-2017_wta_co2.csv')
atp22.1y <- read.csv('../Data Lake/Players/2021_atp_co2.csv')
atp22.3y <- read.csv('../Data Lake/Players/2019-2021_atp_co2.csv')
wta22.1y <- read.csv('../Data Lake/Players/2021_wta_co2.csv')
wta22.3y <- read.csv('../Data Lake/Players/2019-2021_wta_co2.csv')
tm.atp14 <- read.csv('../Data Lake/Experiments/2014_atp_testing.csv')
tm.atp18 <- read.csv('../Data Lake/Experiments/2018_atp_testing.csv')
tm.atp22 <- read.csv('../Data Lake/Experiments/2022_atp_testing.csv')
tm.wta14 <- read.csv('../Data Lake/Experiments/2014_wta_testing.csv')
tm.wta18 <- read.csv('../Data Lake/Experiments/2018_wta_testing.csv')
tm.wta22 <- read.csv('../Data Lake/Experiments/2022_wta_testing.csv')
ic.match <- function(score) grep("[A-Za-z]",score)
ic.atp14 <- ic.match(tm.atp14$score)
ic.atp18 <- ic.match(tm.atp18$score)
ic.atp22 <- ic.match(tm.atp22$score)
ic.wta14 <- ic.match(tm.wta14$score)
ic.wta18 <- ic.match(tm.wta18$score)
ic.wta22 <- ic.match(tm.wta22$score)
atp14.1y <- atp14.1y[-ic.atp14,]
atp14.3y <- atp14.3y[-ic.atp14,]
wta14.1y <- wta14.1y[-ic.wta14,]
wta14.3y <- wta14.3y[-ic.wta14,]
atp18.1y <- atp18.1y[-ic.atp18,]
atp18.3y <- atp18.3y[-ic.atp18,]
wta18.1y <- wta18.1y[-ic.wta18,]
wta18.3y <- wta18.3y[-ic.wta18,]
atp22.1y <- atp22.1y[-ic.atp22,]
atp22.3y <- atp22.3y[-ic.atp22,]
wta22.1y <- wta22.1y[-ic.wta22,]
wta22.3y <- wta22.3y[-ic.wta22,]
rm(tm.atp14,tm.atp18,tm.atp22,tm.wta14,tm.wta18,tm.wta22,
   ic.atp14,ic.atp18,ic.atp22,ic.wta14,ic.wta18,ic.wta22,ic.match)
```

```{r}
co2.res <- function(dat){
  dat$p1 <- dat$service_pts_won1/dat$pts_served1
  dat$p2 <- dat$service_pts_won2/dat$pts_served2
  dat$res <- dat$p1 > dat$p2
  dat$res[which(is.na(dat$res))] <- -1
  return(dat$res)
}
```

```{r}
res14atp.1yr.co2 <- co2.res(atp14.1y)
saveRDS(res14atp.1yr.co2,file="res14atp_1yr_co2.rds")
res14atp.3yr.co2 <- co2.res(atp14.3y)
saveRDS(res14atp.3yr.co2,file="res14atp_3yr_co2.rds")
res14wta.1yr.co2 <- co2.res(wta14.1y)
saveRDS(res14wta.1yr.co2,file="res14wta_1yr_co2.rds")
res14wta.3yr.co2 <- co2.res(wta14.3y)
saveRDS(res14wta.3yr.co2,file="res14wta_3yr_co2.rds")
res18atp.1yr.co2 <- co2.res(atp18.1y)
saveRDS(res18atp.1yr.co2,file="res18atp_1yr_co2.rds")
res18atp.3yr.co2 <- co2.res(atp18.3y)
saveRDS(res18atp.3yr.co2,file="res18atp_3yr_co2.rds")
res18wta.1yr.co2 <- co2.res(wta18.1y)
saveRDS(res18wta.1yr.co2,file="res18wta_1yr_co2.rds")
res18wta.3yr.co2 <- co2.res(wta18.3y)
saveRDS(res18wta.3yr.co2,file="res18wta_3yr_co2.rds")
res22atp.1yr.co2 <- co2.res(atp22.1y)
saveRDS(res22atp.1yr.co2,file="res22atp_1yr_co2.rds")
res22atp.3yr.co2 <- co2.res(atp22.3y)
saveRDS(res22atp.3yr.co2,file="res22atp_3yr_co2.rds")
res22wta.1yr.co2 <- co2.res(wta22.1y)
saveRDS(res22wta.1yr.co2,file="res22wta_1yr_co2.rds")
res22wta.3yr.co2 <- co2.res(wta22.3y)
saveRDS(res22wta.3yr.co2,file="res22wta_3yr_co2.rds")
```

```{r}
print("14-ATP")
mean(res14atp.1yr.co2[which(res14atp.1yr.co2>=0)])
length(res14atp.1yr.co2)-length(which(res14atp.1yr.co2<0))
mean(res14atp.3yr.co2[which(res14atp.3yr.co2>=0)])
length(res14atp.3yr.co2)-length(which(res14atp.3yr.co2<0))
print("14-WTA")
mean(res14wta.1yr.co2[which(res14wta.1yr.co2>=0)])
length(res14wta.1yr.co2)-length(which(res14wta.1yr.co2<0))
mean(res14wta.3yr.co2[which(res14wta.3yr.co2>=0)])
length(res14wta.3yr.co2)-length(which(res14wta.3yr.co2<0))
print("18-ATP")
mean(res18atp.1yr.co2[which(res18atp.1yr.co2>=0)])
length(res18atp.1yr.co2)-length(which(res18atp.1yr.co2<0))
mean(res18atp.3yr.co2[which(res18atp.3yr.co2>=0)])
length(res18atp.3yr.co2)-length(which(res18atp.3yr.co2<0))
print("18-WTA")
mean(res18wta.1yr.co2[which(res18wta.1yr.co2>=0)])
length(res18wta.1yr.co2)-length(which(res18wta.1yr.co2<0))
mean(res18wta.3yr.co2[which(res18wta.3yr.co2>=0)])
length(res18wta.3yr.co2)-length(which(res18wta.3yr.co2<0))
print("22-ATP")
mean(res22atp.1yr.co2[which(res22atp.1yr.co2>=0)])
length(res22atp.1yr.co2)-length(which(res22atp.1yr.co2<0))
mean(res22atp.3yr.co2[which(res22atp.3yr.co2>=0)])
length(res22atp.3yr.co2)-length(which(res22atp.3yr.co2<0))
print("22-WTA")
mean(res22wta.1yr.co2[which(res22wta.1yr.co2>=0)])
length(res22wta.1yr.co2)-length(which(res22wta.1yr.co2<0))
mean(res22wta.3yr.co2[which(res22wta.3yr.co2>=0)])
length(res22wta.3yr.co2)-length(which(res22wta.3yr.co2<0))
```

# CO2(ns)

```{r}
atp14.1y <- read.csv('../Data Lake/Players/2013_atp_co2_ns.csv')
atp14.3y <- read.csv('../Data Lake/Players/2011-2013_atp_co2_ns.csv')
wta14.1y <- read.csv('../Data Lake/Players/2013_wta_co2_ns.csv')
wta14.3y <- read.csv('../Data Lake/Players/2011-2013_wta_co2_ns.csv')
atp18.1y <- read.csv('../Data Lake/Players/2017_atp_co2_ns.csv')
atp18.3y <- read.csv('../Data Lake/Players/2015-2017_atp_co2_ns.csv')
wta18.1y <- read.csv('../Data Lake/Players/2017_wta_co2_ns.csv')
wta18.3y <- read.csv('../Data Lake/Players/2015-2017_wta_co2_ns.csv')
atp22.1y <- read.csv('../Data Lake/Players/2021_atp_co2_ns.csv')
atp22.3y <- read.csv('../Data Lake/Players/2019-2021_atp_co2_ns.csv')
wta22.1y <- read.csv('../Data Lake/Players/2021_wta_co2_ns.csv')
wta22.3y <- read.csv('../Data Lake/Players/2019-2021_wta_co2_ns.csv')
tm.atp14 <- read.csv('../Data Lake/Experiments/2014_atp_testing.csv')
tm.atp18 <- read.csv('../Data Lake/Experiments/2018_atp_testing.csv')
tm.atp22 <- read.csv('../Data Lake/Experiments/2022_atp_testing.csv')
tm.wta14 <- read.csv('../Data Lake/Experiments/2014_wta_testing.csv')
tm.wta18 <- read.csv('../Data Lake/Experiments/2018_wta_testing.csv')
tm.wta22 <- read.csv('../Data Lake/Experiments/2022_wta_testing.csv')
ic.match <- function(score) grep("[A-Za-z]",score)
ic.atp14 <- ic.match(tm.atp14$score)
ic.atp18 <- ic.match(tm.atp18$score)
ic.atp22 <- ic.match(tm.atp22$score)
ic.wta14 <- ic.match(tm.wta14$score)
ic.wta18 <- ic.match(tm.wta18$score)
ic.wta22 <- ic.match(tm.wta22$score)
atp14.1y <- atp14.1y[-ic.atp14,]
atp14.3y <- atp14.3y[-ic.atp14,]
wta14.1y <- wta14.1y[-ic.wta14,]
wta14.3y <- wta14.3y[-ic.wta14,]
atp18.1y <- atp18.1y[-ic.atp18,]
atp18.3y <- atp18.3y[-ic.atp18,]
wta18.1y <- wta18.1y[-ic.wta18,]
wta18.3y <- wta18.3y[-ic.wta18,]
atp22.1y <- atp22.1y[-ic.atp22,]
atp22.3y <- atp22.3y[-ic.atp22,]
wta22.1y <- wta22.1y[-ic.wta22,]
wta22.3y <- wta22.3y[-ic.wta22,]
rm(tm.atp14,tm.atp18,tm.atp22,tm.wta14,tm.wta18,tm.wta22,
   ic.atp14,ic.atp18,ic.atp22,ic.wta14,ic.wta18,ic.wta22,ic.match)
```

```{r}
co2ns.res <- function(dat){
  dat$p1 <- dat$service_pts_won1/dat$pts_served1
  dat$p2 <- dat$service_pts_won2/dat$pts_served2
  dat$res <- dat$p1 > dat$p2
  dat$res[which(is.na(dat$res))] <- -1
  return(dat$res)
}
```

```{r}
res14atp.1yr.co2ns <- co2ns.res(atp14.1y)
saveRDS(res14atp.1yr.co2ns,file="res14atp_1yr_co2ns.rds")
res14atp.3yr.co2ns <- co2ns.res(atp14.3y)
saveRDS(res14atp.3yr.co2ns,file="res14atp_3yr_co2ns.rds")
res14wta.1yr.co2ns <- co2ns.res(wta14.1y)
saveRDS(res14wta.1yr.co2ns,file="res14wta_1yr_co2ns.rds")
res14wta.3yr.co2ns <- co2ns.res(wta14.3y)
saveRDS(res14wta.3yr.co2ns,file="res14wta_3yr_co2ns.rds")
res18atp.1yr.co2ns <- co2ns.res(atp18.1y)
saveRDS(res18atp.1yr.co2ns,file="res18atp_1yr_co2ns.rds")
res18atp.3yr.co2ns <- co2ns.res(atp18.3y)
saveRDS(res18atp.3yr.co2ns,file="res18atp_3yr_co2ns.rds")
res18wta.1yr.co2ns <- co2ns.res(wta18.1y)
saveRDS(res18wta.1yr.co2ns,file="res18wta_1yr_co2ns.rds")
res18wta.3yr.co2ns <- co2ns.res(wta18.3y)
saveRDS(res18wta.3yr.co2ns,file="res18wta_3yr_co2ns.rds")
res22atp.1yr.co2ns <- co2ns.res(atp22.1y)
saveRDS(res22atp.1yr.co2ns,file="res22atp_1yr_co2ns.rds")
res22atp.3yr.co2ns <- co2ns.res(atp22.3y)
saveRDS(res22atp.3yr.co2ns,file="res22atp_3yr_co2ns.rds")
res22wta.1yr.co2ns <- co2ns.res(wta22.1y)
saveRDS(res22wta.1yr.co2ns,file="res22wta_1yr_co2ns.rds")
res22wta.3yr.co2ns <- co2ns.res(wta22.3y)
saveRDS(res22wta.3yr.co2ns,file="res22wta_3yr_co2ns.rds")
```

```{r}
print("14-ATP")
mean(res14atp.1yr.co2ns[which(res14atp.1yr.co2ns>=0)])
length(res14atp.1yr.co2ns)-length(which(res14atp.1yr.co2ns<0))
mean(res14atp.3yr.co2ns[which(res14atp.3yr.co2ns>=0)])
length(res14atp.3yr.co2ns)-length(which(res14atp.3yr.co2ns<0))
print("14-WTA")
mean(res14wta.1yr.co2ns[which(res14wta.1yr.co2ns>=0)])
length(res14wta.1yr.co2ns)-length(which(res14wta.1yr.co2ns<0))
mean(res14wta.3yr.co2ns[which(res14wta.3yr.co2ns>=0)])
length(res14wta.3yr.co2ns)-length(which(res14wta.3yr.co2ns<0))
print("18-ATP")
mean(res18atp.1yr.co2ns[which(res18atp.1yr.co2ns>=0)])
length(res18atp.1yr.co2ns)-length(which(res18atp.1yr.co2ns<0))
mean(res18atp.3yr.co2ns[which(res18atp.3yr.co2ns>=0)])
length(res18atp.3yr.co2ns)-length(which(res18atp.3yr.co2ns<0))
print("18-WTA")
mean(res18wta.1yr.co2ns[which(res18wta.1yr.co2ns>=0)])
length(res18wta.1yr.co2ns)-length(which(res18wta.1yr.co2ns<0))
mean(res18wta.3yr.co2ns[which(res18wta.3yr.co2ns>=0)])
length(res18wta.3yr.co2ns)-length(which(res18wta.3yr.co2ns<0))
print("22-ATP")
mean(res22atp.1yr.co2ns[which(res22atp.1yr.co2ns>=0)])
length(res22atp.1yr.co2ns)-length(which(res22atp.1yr.co2ns<0))
mean(res22atp.3yr.co2ns[which(res22atp.3yr.co2ns>=0)])
length(res22atp.3yr.co2ns)-length(which(res22atp.3yr.co2ns<0))
print("22-WTA")
mean(res22wta.1yr.co2ns[which(res22wta.1yr.co2ns>=0)])
length(res22wta.1yr.co2ns)-length(which(res22wta.1yr.co2ns<0))
mean(res22wta.3yr.co2ns[which(res22wta.3yr.co2ns>=0)])
length(res22wta.3yr.co2ns)-length(which(res22wta.3yr.co2ns<0))
```


# WTA22 H2H

```{r}
res22wta.1yr.h2h.ns <- readRDS("res22wta_1yr_h2h_ns.rds")
res22wta.1yr.h2h.s <- readRDS("res22wta_1yr_h2h_s.rds")
res22wta.3yr.h2h.ns <- readRDS("res22wta_3yr_h2h_ns.rds")
res22wta.3yr.h2h.s <- readRDS("res22wta_3yr_h2h_s.rds")
res22wta.1yr.co.ns <- readRDS("res22wta_1yr_co_ns.rds")
res22wta.1yr.co.s <- readRDS("res22wta_1yr_co_s.rds")
res22wta.3yr.co.ns <- readRDS("res22wta_3yr_co_ns.rds")
res22wta.3yr.co.s <- readRDS("res22wta_3yr_co_s.rds")
res22wta.1yr.oaf.ns <- readRDS("res22wta_1yr_oaf_ns.rds")
res22wta.1yr.oaf.s <- readRDS("res22wta_1yr_oaf_s.rds")
res22wta.3yr.oaf.ns <- readRDS("res22wta_3yr_oaf_ns.rds")
res22wta.3yr.oaf.s <- readRDS("res22wta_3yr_oaf_s.rds")
res22wta.1yr.g.ns <- readRDS("res22wta_1yr_g_ns.rds")
res22wta.1yr.g.s <- readRDS("res22wta_1yr_g_s.rds")
res22wta.3yr.g.ns <- readRDS("res22wta_3yr_g_ns.rds")
res22wta.3yr.g.s <- readRDS("res22wta_3yr_g_s.rds")
res22wta.1yr.cooaf.ns <- readRDS("res22wta_1yr_cooaf_ns.rds")
res22wta.1yr.cooaf.s <- readRDS("res22wta_1yr_cooaf_s.rds")
res22wta.3yr.cooaf.ns <- readRDS("res22wta_3yr_cooaf_ns.rds")
res22wta.3yr.cooaf.s <- readRDS("res22wta_3yr_cooaf_s.rds")
res22wta.1yr.co2 <- readRDS("res22wta_1yr_co2.rds")
res22wta.3yr.co2 <- readRDS("res22wta_3yr_co2.rds")
wta.test.2022 <- read.csv('../Data Lake/Experiments/2022_wta_testing.csv')
ic.match <- function(score) grep("[A-Za-z]",score)
ic.wta <- ic.match(wta.test.2022$score)
wta.test.2022 <- wta.test.2022[-ic.wta,]
rm(ic.wta,ic.match)
```
```{r}
examine <- cbind(wta.test.2022$tourney_name,
                 wta.test.2022$surface,
                 wta.test.2022$winner_name,
                 wta.test.2022$loser_name,
                 res22wta.1yr.g.ns,
                 res22wta.1yr.g.s,
                 res22wta.3yr.g.ns,
                 res22wta.3yr.g.s,
                 res22wta.1yr.h2h.ns,
                 res22wta.1yr.h2h.s,
                 res22wta.3yr.h2h.ns,
                 res22wta.3yr.h2h.s,
                 res22wta.1yr.co.ns,
                 res22wta.1yr.co.s,
                 res22wta.3yr.co.ns,
                 res22wta.3yr.co.s,
                 res22wta.1yr.oaf.ns,
                 res22wta.1yr.oaf.s,
                 res22wta.3yr.oaf.ns,
                 res22wta.3yr.oaf.s,
                 res22wta.1yr.cooaf.ns,
                 res22wta.1yr.cooaf.s,
                 res22wta.3yr.cooaf.ns,
                 res22wta.3yr.cooaf.s)
examine <- data.frame(examine)
```
```{r}
ex <- examine[which(examine$res22wta.3yr.g.ns!=examine$res22wta.3yr.h2h.ns
                    & examine$res22wta.3yr.h2h.ns!=-1),
              c(1:4,7,11)]
```


# Test sets
```{r}
atp.test.2014 <- read.csv('../Data Lake/Experiments/2014_atp_testing.csv')
atp.test.2018 <- read.csv('../Data Lake/Experiments/2018_atp_testing.csv')
atp.test.2022 <- read.csv('../Data Lake/Experiments/2022_atp_testing.csv')
wta.test.2014 <- read.csv('../Data Lake/Experiments/2014_wta_testing.csv')
wta.test.2018 <- read.csv('../Data Lake/Experiments/2018_wta_testing.csv')
wta.test.2022 <- read.csv('../Data Lake/Experiments/2022_wta_testing.csv')
```

# CO2 Examination

```{r}
s <- readRDS("res14wta_1yr_co2.rds")
ns <- readRDS("res14wta_1yr_co2ns.rds")
tm.wta14 <- read.csv('../Data Lake/Experiments/2014_wta_testing.csv')
ic.match <- function(score) grep("[A-Za-z]",score)
ic.wta14 <- ic.match(tm.wta14$score)
tm.wta14 <- tm.wta14[-ic.wta14,]
```
```{r}
which(s==-1)
which(ns==-1)
```
```{r}
ex <- cbind(tm.wta14[,c(2,5,6)],s,ns)
```

