---
title: "Overlay"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Code for two layer and three layer overlays. Taken from code at the end of notebook 4.

```{r}
two.layer <- function(l1,l2){
  # l1/l2, e.g., in H2H/G, H2H is l1 and G is l2
  l1.valid <- which(!(l1==-1))
  res <- l2
  res[l1.valid] <- l1[l1.valid]
  mean(res)
}
three.layer <- function(l1,l2,l3){
  # same as above, l3 is bottom layer with full coverage
  l1.valid <- which(!(l1==-1))
  l2.valid <- which(!(l2==-1))
  res <- l3
  res[l2.valid] <- l2[l2.valid]
  res[l1.valid] <- l1[l1.valid]
  mean(res)
}
```

# Loading Data

Ctrl+F and replace all for "resyy" where "yy" is year - 14, 18, or 22.

```{r}
res14atp.1yr.h2h.ns <- readRDS("res14atp_1yr_h2h_ns.rds")
res14atp.1yr.h2h.s <- readRDS("res14atp_1yr_h2h_s.rds")
res14atp.3yr.h2h.ns <- readRDS("res14atp_3yr_h2h_ns.rds")
res14atp.3yr.h2h.s <- readRDS("res14atp_3yr_h2h_s.rds")
res14atp.1yr.co.ns <- readRDS("res14atp_1yr_co_ns.rds")
res14atp.1yr.co.s <- readRDS("res14atp_1yr_co_s.rds")
res14atp.3yr.co.ns <- readRDS("res14atp_3yr_co_ns.rds")
res14atp.3yr.co.s <- readRDS("res14atp_3yr_co_s.rds")
res14atp.1yr.cooaf.ns <- readRDS("res14atp_1yr_cooaf_ns.rds")
res14atp.1yr.cooaf.s <- readRDS("res14atp_1yr_cooaf_s.rds")
res14atp.3yr.cooaf.ns <- readRDS("res14atp_3yr_cooaf_ns.rds")
res14atp.3yr.cooaf.s <- readRDS("res14atp_3yr_cooaf_s.rds")
res14atp.1yr.oaf.ns <- readRDS("res14atp_1yr_oaf_ns.rds")
res14atp.1yr.oaf.s <- readRDS("res14atp_1yr_oaf_s.rds")
res14atp.3yr.oaf.ns <- readRDS("res14atp_3yr_oaf_ns.rds")
res14atp.3yr.oaf.s <- readRDS("res14atp_3yr_oaf_s.rds")
res14atp.1yr.g.ns <- readRDS("res14atp_1yr_g_ns.rds")
res14atp.1yr.g.s <- readRDS("res14atp_1yr_g_s.rds")
res14atp.3yr.g.ns <- readRDS("res14atp_3yr_g_ns.rds")
res14atp.3yr.g.s <- readRDS("res14atp_3yr_g_s.rds")
res14atp.1yr.co2 <- readRDS("res14atp_1yr_co2.rds")
res14atp.3yr.co2 <- readRDS("res14atp_3yr_co2.rds")
res14wta.1yr.h2h.ns <- readRDS("res14wta_1yr_h2h_ns.rds")
res14wta.1yr.h2h.s <- readRDS("res14wta_1yr_h2h_s.rds")
res14wta.3yr.h2h.ns <- readRDS("res14wta_3yr_h2h_ns.rds")
res14wta.3yr.h2h.s <- readRDS("res14wta_3yr_h2h_s.rds")
res14wta.1yr.co.ns <- readRDS("res14wta_1yr_co_ns.rds")
res14wta.1yr.co.s <- readRDS("res14wta_1yr_co_s.rds")
res14wta.3yr.co.ns <- readRDS("res14wta_3yr_co_ns.rds")
res14wta.3yr.co.s <- readRDS("res14wta_3yr_co_s.rds")
res14wta.1yr.oaf.ns <- readRDS("res14wta_1yr_oaf_ns.rds")
res14wta.1yr.oaf.s <- readRDS("res14wta_1yr_oaf_s.rds")
res14wta.3yr.oaf.ns <- readRDS("res14wta_3yr_oaf_ns.rds")
res14wta.3yr.oaf.s <- readRDS("res14wta_3yr_oaf_s.rds")
res14wta.1yr.g.ns <- readRDS("res14wta_1yr_g_ns.rds")
res14wta.1yr.g.s <- readRDS("res14wta_1yr_g_s.rds")
res14wta.3yr.g.ns <- readRDS("res14wta_3yr_g_ns.rds")
res14wta.3yr.g.s <- readRDS("res14wta_3yr_g_s.rds")
res14wta.1yr.cooaf.ns <- readRDS("res14wta_1yr_cooaf_ns.rds")
res14wta.1yr.cooaf.s <- readRDS("res14wta_1yr_cooaf_s.rds")
res14wta.3yr.cooaf.ns <- readRDS("res14wta_3yr_cooaf_ns.rds")
res14wta.3yr.cooaf.s <- readRDS("res14wta_3yr_cooaf_s.rds")
res14wta.1yr.co2 <- readRDS("res14wta_1yr_co2.rds")
res14wta.3yr.co2 <- readRDS("res14wta_3yr_co2.rds")
```

# Results

## H2H/G

```{r}
two.layer(res14atp.1yr.h2h.ns,res14atp.1yr.g.ns)
two.layer(res14atp.1yr.h2h.s,res14atp.1yr.g.s)
two.layer(res14atp.3yr.h2h.ns,res14atp.3yr.g.ns)
two.layer(res14atp.3yr.h2h.s,res14atp.3yr.g.s)
two.layer(res14wta.1yr.h2h.ns,res14wta.1yr.g.ns)
two.layer(res14wta.1yr.h2h.s,res14wta.1yr.g.s)
two.layer(res14wta.3yr.h2h.ns,res14wta.3yr.g.ns)
two.layer(res14wta.3yr.h2h.s,res14wta.3yr.g.s)
```

## H2H/OAF

```{r}
two.layer(res14atp.1yr.h2h.ns,res14atp.1yr.oaf.ns)
two.layer(res14atp.1yr.h2h.s,res14atp.1yr.oaf.s)
two.layer(res14atp.3yr.h2h.ns,res14atp.3yr.oaf.ns)
two.layer(res14atp.3yr.h2h.s,res14atp.3yr.oaf.s)
two.layer(res14wta.1yr.h2h.ns,res14wta.1yr.oaf.ns)
two.layer(res14wta.1yr.h2h.s,res14wta.1yr.oaf.s)
two.layer(res14wta.3yr.h2h.ns,res14wta.3yr.oaf.ns)
two.layer(res14wta.3yr.h2h.s,res14wta.3yr.oaf.s)
```

## CO/G

```{r}
two.layer(res14atp.1yr.co.ns,res14atp.1yr.g.ns)
two.layer(res14atp.1yr.co.s,res14atp.1yr.g.s)
two.layer(res14atp.3yr.co.ns,res14atp.3yr.g.ns)
two.layer(res14atp.3yr.co.s,res14atp.3yr.g.s)
two.layer(res14wta.1yr.co.ns,res14wta.1yr.g.ns)
two.layer(res14wta.1yr.co.s,res14wta.1yr.g.s)
two.layer(res14wta.3yr.co.ns,res14wta.3yr.g.ns)
two.layer(res14wta.3yr.co.s,res14wta.3yr.g.s)
```

## CO/OAF

```{r}
two.layer(res14atp.1yr.co.ns,res14atp.1yr.oaf.ns)
two.layer(res14atp.1yr.co.s,res14atp.1yr.oaf.s)
two.layer(res14atp.3yr.co.ns,res14atp.3yr.oaf.ns)
two.layer(res14atp.3yr.co.s,res14atp.3yr.oaf.s)
two.layer(res14wta.1yr.co.ns,res14wta.1yr.oaf.ns)
two.layer(res14wta.1yr.co.s,res14wta.1yr.oaf.s)
two.layer(res14wta.3yr.co.ns,res14wta.3yr.oaf.ns)
two.layer(res14wta.3yr.co.s,res14wta.3yr.oaf.s)
```

## CO(OAF)/G

```{r}
two.layer(res14atp.1yr.cooaf.ns,res14atp.1yr.g.ns)
two.layer(res14atp.1yr.cooaf.s,res14atp.1yr.g.s)
two.layer(res14atp.3yr.cooaf.ns,res14atp.3yr.g.ns)
two.layer(res14atp.3yr.cooaf.s,res14atp.3yr.g.s)
two.layer(res14wta.1yr.cooaf.ns,res14wta.1yr.g.ns)
two.layer(res14wta.1yr.cooaf.s,res14wta.1yr.g.s)
two.layer(res14wta.3yr.cooaf.ns,res14wta.3yr.g.ns)
two.layer(res14wta.3yr.cooaf.s,res14wta.3yr.g.s)
```

## CO(OAF)/OAF

```{r}
two.layer(res14atp.1yr.cooaf.ns,res14atp.1yr.oaf.ns)
two.layer(res14atp.1yr.cooaf.s,res14atp.1yr.oaf.s)
two.layer(res14atp.3yr.cooaf.ns,res14atp.3yr.oaf.ns)
two.layer(res14atp.3yr.cooaf.s,res14atp.3yr.oaf.s)
two.layer(res14wta.1yr.cooaf.ns,res14wta.1yr.oaf.ns)
two.layer(res14wta.1yr.cooaf.s,res14wta.1yr.oaf.s)
two.layer(res14wta.3yr.cooaf.ns,res14wta.3yr.oaf.ns)
two.layer(res14wta.3yr.cooaf.s,res14wta.3yr.oaf.s)
```

## H2H/CO/G

```{r}
three.layer(res14atp.1yr.h2h.ns,res14atp.1yr.co.ns,res14atp.1yr.g.ns)
three.layer(res14atp.1yr.h2h.s,res14atp.1yr.co.s,res14atp.1yr.g.s)
three.layer(res14atp.3yr.h2h.ns,res14atp.3yr.co.ns,res14atp.3yr.g.ns)
three.layer(res14atp.3yr.h2h.s,res14atp.3yr.co.s,res14atp.3yr.g.s)
three.layer(res14wta.1yr.h2h.ns,res14wta.1yr.co.ns,res14wta.1yr.g.ns)
three.layer(res14wta.1yr.h2h.s,res14wta.1yr.co.s,res14wta.1yr.g.s)
three.layer(res14wta.3yr.h2h.ns,res14wta.3yr.co.ns,res14wta.3yr.g.ns)
three.layer(res14wta.3yr.h2h.s,res14wta.3yr.co.s,res14wta.3yr.g.s)
```

## H2H/CO/OAF

```{r}
three.layer(res14atp.1yr.h2h.ns,res14atp.1yr.co.ns,res14atp.1yr.oaf.ns)
three.layer(res14atp.1yr.h2h.s,res14atp.1yr.co.s,res14atp.1yr.oaf.s)
three.layer(res14atp.3yr.h2h.ns,res14atp.3yr.co.ns,res14atp.3yr.oaf.ns)
three.layer(res14atp.3yr.h2h.s,res14atp.3yr.co.s,res14atp.3yr.oaf.s)
three.layer(res14wta.1yr.h2h.ns,res14wta.1yr.co.ns,res14wta.1yr.oaf.ns)
three.layer(res14wta.1yr.h2h.s,res14wta.1yr.co.s,res14wta.1yr.oaf.s)
three.layer(res14wta.3yr.h2h.ns,res14wta.3yr.co.ns,res14wta.3yr.oaf.ns)
three.layer(res14wta.3yr.h2h.s,res14wta.3yr.co.s,res14wta.3yr.oaf.s)
```

## H2H/CO(OAF)/G

```{r}
three.layer(res14atp.1yr.h2h.ns,res14atp.1yr.cooaf.ns,res14atp.1yr.g.ns)
three.layer(res14atp.1yr.h2h.s,res14atp.1yr.cooaf.s,res14atp.1yr.g.s)
three.layer(res14atp.3yr.h2h.ns,res14atp.3yr.cooaf.ns,res14atp.3yr.g.ns)
three.layer(res14atp.3yr.h2h.s,res14atp.3yr.cooaf.s,res14atp.3yr.g.s)
three.layer(res14wta.1yr.h2h.ns,res14wta.1yr.cooaf.ns,res14wta.1yr.g.ns)
three.layer(res14wta.1yr.h2h.s,res14wta.1yr.cooaf.s,res14wta.1yr.g.s)
three.layer(res14wta.3yr.h2h.ns,res14wta.3yr.cooaf.ns,res14wta.3yr.g.ns)
three.layer(res14wta.3yr.h2h.s,res14wta.3yr.cooaf.s,res14wta.3yr.g.s)
```

## H2H/CO(OAF)/OAF

```{r}
three.layer(res14atp.1yr.h2h.ns,res14atp.1yr.cooaf.ns,res14atp.1yr.oaf.ns)
three.layer(res14atp.1yr.h2h.s,res14atp.1yr.cooaf.s,res14atp.1yr.oaf.s)
three.layer(res14atp.3yr.h2h.ns,res14atp.3yr.cooaf.ns,res14atp.3yr.oaf.ns)
three.layer(res14atp.3yr.h2h.s,res14atp.3yr.cooaf.s,res14atp.3yr.oaf.s)
three.layer(res14wta.1yr.h2h.ns,res14wta.1yr.cooaf.ns,res14wta.1yr.oaf.ns)
three.layer(res14wta.1yr.h2h.s,res14wta.1yr.cooaf.s,res14wta.1yr.oaf.s)
three.layer(res14wta.3yr.h2h.ns,res14wta.3yr.cooaf.ns,res14wta.3yr.oaf.ns)
three.layer(res14wta.3yr.h2h.s,res14wta.3yr.cooaf.s,res14wta.3yr.oaf.s)
```

## CO2/G

```{r}
two.layer(res14atp.1yr.co2,res14atp.1yr.g.s)
two.layer(res14atp.3yr.co2,res14atp.3yr.g.s)
two.layer(res14wta.1yr.co2,res14wta.1yr.g.s)
two.layer(res14wta.3yr.co2,res14wta.3yr.g.s)
```

## CO2/OAF

```{r}
two.layer(res14atp.1yr.co2,res14atp.1yr.oaf.s)
two.layer(res14atp.3yr.co2,res14atp.3yr.oaf.s)
two.layer(res14wta.1yr.co2,res14wta.1yr.oaf.s)
two.layer(res14wta.3yr.co2,res14wta.3yr.oaf.s)
```

## H2H/CO2/G

```{r}
three.layer(res14atp.1yr.h2h.s,res14atp.1yr.co2,res14atp.1yr.g.s)
three.layer(res14atp.3yr.h2h.s,res14atp.3yr.co2,res14atp.3yr.g.s)
three.layer(res14wta.1yr.h2h.s,res14wta.1yr.co2,res14wta.1yr.g.s)
three.layer(res14wta.3yr.h2h.s,res14wta.3yr.co2,res14wta.3yr.g.s)
```

## H2H/CO2/OAF

```{r}
three.layer(res14atp.1yr.h2h.s,res14atp.1yr.co2,res14atp.1yr.oaf.s)
three.layer(res14atp.3yr.h2h.s,res14atp.3yr.co2,res14atp.3yr.oaf.s)
three.layer(res14wta.1yr.h2h.s,res14wta.1yr.co2,res14wta.1yr.oaf.s)
three.layer(res14wta.3yr.h2h.s,res14wta.3yr.co2,res14wta.3yr.oaf.s)
```

# Experimental Combinations for H2H

```{r}
e.res14atp.1yr.h2h.ns <- readRDS("p_est_exact_probs/atp2018_1y_ns_h2h.rds")
e.res14atp.1yr.h2h.s <- readRDS("p_est_exact_probs/atp2018_1y_s_h2h.rds")
e.res14atp.3yr.h2h.ns <- readRDS("p_est_exact_probs/atp2018_3y_ns_h2h.rds")
e.res14atp.3yr.h2h.s <- readRDS("p_est_exact_probs/atp2018_3y_s_h2h.rds")
e.res14atp.1yr.co.ns <- readRDS("p_est_exact_probs/atp2018_1y_ns_co.rds")
e.res14atp.1yr.co.s <- readRDS("p_est_exact_probs/atp2018_1y_s_co.rds")
e.res14atp.3yr.co.ns <- readRDS("p_est_exact_probs/atp2018_3y_ns_co.rds")
e.res14atp.3yr.co.s <- readRDS("p_est_exact_probs/atp2018_3y_s_co.rds")
e.res14atp.1yr.oaf.ns <- readRDS("p_est_exact_probs/atp2018_1y_ns_oaf_exact.rds")
e.res14atp.1yr.oaf.s <- readRDS("p_est_exact_probs/atp2018_1y_s_oaf_exact.rds")
e.res14atp.3yr.oaf.ns <- readRDS("p_est_exact_probs/atp2018_3y_ns_oaf_exact.rds")
e.res14atp.3yr.oaf.s <- readRDS("p_est_exact_probs/atp2018_3y_s_oaf_exact.rds")
e.res14atp.1yr.cooaf.ns <- readRDS("p_est_exact_probs/atp2018_1y_ns_cooaf.rds")
e.res14atp.1yr.cooaf.s <- readRDS("p_est_exact_probs/atp2018_1y_s_cooaf.rds")
e.res14atp.3yr.cooaf.ns <- readRDS("p_est_exact_probs/atp2018_3y_ns_cooaf.rds")
e.res14atp.3yr.cooaf.s <- readRDS("p_est_exact_probs/atp2018_3y_s_cooaf.rds")
e.res14wta.1yr.h2h.ns <- readRDS("p_est_exact_probs/wta2018_1y_ns_h2h.rds")
e.res14wta.1yr.h2h.s <- readRDS("p_est_exact_probs/wta2018_1y_s_h2h.rds")
e.res14wta.3yr.h2h.ns <- readRDS("p_est_exact_probs/wta2018_3y_ns_h2h.rds")
e.res14wta.3yr.h2h.s <- readRDS("p_est_exact_probs/wta2018_3y_s_h2h.rds")
e.res14wta.1yr.co.ns <- readRDS("p_est_exact_probs/wta2018_1y_ns_co.rds")
e.res14wta.1yr.co.s <- readRDS("p_est_exact_probs/wta2018_1y_s_co.rds")
e.res14wta.3yr.co.ns <- readRDS("p_est_exact_probs/wta2018_3y_ns_co.rds")
e.res14wta.3yr.co.s <- readRDS("p_est_exact_probs/wta2018_3y_s_co.rds")
e.res14wta.1yr.oaf.ns <- readRDS("p_est_exact_probs/wta2018_1y_ns_oaf_exact.rds")
e.res14wta.1yr.oaf.s <- readRDS("p_est_exact_probs/wta2018_1y_s_oaf_exact.rds")
e.res14wta.3yr.oaf.ns <- readRDS("p_est_exact_probs/wta2018_3y_ns_oaf_exact.rds")
e.res14wta.3yr.oaf.s <- readRDS("p_est_exact_probs/wta2018_3y_s_oaf_exact.rds")
e.res14wta.1yr.cooaf.ns <- readRDS("p_est_exact_probs/wta2018_1y_ns_cooaf.rds")
e.res14wta.1yr.cooaf.s <- readRDS("p_est_exact_probs/wta2018_1y_s_cooaf.rds")
e.res14wta.3yr.cooaf.ns <- readRDS("p_est_exact_probs/wta2018_3y_ns_cooaf.rds")
e.res14wta.3yr.cooaf.s <- readRDS("p_est_exact_probs/wta2018_3y_s_cooaf.rds")
```

```{r}
add.when.valid.2 <- function(res1,res2){
  n <- length(res1)
  res <- rep(0,n)
  for (i in 1:n){
    if (res1[i]==-1){
      res[i] <- res2[i]
    } else if (res2[i]==-1){
      res[i] <- res1[i]
    } else {
      res[i] <- (res1[i]+res2[i])/2
    }
  }
  return(res)
}

add.when.valid.3 <- function(res1,res2,res3){
  n <- length(res1)
  res <- rep(0,n)
  for (i in 1:n){
    if (res1[i]==-1){
      res[i] <- add.when.valid.2(res2[i],res3[i])
    } else if (res2[i]==-1){
      res[i] <- add.when.valid.2(res1[i],res3[i])
    } else if (res3[i]==-1){
      res[i] <- add.when.valid.2(res1[i],res2[i])
    } else {
      res[i] <- mean(res1[i],res2[i],res3[i])
    }
  }
  return(res)
}
```

## H2H + CO

```{r}
a <- add.when.valid.2(e.res14atp.1yr.h2h.ns,e.res14atp.1yr.co.ns)
b <- add.when.valid.2(e.res14atp.1yr.h2h.s,e.res14atp.1yr.co.s)
c <- add.when.valid.2(e.res14atp.3yr.h2h.ns,e.res14atp.3yr.co.ns)
d <- add.when.valid.2(e.res14atp.3yr.h2h.s,e.res14atp.3yr.co.s)
e <- add.when.valid.2(e.res14wta.1yr.h2h.ns,e.res14wta.1yr.co.ns)
f <- add.when.valid.2(e.res14wta.1yr.h2h.s,e.res14wta.1yr.co.s)
g <- add.when.valid.2(e.res14wta.3yr.h2h.ns,e.res14wta.3yr.co.ns)
h <- add.when.valid.2(e.res14wta.3yr.h2h.s,e.res14wta.3yr.co.s)
mean(a[which(a>=0)]>0.5)
mean(b[which(b>=0)]>0.5)
mean(c[which(c>=0)]>0.5)
mean(d[which(d>=0)]>0.5)
mean(e[which(e>=0)]>0.5)
mean(f[which(f>=0)]>0.5)
mean(g[which(g>=0)]>0.5)
mean(h[which(h>=0)]>0.5)
```

## H2H+OAF

```{r}
a <- add.when.valid.2(e.res14atp.1yr.h2h.ns,e.res14atp.1yr.oaf.ns)
b <- add.when.valid.2(e.res14atp.1yr.h2h.s,e.res14atp.1yr.oaf.s)
c <- add.when.valid.2(e.res14atp.3yr.h2h.ns,e.res14atp.3yr.oaf.ns)
d <- add.when.valid.2(e.res14atp.3yr.h2h.s,e.res14atp.3yr.oaf.s)
e <- add.when.valid.2(e.res14wta.1yr.h2h.ns,e.res14wta.1yr.oaf.ns)
f <- add.when.valid.2(e.res14wta.1yr.h2h.s,e.res14wta.1yr.oaf.s)
g <- add.when.valid.2(e.res14wta.3yr.h2h.ns,e.res14wta.3yr.oaf.ns)
h <- add.when.valid.2(e.res14wta.3yr.h2h.s,e.res14wta.3yr.oaf.s)
mean(a[which(a>=0)]>0.5)
mean(b[which(b>=0)]>0.5)
mean(c[which(c>=0)]>0.5)
mean(d[which(d>=0)]>0.5)
mean(e[which(e>=0)]>0.5)
mean(f[which(f>=0)]>0.5)
mean(g[which(g>=0)]>0.5)
mean(h[which(h>=0)]>0.5)
```

## H2H+CO(OAF)

```{r}
a <- add.when.valid.2(e.res14atp.1yr.h2h.ns,e.res14atp.1yr.cooaf.ns)
b <- add.when.valid.2(e.res14atp.1yr.h2h.s,e.res14atp.1yr.cooaf.s)
c <- add.when.valid.2(e.res14atp.3yr.h2h.ns,e.res14atp.3yr.cooaf.ns)
d <- add.when.valid.2(e.res14atp.3yr.h2h.s,e.res14atp.3yr.cooaf.s)
e <- add.when.valid.2(e.res14wta.1yr.h2h.ns,e.res14wta.1yr.cooaf.ns)
f <- add.when.valid.2(e.res14wta.1yr.h2h.s,e.res14wta.1yr.cooaf.s)
g <- add.when.valid.2(e.res14wta.3yr.h2h.ns,e.res14wta.3yr.cooaf.ns)
h <- add.when.valid.2(e.res14wta.3yr.h2h.s,e.res14wta.3yr.cooaf.s)
mean(a[which(a>=0)]>0.5)
mean(b[which(b>=0)]>0.5)
mean(c[which(c>=0)]>0.5)
mean(d[which(d>=0)]>0.5)
mean(e[which(e>=0)]>0.5)
mean(f[which(f>=0)]>0.5)
mean(g[which(g>=0)]>0.5)
mean(h[which(h>=0)]>0.5)
```

## H2H+CO+OAF

```{r}
a <- add.when.valid.3(e.res14atp.1yr.h2h.ns,e.res14atp.1yr.co.ns,e.res14atp.1yr.oaf.ns)
b <- add.when.valid.3(e.res14atp.1yr.h2h.s,e.res14atp.1yr.co.s,e.res14atp.1yr.oaf.s)
c <- add.when.valid.3(e.res14atp.3yr.h2h.ns,e.res14atp.3yr.co.ns,e.res14atp.3yr.oaf.ns)
d <- add.when.valid.3(e.res14atp.3yr.h2h.s,e.res14atp.3yr.co.s,e.res14atp.3yr.oaf.s)
e <- add.when.valid.3(e.res14wta.1yr.h2h.ns,e.res14wta.1yr.co.ns,e.res14wta.1yr.oaf.ns)
f <- add.when.valid.3(e.res14wta.1yr.h2h.s,e.res14wta.1yr.co.s,e.res14wta.1yr.oaf.s)
g <- add.when.valid.3(e.res14wta.3yr.h2h.ns,e.res14wta.3yr.co.ns,e.res14wta.3yr.oaf.ns)
h <- add.when.valid.3(e.res14wta.3yr.h2h.s,e.res14wta.3yr.co.s,e.res14wta.3yr.oaf.s)
mean(a[which(a>=0)]>0.5)
mean(b[which(b>=0)]>0.5)
mean(c[which(c>=0)]>0.5)
mean(d[which(d>=0)]>0.5)
mean(e[which(e>=0)]>0.5)
mean(f[which(f>=0)]>0.5)
mean(g[which(g>=0)]>0.5)
mean(h[which(h>=0)]>0.5)
```

## CO+OAF

```{r}
a <- add.when.valid.2(e.res14atp.1yr.co.ns,e.res14atp.1yr.oaf.ns)
b <- add.when.valid.2(e.res14atp.1yr.co.s,e.res14atp.1yr.oaf.s)
c <- add.when.valid.2(e.res14atp.3yr.co.ns,e.res14atp.3yr.oaf.ns)
d <- add.when.valid.2(e.res14atp.3yr.co.s,e.res14atp.3yr.oaf.s)
e <- add.when.valid.2(e.res14wta.1yr.co.ns,e.res14wta.1yr.oaf.ns)
f <- add.when.valid.2(e.res14wta.1yr.co.s,e.res14wta.1yr.oaf.s)
g <- add.when.valid.2(e.res14wta.3yr.co.ns,e.res14wta.3yr.oaf.ns)
h <- add.when.valid.2(e.res14wta.3yr.co.s,e.res14wta.3yr.oaf.s)
mean(a[which(a>=0)]>0.5)
mean(b[which(b>=0)]>0.5)
mean(c[which(c>=0)]>0.5)
mean(d[which(d>=0)]>0.5)
mean(e[which(e>=0)]>0.5)
mean(f[which(f>=0)]>0.5)
mean(g[which(g>=0)]>0.5)
mean(h[which(h>=0)]>0.5)
```

## CO+CO(OAF)

```{r}
a <- add.when.valid.2(e.res14atp.1yr.co.ns,e.res14atp.1yr.cooaf.ns)
b <- add.when.valid.2(e.res14atp.1yr.co.s,e.res14atp.1yr.cooaf.s)
c <- add.when.valid.2(e.res14atp.3yr.co.ns,e.res14atp.3yr.cooaf.ns)
d <- add.when.valid.2(e.res14atp.3yr.co.s,e.res14atp.3yr.cooaf.s)
e <- add.when.valid.2(e.res14wta.1yr.co.ns,e.res14wta.1yr.cooaf.ns)
f <- add.when.valid.2(e.res14wta.1yr.co.s,e.res14wta.1yr.cooaf.s)
g <- add.when.valid.2(e.res14wta.3yr.co.ns,e.res14wta.3yr.cooaf.ns)
h <- add.when.valid.2(e.res14wta.3yr.co.s,e.res14wta.3yr.cooaf.s)
mean(a[which(a>=0)]>0.5)
mean(b[which(b>=0)]>0.5)
mean(c[which(c>=0)]>0.5)
mean(d[which(d>=0)]>0.5)
mean(e[which(e>=0)]>0.5)
mean(f[which(f>=0)]>0.5)
mean(g[which(g>=0)]>0.5)
mean(h[which(h>=0)]>0.5)
```

## OAF+CO(OAF)

```{r}
a <- add.when.valid.2(e.res14atp.1yr.oaf.ns,e.res14atp.1yr.cooaf.ns)
b <- add.when.valid.2(e.res14atp.1yr.oaf.s,e.res14atp.1yr.cooaf.s)
c <- add.when.valid.2(e.res14atp.3yr.oaf.ns,e.res14atp.3yr.cooaf.ns)
d <- add.when.valid.2(e.res14atp.3yr.oaf.s,e.res14atp.3yr.cooaf.s)
e <- add.when.valid.2(e.res14wta.1yr.oaf.ns,e.res14wta.1yr.cooaf.ns)
f <- add.when.valid.2(e.res14wta.1yr.oaf.s,e.res14wta.1yr.cooaf.s)
g <- add.when.valid.2(e.res14wta.3yr.oaf.ns,e.res14wta.3yr.cooaf.ns)
h <- add.when.valid.2(e.res14wta.3yr.oaf.s,e.res14wta.3yr.cooaf.s)
mean(a[which(a>=0)]>0.5)
mean(b[which(b>=0)]>0.5)
mean(c[which(c>=0)]>0.5)
mean(d[which(d>=0)]>0.5)
mean(e[which(e>=0)]>0.5)
mean(f[which(f>=0)]>0.5)
mean(g[which(g>=0)]>0.5)
mean(h[which(h>=0)]>0.5)
```

# Only merges with full support (denote with '&')

```{r}
only.agrees <- function(res1,res2){
  ind <- res1==res2 & res1>=0
  print(sum(ind))
  mean(res1[ind])
}

only.agrees.3 <- function(res1,res2,res3){
  ind <- res1==res2 & res2==res3 & res1>=0
  print(sum(ind))
  mean(res1[ind])
}
```

## H2H&CO

```{r}
only.agrees(res14atp.1yr.co.ns,res14atp.1yr.h2h.ns)
only.agrees(res14atp.1yr.co.s,res14atp.1yr.h2h.s)
only.agrees(res14atp.3yr.co.ns,res14atp.3yr.h2h.ns)
only.agrees(res14atp.3yr.co.s,res14atp.3yr.h2h.s)
only.agrees(res14wta.1yr.co.ns,res14wta.1yr.h2h.ns)
only.agrees(res14wta.1yr.co.s,res14wta.1yr.h2h.s)
only.agrees(res14wta.3yr.co.ns,res14wta.3yr.h2h.ns)
only.agrees(res14wta.3yr.co.s,res14wta.3yr.h2h.s)
```

## H2H&OAF

```{r}
only.agrees(res14atp.1yr.oaf.ns,res14atp.1yr.h2h.ns)
only.agrees(res14atp.1yr.oaf.s,res14atp.1yr.h2h.s)
only.agrees(res14atp.3yr.oaf.ns,res14atp.3yr.h2h.ns)
only.agrees(res14atp.3yr.oaf.s,res14atp.3yr.h2h.s)
only.agrees(res14wta.1yr.oaf.ns,res14wta.1yr.h2h.ns)
only.agrees(res14wta.1yr.oaf.s,res14wta.1yr.h2h.s)
only.agrees(res14wta.3yr.oaf.ns,res14wta.3yr.h2h.ns)
only.agrees(res14wta.3yr.oaf.s,res14wta.3yr.h2h.s)
```

## H2H&CO(OAF)

```{r}
only.agrees(res14atp.1yr.cooaf.ns,res14atp.1yr.h2h.ns)
only.agrees(res14atp.1yr.cooaf.s,res14atp.1yr.h2h.s)
only.agrees(res14atp.3yr.cooaf.ns,res14atp.3yr.h2h.ns)
only.agrees(res14atp.3yr.cooaf.s,res14atp.3yr.h2h.s)
only.agrees(res14wta.1yr.cooaf.ns,res14wta.1yr.h2h.ns)
only.agrees(res14wta.1yr.cooaf.s,res14wta.1yr.h2h.s)
only.agrees(res14wta.3yr.cooaf.ns,res14wta.3yr.h2h.ns)
only.agrees(res14wta.3yr.cooaf.s,res14wta.3yr.h2h.s)
```

## CO&OAF

```{r}
only.agrees(res14atp.1yr.co.ns,res14atp.1yr.oaf.ns)
only.agrees(res14atp.1yr.co.s,res14atp.1yr.oaf.s)
only.agrees(res14atp.3yr.co.ns,res14atp.3yr.oaf.ns)
only.agrees(res14atp.3yr.co.s,res14atp.3yr.oaf.s)
only.agrees(res14wta.1yr.co.ns,res14wta.1yr.oaf.ns)
only.agrees(res14wta.1yr.co.s,res14wta.1yr.oaf.s)
only.agrees(res14wta.3yr.co.ns,res14wta.3yr.oaf.ns)
only.agrees(res14wta.3yr.co.s,res14wta.3yr.oaf.s)
```

## CO&CO(OAF)

```{r}
only.agrees(res14atp.1yr.co.ns,res14atp.1yr.cooaf.ns)
only.agrees(res14atp.1yr.co.s,res14atp.1yr.cooaf.s)
only.agrees(res14atp.3yr.co.ns,res14atp.3yr.cooaf.ns)
only.agrees(res14atp.3yr.co.s,res14atp.3yr.cooaf.s)
only.agrees(res14wta.1yr.co.ns,res14wta.1yr.cooaf.ns)
only.agrees(res14wta.1yr.co.s,res14wta.1yr.cooaf.s)
only.agrees(res14wta.3yr.co.ns,res14wta.3yr.cooaf.ns)
only.agrees(res14wta.3yr.co.s,res14wta.3yr.cooaf.s)
```

## OAF&CO(OAF)

```{r}
only.agrees(res14atp.1yr.oaf.ns,res14atp.1yr.cooaf.ns)
only.agrees(res14atp.1yr.oaf.s,res14atp.1yr.cooaf.s)
only.agrees(res14atp.3yr.oaf.ns,res14atp.3yr.cooaf.ns)
only.agrees(res14atp.3yr.oaf.s,res14atp.3yr.cooaf.s)
only.agrees(res14wta.1yr.oaf.ns,res14wta.1yr.cooaf.ns)
only.agrees(res14wta.1yr.oaf.s,res14wta.1yr.cooaf.s)
only.agrees(res14wta.3yr.oaf.ns,res14wta.3yr.cooaf.ns)
only.agrees(res14wta.3yr.oaf.s,res14wta.3yr.cooaf.s)
```

## H2H&CO&OAF

```{r}
only.agrees.3(res14atp.1yr.h2h.ns,res14atp.1yr.co.ns,res14atp.1yr.oaf.ns)
only.agrees.3(res14atp.1yr.h2h.s,res14atp.1yr.co.s,res14atp.1yr.oaf.s)
only.agrees.3(res14atp.3yr.h2h.ns,res14atp.3yr.co.ns,res14atp.3yr.oaf.ns)
only.agrees.3(res14atp.3yr.h2h.s,res14atp.3yr.co.s,res14atp.3yr.oaf.s)
only.agrees.3(res14wta.1yr.h2h.ns,res14wta.1yr.co.ns,res14wta.1yr.oaf.ns)
only.agrees.3(res14wta.1yr.h2h.s,res14wta.1yr.co.s,res14wta.1yr.oaf.s)
only.agrees.3(res14wta.3yr.h2h.ns,res14wta.3yr.co.ns,res14wta.3yr.oaf.ns)
only.agrees.3(res14wta.3yr.h2h.s,res14wta.3yr.co.s,res14wta.3yr.oaf.s)
```


